### 2013-10-22 paper/jfm-ifc/jfm-instructions.tex
adding initial version of paper

% This is file JFM2esam.tex
% first release v1.0, 20th October 1996
%       release v1.01, 29th October 1996
%       release v1.1, 25th June 1997
%       release v2.0, 27th July 2004
%   (based on JFMsampl.tex v1.3 for LaTeX2.09)
% Copyright (C) 1996, 1997 Cambridge University Press

\NeedsTeXFormat{LaTeX2e}

\documentclass{jfm}

\usepackage{graphicx}
\usepackage{natbib}

% See if the author has AMS Euler fonts installed: If they have, attempt
% to use the 'upmath' package to provide upright math.
\ifCUPmtlplainloaded \else
  \checkfont{eurm10}
  \iffontfound
    \IfFileExists{upmath.sty}
      {\typeout{^^JFound AMS Euler Roman fonts on the system,
                   using the 'upmath' package.^^J}%
       \usepackage{upmath}}
      {\typeout{^^JFound AMS Euler Roman fonts on the system, but you
                   dont seem to have the}%
       \typeout{'upmath' package installed. JFM.cls can take advantage
                 of these fonts,^^Jif you use 'upmath' package.^^J}%
       \providecommand\upi{\pi}%
      }
  \else
    \providecommand\upi{\pi}%
  \fi
\fi

% See if the author has AMS symbol fonts installed: If they have, attempt
% to use the 'amssymb' package to provide the AMS symbol characters.

\ifCUPmtlplainloaded \else
  \checkfont{msam10}
  \iffontfound
    \IfFileExists{amssymb.sty}
      {\typeout{^^JFound AMS Symbol fonts on the system, using the
                'amssymb' package.^^J}%
       \usepackage{amssymb}%
       \let\le=\leqslant  \let\leq=\leqslant
       \let\ge=\geqslant  \let\geq=\geqslant
      }{}
  \fi
\fi

% See if the author has the AMS 'amsbsy' package installed: If they have,
% use it to provide better bold math support (with \boldsymbol).

\ifCUPmtlplainloaded \else
  \IfFileExists{amsbsy.sty}
    {\typeout{^^JFound the 'amsbsy' package on the system, using it.^^J}%
     \usepackage{amsbsy}}
    {\providecommand\boldsymbol[1]{\mbox{\boldmath $##1$}}}
\fi

%%% Example macros (some are not used in this sample file) %%%

% For units of measure
\newcommand\dynpercm{\nobreak\mbox{$\;$dyn\,cm$^{-1}$}}
\newcommand\cmpermin{\nobreak\mbox{$\;$cm\,min$^{-1}$}}

% Various bold symbols
\providecommand\bnabla{\boldsymbol{\nabla}}
\providecommand\bcdot{\boldsymbol{\cdot}}
\newcommand\biS{\boldsymbol{S}}
\newcommand\etb{\boldsymbol{\eta}}

% For multiletter symbols
\newcommand\Real{\mbox{Re}} % cf plain TeX's \Re and Reynolds number
\newcommand\Imag{\mbox{Im}} % cf plain TeX's \Im
\newcommand\Rey{\mbox{\textit{Re}}}  % Reynolds number
\newcommand\Pran{\mbox{\textit{Pr}}} % Prandtl number, cf TeX's \Pr product
\newcommand\Pen{\mbox{\textit{Pe}}}  % Peclet number
\newcommand\Ai{\mbox{Ai}}            % Airy function
\newcommand\Bi{\mbox{Bi}}            % Airy function

% For sans serif characters:
% The following macros are setup in JFM.cls for sans-serif fonts in text
% and math.  If you use these macros in your article, the required fonts
% will be substitued when you article is typeset by the typesetter.
%
% \textsfi, \mathsfi   : sans-serif slanted
% \textsfb, \mathsfb   : sans-serif bold
% \textsfbi, \mathsfbi : sans-serif bold slanted (doesnt exist in CM fonts)
%
% For san-serif roman use \textsf and \mathsf as normal.
%
\newcommand\ssC{\mathsf{C}}    % for sans serif C
\newcommand\sfsP{\mathsfi{P}}  % for sans serif sloping P
\newcommand\slsQ{\mathsfbi{Q}} % for sans serif bold-sloping Q

% Hat position
\newcommand\hatp{\skew3\hat{p}}      % p with hat
\newcommand\hatR{\skew3\hat{R}}      % R with hat
\newcommand\hatRR{\skew3\hat{\hatR}} % R with 2 hats
\newcommand\doubletildesigma{\skew2\tilde{\skew2\tilde{\Sigma}}}
%       italic Sigma with double tilde

% array strut to make delimiters come out right size both ends
\newsavebox{\astrutbox}
\sbox{\astrutbox}{\rule[-5pt]{0pt}{20pt}}
\newcommand{\astrut}{\usebox{\astrutbox}}

\newcommand\GaPQ{\ensuremath{G_a(P,Q)}}
\newcommand\GsPQ{\ensuremath{G_s(P,Q)}}
\newcommand\p{\ensuremath{\partial}}
\newcommand\tti{\ensuremath{\rightarrow\infty}}
\newcommand\kgd{\ensuremath{k\gamma d}}
\newcommand\shalf{\ensuremath{{\scriptstyle\frac{1}{2}}}}
\newcommand\sh{\ensuremath{^{\shalf}}}
\newcommand\smh{\ensuremath{^{-\shalf}}}
\newcommand\squart{\ensuremath{{\textstyle\frac{1}{4}}}}
\newcommand\thalf{\ensuremath{{\textstyle\frac{1}{2}}}}
\newcommand\Gat{\ensuremath{\widetilde{G_a}}}
\newcommand\ttz{\ensuremath{\rightarrow 0}}
\newcommand\ndq{\ensuremath{\frac{\mbox{$\partial$}}{\mbox{$\partial$} n_q}}}
\newcommand\sumjm{\ensuremath{\sum_{j=1}^{M}}}
\newcommand\pvi{\ensuremath{\int_0^{\infty}%
  \mskip \ifCUPmtlplainloaded -30mu\else -33mu\fi -\quad}}

\newcommand\etal{\mbox{\textit{et al.}}}
\newcommand\etc{etc.\ }
\newcommand\eg{e.g.\ }

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\title[Guidelines for authors]{Guidelines for authors and submission template}

\author[A. N. Other, H.-C. Smith and J. Q. Public]%
{Alan N. Other$^1$%
  \thanks{Email address for correspondence: jfm@damtp.cam.ac.uk},\ns
H. - C. Smith$^1$\break
and J. Q.  Public$^2$}

% NOTE: A full address must be provided: department, university/institution, town/city, zipcode/postcode, country.
\affiliation{$^1$Department of Chemical Engineering, University of America,
Somewhere, IN 12345, USA\\[\affilskip]
$^2$Department of Aerospace and Mechanical Engineering, University of
Camford, Academic Street, Camford CF3 5QL, UK}

\pubyear{2010}
\volume{650}
\pagerange{119--126}
% Do not enter received and revised dates. These will be entered by the editorial office.
\date{?; revised ?; accepted ?. - To be entered by editorial office}
%\setcounter{page}{1}
\begin{document}

\maketitle

\begin{abstract}
This file contains instructions for authors planning to submit a paper to the {\it Journal of Fluid Mechanics}. These instructions were generated in {\LaTeX} using the JFM style, so the {\LaTeX} source file can be used as a template for submissions. The present paragraph appears in the \verb}abstract} environment. All papers should feature a single-paragraph abstract of no more than 250 words, which provides a summary of the main aims and results. 
\end{abstract}

\begin{keywords}
Authors should not enter keywords on the manuscript, as these must be chosen by the author during the online submission process and will then be added during the typesetting process (see http://journals.cambridge.org/data/\linebreak[3]relatedlink/jfm-\linebreak[3]keywords.pdf for the full list)
\end{keywords}

\section{How to submit to the \textbf{\textit{Journal of Fluid Mechanics}}}
Authors must submit using the online submission and peer review system, Scholar One Manuscripts (formerly Manuscript Central) at http://mc.manuscriptcentral.com/jfm. If visiting the site for the first time, users must create a new account by clicking on `register here'. Once logged in, authors should click on the `Corresponding Author Centre', from which point a new manuscript can be submitted, with step-by-step instructions provided. Authors must at this stage specify whether the submission is a standard paper, or a {\it JFM Rapids} paper (see \S\ref{sec:filetypes} for more details). In addition, authors must specify an editor to whom the paper will be submitted from the drop-down list provided. Note that all editors exclusively deal with either standard papers or {\it JFM Rapids} (clearly indicated on the list), so please ensure that you choose an editor accordingly. Once your submission is completed you will receive an email confirmation.  Book reviews should not be submitted via the online submission site and should instead be submitted by email to c.p.caulfield@damtp.cam.ac.uk.

\section{Rules of submission}\label{sec:rules_submission}
Submission of a paper implies a declaration by the author that the work has not previously been published, that it is not being considered for publication elsewhere and that it has not already been considered by a different editor of the Journal. Note that a report on a conference must be submitted within 3 months of the meeting.

\section{Types of paper}\label{sec:types_paper}
\subsection{Standard papers}
Regular submissions to JFM are termed `standard papers'. Note that such papers must contain original research, as review articles are not published in JFM. Papers should be written in a concise manner; though JFM has no page limit, each paper will be judged on its own merits, and those deemed excessive in length will be rejected or will require significant revision.  
\subsection{JFM Rapids}
{\it JFM Rapids} is an evolution of the Fast Track scheme, and is devoted to the rapid publication of short, high-impact papers across the full range of fluid mechanics. {\it Rapids}  must occupy 10 or fewer printed pages, and must be submitted in {\LaTeX} using the jfm.cls class file, so as to ensure that they meet the page limit and to expedite their production.  The principal and over-riding objective is to publish papers of the highest scientific quality. Once a paper is submitted, referees are asked to provide reports with a short turnaround.  In order to be accepted for publication in {\it JFM Rapids}, such papers must require only minor revisions to improve clarity, usually without recourse to a second round of refereeing.  Where the editor, guided by the referees, judges that a paper has merit but requires substantial revision that will require significant refereeing, a decision of `revise and resubmit' will be given. On re-submission, such papers will be handled as standard JFM papers and will not subsequently appear as {\it JFM Rapids}.

{\it Rapids} will be published online within one month of final acceptance.  They will appear within a new devoted section on the Journal of Fluid Mechanics website, which has been re-designed as part of this development. Each {\it Rapid} will still be cited and indexed as a JFM article but with a distinctive {\it Rapids} identifier, and will be assigned to a JFM volume. {\it Rapids} will not be included in the regular print versions of JFM, but a collection of all {\it Rapids} will be available to order in print at the end of each year. {\it JFM Rapids} will have free colour and for the first year of operation will be freely accessible to all.

\section{File types}\label{sec:filetypes}
Authors are strongly encouraged to compose their papers in {\LaTeX}, using the jfm.cls style file and supporting files provided at http://journals.cambridge.org/\linebreak[3]data/\linebreak[3]relatedlink\linebreak[3]/jfm\linebreak[3]-ifc.zip, with the jfm-instructions.tex file serving as a template (note that this is mandatory for {\it JFM Rapids}). A PDF of the {\LaTeX} file should then be generated and submitted via the submission site. Please note that PDFs larger than 3MB are not acceptable for review. There is no need to submit the {\LaTeX} source file alongside the PDF, but upon provisional acceptance of the paper, the {\LaTeX} source file, along with individual figure files and a PDF of the final version, will need to be submitted for typesetting purposes. 
%If you require guidance on how to prepare a file in \LaTeX, please refer to the document jfm2egui.tex, which is found in the zip archive at http://journals.cambridge.org/\linebreak[3]data/\linebreak[3]relatedlink/\linebreak[3]jfm-ifc.zip. 
Authors may also compose standard papers in Word, though this will lead to the paper spending a longer period in production. If using Word, please note that equations must NOT be converted to picture format and the file must be saved with the option `make equation editable'. 
\section{Preparing your manuscript}
Authors should write their papers clearly and concisely in English, adhering to JFM's established style for notation, as provided in \S\ref{notstyle}. We encourage the submission of online supplementary material alongside the manuscript where appropriate (see section \ref{online}). Metric units should be used throughout and all abbreviations must be defined at first use, even those deemed to be well known to the readership. British spelling must be used, and should follow the \textit{Shorter Oxford English Dictionary}.

\subsection{Figures}
Figures should be as small as possible while displaying clearly all the information required, and with all lettering readable. Every effort should be taken to avoid figures that run over more than one page. Figures submitted in colour will appear online in colour but, with the exception of {\it JFM Rapids}, all figures will be printed in black and white unless authors specify during submission that figures should be printed in colour, for which there is a charge of \pounds300 for the first page and \pounds150 for each subsequent page that uses colour (colour is free for {\it JFM Rapids}).  Note that separate figures for online and print will {\bf not} be accepted and it is the author's responsibility to ensure that if a figure is to appear in colour online only, that same figure will still be meaningful when printed in black and white (for example, do not rely upon colours to distinguish lines if those colours will just appear as similar shades of grey when printed). If using colour, authors should also ensure that some consistency is applied within the manuscript. For review purposes figures should be embedded within the manuscript. Upon final acceptance, however, individual figure files will be required for production. These should be submitted in EPS or high-resolution TIFF format (1200 dpi for lines, 300 dpi for halftone and colour in CMYK format, and 600 dpi for a mixture of lines and halftone). The minimum acceptable width of any line is 0.5pt. Each figure should be accompanied by a single caption, to appear beneath, and must be cited in the text. Figures should appear in the order in which they are first mentioned in the text and figure files must be named accordingly (`Figure 1.eps', `Figure 2a.tiff', etc) to assist the production process (and numbering of figures should continue through any appendices). The word \textit {figure} is only capitalized at the start of a sentence. For example see figures \ref{fig:ka} and \ref{fig:kd}. Failure to follow figure guidelines may result in a request for resupply and a subsequent delay in the production process. Note that {\em all} figures are relabelled by the typesetter, so please ensure all figure labels are carefully checked against your originals when you receive your proofs.

\begin{figure}
  \centerline{\includegraphics{trapped.eps}}% Images in 100% size
  \caption{Trapped-mode wavenumbers, $kd$, plotted against $a/d$ for
    three ellipses:\protect\\
    ---$\!$---,
    $b/a=1$; $\cdots$\,$\cdots$, $b/a=1.5$.}
\label{fig:ka}
\end{figure}

\begin{figure}
  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
%  \centerline{\includegraphics{modes.eps}}
  \caption{The features of the four possible modes corresponding to
  (\textit{a}) periodic\protect\\ and (\textit{b}) half-periodic solutions.}
\label{fig:kd}
\end{figure}

\subsection{Tables}
Tables, however small, must be numbered sequentially in the order in which they are mentioned in the text. The word \textit {table} is only capitalized at the start of a sentence. See table \ref{tab:kd} for an example.

\begin{table}
  \begin{center}
\def~{\hphantom{0}}
  \begin{tabular}{lccc}
      $a/d$  & $M=4$   &   $M=8$ & Callan \etal \\[3pt]
       0.1   & 1.56905 & ~~1.56~ & 1.56904\\
       0.3   & 1.50484 & ~~1.504 & 1.50484\\
       0.55  & 1.39128 & ~~1.391 & 1.39131\\
       0.7   & 1.32281 & ~10.322 & 1.32288\\
       0.913 & 1.34479 & 100.351 & 1.35185\\
  \end{tabular}
  \caption{Values of $kd$ at which trapped modes occur when $\rho(\theta)=a$}
  \label{tab:kd}
  \end{center}
\end{table}

\subsection{Online supplementary material}\label{online}
Relevant material which is not suitable for print production, such as movies or numerical simulations/animations, can be uploaded as part of the initial submission. Movies should be designated as `Movie' and each individual file must be accompanied by a separate caption and a suitable title (eg Movie 1). Accepted formats are .mov, .mpg, .mp4, and .avi, though they should be archived as a .zip or .tar file before uploading. Each movie should be no more than 10MB. Upon publication these materials will then be hosted online alongside the final published article. Likewise, should there be detailed mathematical relations, tables or figures which are likely to be useful only to a few specialists or take up excessive space in the printed journal, these can also be published online as supplementary material [designated as `Other supplementary material']. Note that supplementary material is published `as is', with no further production performed.

\section{Editorial decisions}
\subsection{Revision}
If a revision is requested, you should upload revised files following the same procedure as for submitting a new paper. You begin by clicking on `Manuscripts with decision' in your Corresponding Author Center, and then on `Create a revision'. (Note that if you abandon the process before completing the submission, to continue the submission, you must click on `Revised manuscripts in draft'.) There is a new first page showing the decision letter and a space for your reply to the referee's/editor's comments. You also have the opportunity at this stage to upload your reply to the comments as a separate file. All the values filled in on original submission are displayed again. The ID number of the paper will be appended `.R1'. Also note that if a manuscript is submitted as a {\it JFM Rapid}, but requires substantial revision, it will be re-designated as a standard paper, and the ID and paper type will be amended to reflect this.

\subsection{Provisional acceptance}
If the paper is accepted as suitable for publication you will be sent a provisional acceptance decision. This enables you to upload the final files required for production:
(1) the final PDF or word version of the paper, designated as a `main document';
(2) any source files (see section \ref{sec:filetypes}) which must be designated as `production (not for review)' and uploaded as a single .zip or .tar file.

\subsection{Acceptance}
On receipt of the production files you will be sent an email indicating completion of the acceptance process.

\section{Publication process}
Once a paper has been accepted for publication and the source files have been uploaded, the manuscript will be sent to Cambridge University Press for copyediting and typesetting, and will be assigned a digital object identifier (doi). When the proof is ready, authors will receive an email alert containing a link to the PDF of the proof, and instructions for its correction and return. It is imperative that authors check their proofs closely, particularly the equations and figures, which should be checked against the accepted file, as the production schedule does not allow for corrections at a later stage. Once ready for printing, papers will be published online on Cambridge Journals Online in the current `open' volume. {\it JFM Rapids} will also be assigned to the current open volume, but will receive an article number in place of traditional pagination, as they will not appear in the print version of that volume. Each volume will be kept open for approximately two weeks, at which point it will be considered `closed', and then printed and distributed. The following volume will be immediately opened. Note that the PDF published online is the Version of Record, matching the print version, and no further alterations/corrections to this document will be allowed. The corresponding author is emailed a link to the published article when it is first published online.

\section{Obtaining help}
Technical support for the online submission system is available by clicking on the `Get Help Now' link at the top-right corner of each page of the submission site. Any other questions relating to the submission or publication process should be directed to the JFM Editorial Assistant, Mrs Amanda Johns, at jfmeditorial@cambridge.org.

\section{Notation and style}\label{notstyle}
Generally any queries concerning notation and journal style can be answered by viewing recent pages in the Journal. However, the following guide provides the key points to note. It is expected that Journal style will be followed, and authors should take care to define all variables or entities upon first use. Also note that footnotes are not normally accepted.

\subsection{Mathematical notation}
\subsubsection{Setting variables, functions, vectors, matrices etc}
{\bf Italic font} should be used for denoting variables, with multiple-letter symbols avoided except in the case of dimensionless numbers such as $\Rey$, $\Pran$ and $\Pen$ (Reynolds, Prandtl, and P\'eclet numbers respectively, which are defined as \verb}\Rey}, \verb}\Pran} and {\verb}\Pen} in the template).\\
{\bf Upright Roman font} (or upright Greek where appropriate) should be used for:\\
Operators: sin, log, d, $\Delta$, e etc.\\
Constants: i ($\sqrt{-1}$), $\upi$ (defined as \verb}\upi}), etc.\\
Functions: $\Ai$, $\Bi$ (Airy functions, defined as \verb}\Ai} and \verb}\Bi}), $\Real$ (real part, defined as \verb}\Real}), $\Imag$ (imaginary part, defined as \verb}\Imag}), etc.\\
Physical units: cm, s, etc\\
Abbreviations: c.c. (complex conjugate), h.o.t. (higher-order terms), DNS, etc.\\
{\bf Bold italic font} (or bold sloping Greek) should be used for:\\
Vectors (with the centred dot for a scalar product also in bold): $\boldsymbol{i \cdot j}$\\
{\bf Bold sloping sans serif font}, defined by the \verb}\mathsfbi} macro, should be used for:\\
Tensors and matrices: $\mathsfbi{D}$ \\
{\bf Script font} (for example $\mathcal{G}$, $\mathcal{R}$) can be used as an alternative to italic when the same letter denotes a different quantity (use \verb}\mathcal} in \LaTeX)\\
The product symbol ($\times$) should only be used to denote multiplication where an equation is broken over more than one line, to denote a cross product, or between numbers (the $\cdot$ symbol should not be used, except to denote a scalar product specifically).\\

\subsubsection{Other symbols}
A centred point should be used only for the scalar product of vectors.
Large numbers that are not scientific powers should not include commas, but have the
form 1600 or 16 000 or 160 000.
Use \textit{O} to denote `of the order of', not the \LaTeX\ $\mathcal{O}$.

\section{Citations and references}
All papers included in the References section must be cited in the article, and vice versa. Citations should be included as, for example ``It has been shown \citep{Rogallo81} that...'' (using the {\verb}\citep} command, part of the natbib package) ``recent work by \citet{Dennis85}...'' (using {\verb}\citet}).
The natbib package can be used to generate citation variations, as shown below.\\
\verb#\citet[pp. 2-4]{Hwang70}#:\\
\citet[pp. 2-4]{Hwang70} \\
\verb#\citep[p. 6]{Worster92}#:\\
\citep[p. 6]{Worster92}\\
\verb#\citep[see][]{Koch83, Lee71, Linton92}#:\\
\citep[see][]{Koch83, Lee71, Linton92}\\
\verb#\citep[see][p. 18]{Martin80}#:\\
\citep[see][p. 18]{Martin80}\\
\verb#\citep{Brownell04,Brownell07,Ursell50,Wijngaarden68,Miller91}#:\\
\citep{Brownell04,Brownell07,Ursell50,Wijngaarden68,Miller91}\\
The References section can either be built from individual \verb#\bibitem# commands, or can be built using BibTex. The BibTex files used to generate the references in this document can be found in the zip file at http://journals.cambridge.org/\linebreak[3]data/\linebreak[3]relatedlink/\linebreak[3]jfm-ifc.zip.\\

Acknowledgements should be included at the end of the paper, before the References section or any appendicies, and should be a separate paragraph without a heading. Several anonymous individuals are thanked for contributions to these instructions.

\appendix
\section{}\label{appA}
This appendix contains sample equations in the JFM style. Please refer to the {\LaTeX} source file for examples of how to display such equations in your manuscript.

\begin{equation}
  (\nabla^2+k^2)G_s=(\nabla^2+k^2)G_a=0
  \label{Helm}
\end{equation}

\begin{equation}
  \bnabla\bcdot\boldsymbol{v} = 0,\quad \nabla^{2}P=
    \bnabla\bcdot(\boldsymbol{v}\times \boldsymbol{w}).
\end{equation}

\begin{equation}
  G_s,G_a\sim 1 / (2\upi)\ln r
  \quad \mbox{as\ }\quad r\equiv|P-Q|\rightarrow 0,
  \label{singular}
\end{equation}

\begin{equation}
\left. \begin{array}{ll}  
\displaystyle\frac{\p G_s}{\p y}=0
  \quad \mbox{on\ }\quad y=0,\\[8pt]
\displaystyle  G_a=0
  \quad \mbox{on\ }\quad y=0,
 \end{array}\right\}
  \label{symbc}
\end{equation}

\begin{equation}
  -\frac{1}{2\upi} \int_0^{\infty} \gamma^{-1}[\mathrm exp(-k\gamma|y-\eta|)
   + \mathrm exp(-k\gamma(2d-y-\eta))] \cos k(x-\xi)t\:\mathrm{d} t,
   \qquad 0<y,\quad \eta<d,
\end{equation}

\begin{equation}
  \gamma(t) = \left\{
    \begin{array}{ll}
      -\mathrm{i}(1-t^2)^{1/2}, & t\le 1 \\[2pt]
      (t^2-1)^{1/2},         & t>1.
    \end{array} \right.
\end{equation}

\[
  -\frac{1}{2\upi}
   \pvi B(t)\frac{\cosh k\gamma(d-y)}{\gamma\sinh k\gamma d}
   \cos k(x-\xi)t\:\mathrm{d} t
\]

\begin{equation}
  G = -\frac{1}{4}\mathrm{i} (H_0(kr)+H_0(kr_1))
    - \frac{1}{\upi} \pvi\frac{\mathrm{e}^{-\kgd}}%
    {\gamma\sinh\kgd} \cosh k\gamma(d-y) \cosh k\gamma(d-\eta)
\end{equation}

Note that when equations are included in definitions, it may be suitable to render them in line, rather than in the equation environment: $\boldsymbol{n}_q=(-y^{\prime}(\theta),
x^{\prime}(\theta))/w(\theta)$.
Now $G_a=\squart Y_0(kr)+\Gat$ where
$r=\{[x(\theta)-x(\psi)]^2 + [y(\theta)-y(\psi)]^2\}^{1/2}$ and $\Gat$ is
regular as $kr\ttz$. However, any fractions displayed like this, other than $\thalf$ or $\squart$, must be written on the line, and not stacked (ie 1/3).

\begin{eqnarray}
  \ndq\left(\frac{1}{4} Y_0(kr)\right) & \sim &
    \frac{1}{4\upi w^3(\theta)}
    [x^{\prime\prime}(\theta)y^{\prime}(\theta)-
    y^{\prime\prime}(\theta)x^{\prime}(\theta)] \nonumber\\
  & = & \frac{1}{4\upi w^3(\theta)}
    [\rho^{\prime}(\theta)\rho^{\prime\prime}(\theta)
    - \rho^2(\theta)-2\rho^{\prime 2}(\theta)]
    \quad \mbox{as\ }\quad kr\ttz . \label{inteqpt}
\end{eqnarray}

\begin{equation}
  \frac{1}{2}\phi_i = \frac{\upi}{M} \sumjm\phi_j K_{ij}^a w_j,
  \qquad i=1,\,\ldots,\,M,
\end{equation}
where
\begin{equation}
  K_{ij}^a = \left\{
    \begin{array}{ll}
      \p G_a(\theta_i,\theta_j)/\p n_q, & i\neq j \\[2pt]
      \p\Gat(\theta_i,\theta_i)/\p n_q
      + [\rho_i^{\prime}\rho_i^{\prime\prime}-\rho_i^2-2\rho_i^{\prime 2}]
      / 4\upi w_i^3, & i=j.
  \end{array} \right.
\end{equation}

\refstepcounter{equation}
$$
  \rho_l = \lim_{\zeta \rightarrow Z^-_l(x)} \rho(x,\zeta), \quad
  \rho_{u} = \lim_{\zeta \rightarrow Z^{+}_u(x)} \rho(x,\zeta)
  \eqno{(\theequation{\mathit{a},\mathit{b}})}\label{eq35}
$$

\begin{equation}
  (\rho(x,\zeta),\phi_{\zeta\zeta}(x,\zeta))=(\rho_0,N_0)
  \quad \mbox{for}\quad Z_l(x) < \zeta < Z_u(x).
\end{equation}

\begin{subeqnarray}
  \tau_{ij} & = &
    (\overline{\overline{u}_i \overline{u}_j}
    - \overline{u}_i\overline{u}_j)
    + (\overline{\overline{u}_iu^{SGS}_j
    + u^{SGS}_i\overline{u}_j})
    + \overline{u^{SGS}_iu^{SGS}_j},\\[3pt]
  \tau^\theta_j & = &
    (\overline{\overline{u}_j\overline{\theta}}
    - \overline{u}_j \overline{\theta})
    + (\overline{\overline{u}_j\theta^{SGS}
    + u^{SGS}_j \overline{\theta}})
    + \overline{u^{SGS}_j\theta^{SGS}}.
\end{subeqnarray}

\begin{equation}
\setlength{\arraycolsep}{0pt}
\renewcommand{\arraystretch}{1.3}
\slsQ_C = \left[
\begin{array}{ccccc}
  -\omega^{-2}V'_w  &  -(\alpha^t\omega)^{-1}  &  0  &  0  &  0  \\
  \displaystyle
  \frac{\beta}{\alpha\omega^2}V'_w  &  0  &  0  &  0  &  \mathrm{i}\omega^{-1} \\
  \mathrm{i}\omega^{-1}  &  0  &  0  &  0  &  0  \\
  \displaystyle
  \mathrm{i} R^{-1}_{\delta}(\alpha^t+\omega^{-1}V''_w)  &  0
    & -(\mathrm{i}\alpha^tR_\delta)^{-1}  &  0  &  0  \\
  \displaystyle
  \frac{\mathrm{i}\beta}{\alpha\omega}R^{-1}_\delta V''_w  &  0  &  0
    &  0  & 0 \\
  (\mathrm{i}\alpha^t)^{-1}V'_w  &  (3R^{-1}_{\delta}+c^t(\mathrm{i}\alpha^t)^{-1})
    &  0  &  -(\alpha^t)^{-2}R^{-1}_{\delta}  &  0  \\
\end{array}  \right] .
\label{defQc}
\end{equation}

\begin{equation}
\etb^t = \skew2\hat{\etb}^t \exp [\mathrm{i} (\alpha^tx^t_1-\omega t)],
\end{equation}
where $\skew2\hat{\etb}^t=\boldsymbol{b}\exp (\mathrm{i}\gamma x^t_3)$. 
\begin{equation}
\mbox{Det}[\rho\omega^2\delta_{ps}-C^t_{pqrs}k^t_qk^t_r]=0,
\end{equation}

\begin{equation}
 \langle k^t_1,k^t_2,k^t_3\rangle = \langle
\alpha^t,0,\gamma\rangle  
\end{equation}

\begin{equation}
\boldsymbol{f}(\theta,\psi) = (g(\psi)\cos \theta,g(\psi) \sin \theta,f(\psi)).
\label{eq41}
\end{equation}

\begin{eqnarray}
f(\psi_1) = \frac{3b}{\upi[2(a+b \cos \psi_1)]^{{3}/{2}}}
  \int^{2\upi}_0 \frac{(\sin \psi_1 - \sin \psi)(a+b \cos \psi)^{1/2}}%
  {[1 - \cos (\psi_1 - \psi)](2+\alpha)^{1/2}}\mathrm{d}x,
\label{eq42}
\end{eqnarray}
\begin{eqnarray}
g(\psi_1) & = & \frac{3}{\upi[2(a+b \cos \psi_1)]^{{3}/{2}}}
  \int^{2\upi}_0 \left(\frac{a+b \cos \psi}{2+\alpha}\right)^{1/2}
  \left\{ \astrut f(\psi)[(\cos \psi_1 - b \beta_1)S + \beta_1P]
  \right. \nonumber\\
&& \mbox{}\times \frac{\sin \psi_1 - \sin \psi}{1-\cos(\psi_1 - \psi)}
  + g(\psi) \left[\left(2+\alpha - \frac{(\sin \psi_1 - \sin \psi)^2}
  {1- \cos (\psi - \psi_1)} - b^2 \gamma \right) S \right.\nonumber\\
&& \left.\left.\mbox{} + \left( b^2 \cos \psi_1\gamma -
  \frac{a}{b}\alpha \right) F(\frac{1}{2}\upi, \delta) - (2+\alpha)
  \cos\psi_1 E(\frac{1}{2}\upi, \delta)\right] \astrut\right\} \mathrm{d} \psi,
\label{eq43}
\end{eqnarray}
\begin{equation}
\alpha = \alpha(\psi,\psi_1) = \frac{b^2[1-\cos(\psi-\psi_1)]}%
  {(a+b\cos\psi) (a+b\cos\psi_1)},
  \quad
  \beta - \beta(\psi,\psi_1) = \frac{1-\cos(\psi-\psi_1)}{a+b\cos\psi}.
\end{equation}

\begin{equation}
\left. \begin{array}{l}
\displaystyle
H(0) = \frac{\epsilon \overline{C}_v}{\tilde{v}^{{1}/{2}}_T
(1- \beta)},\quad H'(0) = -1+\epsilon^{{2}/{3}} \overline{C}_u
+ \epsilon \skew5\hat{C}_u'; \\[16pt]
\displaystyle
H''(0) = \frac{\epsilon u^2_{\ast}}{\tilde{v}^{{1}/{2}}
_T u^2_P},\quad H' (\infty) = 0.
\end{array} \right\}
\end{equation}

\begin{lemma}

Let $f(z)$ be a trial \citet[][pp.~231--232]{Batchelor59} function defined on $[0,1]$.  Let $\varLambda_1$ denote
the ground-state eigenvalue for $-\mathrm{d}^2g/\mathrm{d} z^2=\varLambda g$,
where $g$ must satisfy $\pm\mathrm{d} g/\mathrm{d} z+\alpha g=0$ at $z=0,1$
for some non-negative constant~$\alpha$.  Then for any $f$ that is not
identically zero we have
\begin{equation}
\frac{\displaystyle
  \alpha(f^2(0)+f^2(1)) + \int_0^1 \left(
  \frac{\mathrm{d} f}{\mathrm{d} z} \right)^2 \mathrm{d} z}%
  {\displaystyle \int_0^1 f^2\mathrm{d} z}
\ge \varLambda_1 \ge
\left( \frac{-\alpha+(\alpha^2+8\upi^2\alpha)^{1/2}}{4\upi} \right)^2.
\end{equation}
\end{lemma}

\begin{corollary}
Any non-zero trial function $f$ which satisfies the boundary condition
$f(0)=f(1)=0$ always satisfies
\begin{equation}
  \int_0^1 \left( \frac{\mathrm{d} f}{\mathrm{d} z} \right)^2 \mathrm{d} z.
\end{equation}
\end{corollary}

% susie put cite commands here, don't bother with citet etc just yet.

\bibliographystyle{jfm}
% Note the spaces between the initials

\bibliography{jfm-instructions}

\end{document}

### 2013-10-22 paper/paper.tex
adding initial version of paper

%	paper.tex	Toby Searle
%	Last modified: Tue 22 Oct 13:14:21 2013
%	using jfm template

\NeedsTeXFormat{LaTeX2e}

\documentclass{jfm}

\usepackage{graphicx}
\usepackage{natbib}
%%%%%%%%%%%Added to template:
\usepackage{caption,subcaption, mathtools} % add my own packages
\graphicspath{ {./images/} }
\newcommand\Wi{\mbox{\textit{Wi}}}
\newcommand{\dt}[1]{\frac{d #1}{d t}} %time deriv
\newcommand{\dy}[1]{\frac{\partial #1}{\partial y}}
%%%%%%%%%%%%%%%

% See if the author has AMS Euler fonts installed: If they have, attempt
% to use the 'upmath' package to provide upright math.
\ifCUPmtlplainloaded \else
  \checkfont{eurm10}
  \iffontfound
    \IfFileExists{upmath.sty}
      {\typeout{^^JFound AMS Euler Roman fonts on the system,
                   using the 'upmath' package.^^J}%
       \usepackage{upmath}}
      {\typeout{^^JFound AMS Euler Roman fonts on the system, but you
                   dont seem to have the}%
       \typeout{'upmath' package installed. JFM.cls can take advantage
                 of these fonts,^^Jif you use 'upmath' package.^^J}%
       \providecommand\upi{\pi}%
      }
  \else
    \providecommand\upi{\pi}%
  \fi
\fi

% See if the author has AMS symbol fonts installed: If they have, attempt
% to use the 'amssymb' package to provide the AMS symbol characters.

\ifCUPmtlplainloaded \else
  \checkfont{msam10}
  \iffontfound
    \IfFileExists{amssymb.sty}
      {\typeout{^^JFound AMS Symbol fonts on the system, using the
                'amssymb' package.^^J}%
       \usepackage{amssymb}%
       \let\le=\leqslant  \let\leq=\leqslant
       \let\ge=\geqslant  \let\geq=\geqslant
      }{}
  \fi
\fi

% See if the author has the AMS 'amsbsy' package installed: If they have,
% use it to provide better bold math support (with \boldsymbol).

\ifCUPmtlplainloaded \else
  \IfFileExists{amsbsy.sty}
    {\typeout{^^JFound the 'amsbsy' package on the system, using it.^^J}%
     \usepackage{amsbsy}}
    {\providecommand\boldsymbol[1]{\mbox{\boldmath $##1$}}}
\fi

%%% Example macros (some are not used in this sample file) %%%

% For units of measure
\newcommand\dynpercm{\nobreak\mbox{$\;$dyn\,cm$^{-1}$}}
\newcommand\cmpermin{\nobreak\mbox{$\;$cm\,min$^{-1}$}}

% Various bold symbols
\providecommand\bnabla{\boldsymbol{\nabla}}
\providecommand\bcdot{\boldsymbol{\cdot}}
\newcommand\biS{\boldsymbol{S}}
\newcommand\etb{\boldsymbol{\eta}}

% For multiletter symbols
\newcommand\Real{\mbox{Re}} % cf plain TeX's \Re and Reynolds number
\newcommand\Imag{\mbox{Im}} % cf plain TeX's \Im
\newcommand\Rey{\mbox{\textit{Re}}}  % Reynolds number
\newcommand\Pran{\mbox{\textit{Pr}}} % Prandtl number, cf TeX's \Pr product
\newcommand\Pen{\mbox{\textit{Pe}}}  % Peclet number
\newcommand\Ai{\mbox{Ai}}            % Airy function
\newcommand\Bi{\mbox{Bi}}            % Airy function

% For sans serif characters:
% The following macros are setup in JFM.cls for sans-serif fonts in text
% and math.  If you use these macros in your article, the required fonts
% will be substitued when you article is typeset by the typesetter.
%
% \textsfi, \mathsfi   : sans-serif slanted
% \textsfb, \mathsfb   : sans-serif bold
% \textsfbi, \mathsfbi : sans-serif bold slanted (doesnt exist in CM fonts)
%
% For san-serif roman use \textsf and \mathsf as normal.
%
\newcommand\ssC{\mathsf{C}}    % for sans serif C
\newcommand\sfsP{\mathsfi{P}}  % for sans serif sloping P
\newcommand\slsQ{\mathsfbi{Q}} % for sans serif bold-sloping Q

% Hat position
\newcommand\hatp{\skew3\hat{p}}      % p with hat
\newcommand\hatR{\skew3\hat{R}}      % R with hat
\newcommand\hatRR{\skew3\hat{\hatR}} % R with 2 hats
\newcommand\doubletildesigma{\skew2\tilde{\skew2\tilde{\Sigma}}}
%       italic Sigma with double tilde

% array strut to make delimiters come out right size both ends
\newsavebox{\astrutbox}
\sbox{\astrutbox}{\rule[-5pt]{0pt}{20pt}}
\newcommand{\astrut}{\usebox{\astrutbox}}

\newcommand\GaPQ{\ensuremath{G_a(P,Q)}}
\newcommand\GsPQ{\ensuremath{G_s(P,Q)}}
\newcommand\p{\ensuremath{\partial}}
\newcommand\tti{\ensuremath{\rightarrow\infty}}
\newcommand\kgd{\ensuremath{k\gamma d}}
\newcommand\shalf{\ensuremath{{\scriptstyle\frac{1}{2}}}}
\newcommand\sh{\ensuremath{^{\shalf}}}
\newcommand\smh{\ensuremath{^{-\shalf}}}
\newcommand\squart{\ensuremath{{\textstyle\frac{1}{4}}}}
\newcommand\thalf{\ensuremath{{\textstyle\frac{1}{2}}}}
\newcommand\Gat{\ensuremath{\widetilde{G_a}}}
\newcommand\ttz{\ensuremath{\rightarrow 0}}
\newcommand\ndq{\ensuremath{\frac{\mbox{$\partial$}}{\mbox{$\partial$} n_q}}}
\newcommand\sumjm{\ensuremath{\sum_{j=1}^{M}}}
\newcommand\pvi{\ensuremath{\int_0^{\infty}%
  \mskip \ifCUPmtlplainloaded -30mu\else -33mu\fi -\quad}}

\newcommand\etal{\mbox{\textit{et al.}}}
\newcommand\etc{etc.\ }
\newcommand\eg{e.g.\ }

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\title[Viscoelastic Kelvin-Helmholtz instabilty]{Viscoelastic Kelvin-Helmholtz instability}

\author[T. W. Searle and A. N. Morozov]%
{T. W. Searle$^1$ and A. N. Morozov$^1$%
  \thanks{Email address for correspondence: jfm@damtp.cam.ac.uk},\ns
}

% NOTE: A full address must be provided: department, university/institution, town/city, zipcode/postcode, country.
\affiliation{$^1$SUPA, School of Physics and Astronomy, University of Edinburgh, Mayfield Road,
Edinburgh, EH9 3JZ, UK\\[\affilskip]
}

\pubyear{2013}
\volume{650}
\pagerange{119--126}
% Do not enter received and revised dates. These will be entered by the editorial office.
\date{?; revised ?; accepted ?. - To be entered by editorial office}
%\setcounter{page}{1}
\begin{document}

\maketitle

\begin{abstract}
  Abstract goes here. Abstract goes here. Viscoelastic Kelvin-Helmholtz instability. 
\end{abstract}

\begin{keywords}
Authors should not enter keywords on the manuscript, as these must be chosen by the author during the online submission process and will then be added during the typesetting process (see http://journals.cambridge.org/data/\linebreak[3]relatedlink/jfm-\linebreak[3]keywords.pdf for the full list)
\end{keywords}

\section{Introduction}

Turbulence without inertia in viscoelastic fluids has generated much interest since it was discovered in Taylor-Couette flow by Larson, Shaqfeh and Muller in 1990 \cite{Larson1990}. As well as this numerical and experimental study of Taylor-Couette flow, Groisman and Steinberg \cite{Groisman2000} discovered turbulence in viscoelastic fluids between two counter rotating plates.

For a long time it was thought that the elasticity of a viscoelastic fluid only served to dampen instability. It was observed that the drag in fluid could be reduced by the addition of small amounts of viscoelastic fluid. This drag reduction has been much studied over the last 70 years. However, the studies above give reason to believe that viscoelastic turbulence is present at very low Reynolds number, where it is driven by the elasticity of the polymeric fluid rather than its inertia.

In 1997 Fabian Waleffe identified a Newtonian self sustaining process in plane Couette flow \cite{Waleffe97}. Streamwise rolls redistribute the streamwise velocity into a streaky flow. This streaky flow is unstable through a Kelvin-Helmholtz instability creating a three dimensional perturbation which in turn re-energises the original streamwise rolls. This exact solution to the Navier-Stokes equations is thought to be a component of the transition to turbulence. In 1998 Waleffe constructed a bifurcation diagram for this exact solution \cite{Waleffe98} containing what looks like a bifurcation from infinity. This is the behaviour expected of the transition to turbulence in Couette flow.

Using this work in Newtonian fluid dynamics as a template for the structure of purely elastic turbulence reveals a similar pattern of streaks and, hopefully, a similar self-sustaining process. An important step towards explaining this process in purely elastic flows is establishing the mechanism by which the streaks become unstable. Presumably, this will also be a Kelvin-Helmholtz instability as the streaks shear with the rest of the fluid. To explore this mechanism in the purely elastic regime we have constructed a simple model system of a shearing viscoelastic fluid.

The Kelvin-Helmholtz instability is fundamental to Newtonian fluids, and is often integral to the transition to turbulence in these fluids. It is hoped that by finding a purely elastic version of this instability, we might be able to probe one of the important mechanisms for the transition to purely elastic turbulence.

The key dimensionless number for turbulence without inertia in Viscoelastic flows is the Weissenberg number, which is the ratio of the normal stress to the shear stress of the polymer component of the fluid $Wi = \frac{N_{1}}{\sigma}$. For small shear rates, this is approximately equivalent to $Wi \approx \lambda \dot{\gamma} = De$ where $\dot{\gamma}$ is the shear rate and $De$ is the Deborah number.

We present a linear stability analysis of the Kelvin-Helmholtz instability in the purely elastic regime using direct numerical simulation of both the Oldroyd-B and FENE-CR constitutive models for a polymeric fluid. The purely elastic fluid is found to be unstable at sufficiently high numbers of the dimensionless parameter, the Weissenberg number. The growth rate of the largest growing eigenmode of the instability is found to increase with increasing Weissenberg number for low Reynold's number. This behaviour is consistent across both the Oldroyd-B and FENE-CR models.

The system we use for our analysis uses a hyperbolic tangent shaped laminar profile for the streamwise velocity across a channel, where the instability takes place between $y = \pm \Delta$. $y=0$ is the centreline of the channel, so that if $\Delta << 1$ the flow can be said to be a free shear instability. This gives a base flow profile,
\begin{align}
    U(y) &= \tanh \left( y/\Delta \right) \coth \left( 1/\Delta \right) \nonumber\\
    V &= 0 \nonumber \\
    T_{xx}(y) &= 2 Wi \left( \dy{U} \right)^{2} \nonumber \\
    T_{xy}(y) &= \dy{U} \nonumber \\
    T_{yy}(y) &= 0 \nonumber 
    \label{eq:KH_laminar_profile}
\end{align}

We use Gauss-Labatto points in the wall-normal ($y$) direction for the base profile, and decomposed the disturbances to this flow into Fourier modes.
\begin{equation}
    g(y) = \sum\limits_{n=-N}^{N} \widetilde{g}(y) e^{ikx + \lambda t}
\end{equation}
for all disturbance variables $g = u, v, p, \tau_{i,j}$. Where $N$ is the number of Fourier modes, $k$ is the streamwise wavenumber of the disturbance and $\lambda$ is the growth rate of the mode. This code uses two domains of pseudo-spectral points to give increased resolution in the centre of the simulation. The simulation was also repeated using a code for which the system of points was stretched using:
\begin{align}
    z_{u} &= \frac{y_{u}}{1-y_{u}} \\
    z_{b} &= \frac{y_{b}}{1+y_{b}} \\
    U     &= \tanh{z/\Delta} 
    \label{eq:KH_inf_profile}
\end{align}
This system ought to be completely insensitive to the boundary conditions on the flow and so also behave as a free shear instability.

The dimensionless quantities used throughout are non-dimensionalised relative to the instability size, $\Delta$, rather than the total simulation size. The obvious reason for this is that $\Delta$ is the length scale for the free shear instability.

In order to simulate this flow, we used an Oldroyd-B fluid with very low Reynolds number $\Rey < 0.01$ and a small ratio between the solvent and total viscosities $\beta = \frac{\mu_{s}}{\mu_{s}+\mu_{p}}$. This approximates a purely elastic fluid, where the polymer contribution to the dynamics is higher than the solvent contribution. The Oldroyd-B Navier stokes and constitutive equations are then:
\begin{align}
    Re \left[ \dt{\mathbf{v}} + \mathbf{v} \cdot \nabla  \mathbf{v} \right] &= - \nabla p + \beta \nabla^{2} \mathbf{v} + \frac{1-\beta}{Wi} \nabla \cdot \mathbf{\tau} \\
    \dot{\tau}/Wi + \overset{\nabla}\tau &= \left(\nabla \mathbf{v}\right)^{T} + \nabla{\mathbf{v}}
\end{align}
With $Wi$ denoting the Weissenberg number and $\tau$ the stress in the polymeric fluid. The FENE-CR viscoelastic fluid has the advantage of being similarly easy to simulate, but also including a finite extensibility for the polymers. This leads to a stress which depends on a conformation tensor ($\mathbf{C}$) for the polymer dumbbells via a non-linear spring force:

\begin{equation}
    \mathbf{\tau} = \frac{1-\frac{3}{L^{2}}}{1 + \frac{L^{2}}{tr(\mathbf{C^{2}})}}
\end {equation}

\begin{figure}
    \centering
    \includegraphics[width=0.3\textwidth]{KH_diagram}
    \caption{diagram of the system}
    \label{fig:diagram}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{KH_dispersion}
    \caption{Example of dispersion relation for Weissenberg numbers 200, 100 and $10^{-5}$, with $\beta = 0.1$ and $\Rey = 10000$. Polymer elasticity reduces the height of the instability.}
    \label{fig:KH_growth_rate}
\end{figure}

We performed a Chebyshev decomposition of the flow in the wall-normal ($y$) direction for the base profile, and decomposed the disturbances to this flow in both Chebyshev and Fourier modes.

\begin{equation}
    g(y) = \sum\limits_{m=1}^{m=M} \widetilde{g}_{m} T_{m}(y) e^{ikx + \lambda t}
\end{equation}

for all disturbance variables $g = u, v, p, \tau_{i,j}$. Where $M$ is the number of Chebyshev modes, $T_{m}$ is the mth Chebyshev polynomial of the 1st kind, $k$ is the streamwise wavenumber of the disturbance and $\lambda$ is the growth rate of the mode.

\section{A purely elastic instability}

At low Reynolds number, low $\beta$ and sufficiently large Weissenberg number we observe an instability across a range of streamwise disturbance wavenumbers. This leads us to suppose that this instability might be a plausible reason for the instability in viscoelastic plane Couette flow, similar to that observed by Waleffe.

The instability remains unchanged under variation of $\Delta$ at low $\Delta$, proving that it is a free shear instability. Although the instability appears to require some inertia in the fluid, it is still present for  $\Rey = 0.01$  - far lower than the usual threshold of $\Rey = 1000$ for a Newtonian Kelvin-Helmholtz instability.

We see an instability grow from around $k_x \sim 0.1$ and move to lower $k_x$ as the Weissenberg number increases. The height of the instability also increases with increasing Weissenberg number.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
	\centering
	\includegraphics[width=\textwidth]{inf_purely_elastic}
	\caption{}
	\label{fig:inf_low_Re}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.48\textwidth}
	\centering
	\includegraphics[width=\textwidth]{inf_dispersions_low_Re}
	\caption{}
	\label{fig:dispersions_low_Re}
    \end{subfigure}
    \caption{a) Free shear version of the instability. Plot of the maximum growth rate against Wiessenberg number at $\Rey = 0.01$. b) Dispersion relations at various Weissenberg numbers to accompany the trend in figure a).}
\end{figure}

The dispersion relation saturates at $Wi \sim 50$ and remains approximately constant with increasing Weissenberg number. The dispersion relation for the instability remains broad in $k$ until $Wi \sim 100$ where a new eigenvector becomes dominant. At this point the old peak decreases in size and the new, much narrower, peak stays the same height. It is unclear what this means for the instability at this point.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
	\centering
	\includegraphics[width=\textwidth]{inf_vary_Re}
	\caption{}
	\label{fig:inf_low_Re}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.48\textwidth}
	\centering
	\includegraphics[width=\textwidth]{inf_dispersions_low_Wi}
	\caption{}
	\label{fig:dispersions_low_Wi}
    \end{subfigure}
    \caption{a) Free shear version of the instability. Plot of the maximum growth rate against Reynold's number with $\Wi=50$. b) Dispersion relations at various Reynold's numbers to accompany the trend in figure a).}
\end{figure}

\subsection{ Shear instability with walls}

If we examine the eigenvectors of the instability, we see that there are very large polymer stresses in the $\pm \Delta$ region. This corresponds to the large shear rate brought about as the two flows pass each other. Examining the flow field, we see that there are large vortices arranged with opposite rotational directions above and below the shear region which extend almost to the walls.

\begin{figure}
    \begin{subfigure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{psi_low_delta}
    \caption{}
    \label{fig:psi_low_delta}
    \end{subfigure}
    \vspace{1 mm}
    \begin{subfigure}[b]{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{txx_low_delta}
    \caption{}
    \label{fig:stress_low_delta}
    \end{subfigure}
    \caption{a) Streamfunction of the largest eigenfunction of the instability when $\Rey = 0.1$ and $\Wi =100$. b) xx stress for the same instability.}
\end{figure}

Dependence of the instability on the channel walls persists at very small $\Delta$. We believe that this is due to the inertial effects at low Reynold's number being so weak. This means it is very easy to move the fluid even in at a low shear rate, far from the centre of the channel. I think that the shear rate in the wall normal direction is only less than that in the streamwise direction close to the walls at low Re. The inertial effects must reduce the velocity of the fluid far from the walls so that it can feel the effect of the streamwise component of the velocity gradient.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{KH_vary_delta}
    \caption{Dispersion relations for various values of $\Delta$ at $\Rey = 0.1$, $\Wi = 100$. The sensitivity to the walls seems only to increase the strength of the instability. Even when the system is insensitive to the walls, at $\Delta= 0.0125$, there is still an instability present.}
    \label{fig:walls_dependence}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{psi_high_delta}
    \caption{Streamfunction of the eigenfunction of the instability at $\Delta = 0.1$. The magnitude is scaled by the xx stress in the centre of the channel.}
    \label{fig:psi_high_delta}
\end{figure}

All of this goes to say why it is difficult to see the instability at $\Rey = 0$. As the Reynold's number is reduced the walls become more important to the instability. In order to remove the dependence on the walls and recover a free shear instability it is necessary to move them further away. This problem gets worse at lower $\Rey$. By introducing just a very small contribution from inertia, we can remove the dependence on the walls. This is why all of our results are taken for $\Rey \leq 0.1$ on the length scale of the instability.

The reason we have have the simulation with the walls at all is because of the implications for the plane Couette problem. The Kelvin-Helmholtz instability in the Newtonian problem takes place on a length scale of about 10\% of the width of the channel, or $\Delta = 0.1$ (a guess). The viscoelastic Kelvin-Helmholtz instability is sensitive to the walls at this $\Delta$ and a $\Rey \lesssim 1$ (see figure \ref{fig:vary_Re_delta_conv}). This means that on the scale of the channel, $\Rey \gtrsim 10$ for the walls not to affect the instability. So, the important results for the purely elastic instability from the point of view of the plane Couette problem are probably those for which the walls are relevant.

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{vary_Re_delta_conv}
    \caption{The blue line is the data from the stretched code and the green line is the $\Delta = 0.1$ data. By $\Rey = 1$ it is clear that the Reynold's number is sufficient such that the walled system behaves as though it were insensitive to the walls.}
    \label{fig:vary_Re_delta_conv}
\end{figure}

At $\Delta = 0.1$ we see the same instability as that seen in the completely free case.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
	\centering
    \includegraphics[width=\textwidth]{KH_purely_elastic}
    \caption{}
    \label{fig:KH_purely_elastic}
\end{subfigure}
~
\begin{subfigure}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{KH_low_Wi_vary_Re}
    \caption{}
    \label{fig:KH_reduce_Re}
\end{subfigure}

\begin{subfigure}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{KH_low_Re_vary_Wi}
    \caption{ }
    \label{fig:KH_purely_elastic}
\end{subfigure}
~
\begin{subfigure}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{KH_onset_beta_Wi}
    \caption{}
    \label{fig:KH_elastic_onset}
\end{subfigure}
\caption{a) The change in the height of the dispersion relation as $\Wi$ is increased at $\Rey = 0$. This instability must be entirely elastic in nature. b) The change in the height of the dispersion relation as the Reynolds number is reduced at $\Wi=5$. At low $\Rey$ the instability is clearly still present for large polymer concentrations, consistent with purely elastic turbulence. c) The change in the height of the dispersion relation as $\Wi$ is increased at $\Rey = 0$. This instability must be entirely elastic in nature. d) The value of the Weissenberg number at which the velocity profile becomes unstable against $\beta$. The onset of the purely elastic instability moves to higher $Wi$ as $\beta$ increases.}
\end{figure}

\section{Confirming the model}

\subsection{Consistency of results with the FENE model}

The finite extensibility version of the model gives good agreement with the Oldroyd-B version. Shorter lengths bring about a larger instability but do not delay it to higher Weissenberg number. Otherwise similar dispersion relations are observed with a similar dependence on the distance to the walls.

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{FENE_low_Re_vary_Wi}
    \caption{Results are consistent with figure \ref{fig:KH_purely_elastic}}
    \label{fig:FENE_low_Re}
\end{figure}

\subsection{Varying width of the instability}

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{high_Re_vary_delta}
    \caption{When results are rescaled for the various delta, The instability is found to be insensitive to the width of the instability relative to the wall. At delta = 0.1, $\Rey = 10000$, $\Wi = 0.001$. 300 Gauss-Labatto points were used for each calculation.}
    \label{fig:delta_dispersion}
\end{figure}

\subsection{Drag reduction}

We see drag reduction using the Oldroyd-B model. It is not clear whether or not the maximum drag reduction asymptote is present.

\begin{figure}
%    \showthe\columnwidth %use this to determine size of figures.
    \centering
    \includegraphics[width=0.7\textwidth]{KH_high_Re_vary_Wi}
    \caption{The height of the dispersion relation is reduced for the Kelvin-Helmholtz instability as the Weissenberg number is increased. The grey dashed line is the height of the dispersion relation for the Newtonian fluid. The decrease in $\lambda_{r}$ corresponds to increased stability of the base flow and so confirms the presence of drag reduction in this system.}
    \label{fig:KH_drag_reduction}
\end{figure}

\section{Conclusions}

In conclusion, we can say that there is a Kelvin-Helmholtz like instability for purely elastic shear flows. The unstable region is much larger than that seen in Newtonian fluids relative to the region of shear. The wavenumber of the instability is much smaller in the viscoelastic case ($k<0.06$), suggesting a larger minimal flow unit is required in viscoelastic fluids. This instability is enhanced by introducing a finite extensibility to the polymers. The instability has grown to its maximum by the time it reaches an effective Weissenberg number $ Wi \sim 50$ after which it is saturated. The instability is also strongly dependent on the walls at low effective Reynold's number.

\bibliographystyle{jfm}
% Note the spaces between the initials

%\bibliography{jfm-instructions}

\end{document}

### 2013-10-22 paper/paper_draft131021.tex
adding initial version of paper

--- 2013-10-22 paper/paper.tex
@@
 %	paper.tex	Toby Searle
-%	Last modified: Tue 22 Oct 13:14:21 2013
+%	Last modified: Mon  9 Sep 12:06:19 2013
 %	using jfm template
@@
 %%%%%%%%%%%Added to template:
-\usepackage{caption,subcaption, mathtools} % add my own packages
+\usepackage{mathtools} % add my own packages
 \graphicspath{ {./images/} }
 \newcommand\Wi{\mbox{\textit{Wi}}}
-\newcommand{\dt}[1]{\frac{d #1}{d t}} %time deriv
-\newcommand{\dy}[1]{\frac{\partial #1}{\partial y}}
 %%%%%%%%%%%%%%%
@@
 
-Turbulence without inertia in viscoelastic fluids has generated much interest since it was discovered in Taylor-Couette flow by Larson, Shaqfeh and Muller in 1990 \cite{Larson1990}.
+Fairly recently, a turbulent state has been discovered in viscoelastic fluids.
+There is both experimental and theoretical evidence for this.
+Larson, Shaqfeh and Muller discovered evidence of wavy vortex coherent states in Taylor-Couette flow of a boger viscoelastic fluid at very low Reynolds number \cite{Larson1990}.
 As well as this numerical and experimental study of Taylor-Couette flow, Groisman and Steinberg \cite{Groisman2000} discovered turbulence in viscoelastic fluids between two counter rotating plates.
@@
 Using this work in Newtonian fluid dynamics as a template for the structure of purely elastic turbulence reveals a similar pattern of streaks and, hopefully, a similar self-sustaining process.
-An important step towards explaining this process in purely elastic flows is establishing the mechanism by which the streaks become unstable.
-Presumably, this will also be a Kelvin-Helmholtz instability as the streaks shear with the rest of the fluid.
-To explore this mechanism in the purely elastic regime we have constructed a simple model system of a shearing viscoelastic fluid.
+An important step on the path to explaining this process in purely elastic flows is establishing the mechanism by which the streaks become unstable.
+Presumably, this will also be a Kelvin-Helmholtz instability as the streaks shear past the rest of the fluid.
+For this aim we have constructed this simple model system of a shearing viscoelastic fluid.
 
-The Kelvin-Helmholtz instability is fundamental to Newtonian fluids, and is often integral to the transition to turbulence in these fluids.
+The Kelvin-Helmholtz instability is fundemental to Newtonian fluids, and is often a source for the transition to turbulence in these fluids.
 It is hoped that by finding a purely elastic version of this instability, we might be able to probe one of the important mechanisms for the transition to purely elastic turbulence.
 
-The key dimensionless number for turbulence without inertia in Viscoelastic flows is the Weissenberg number, which is the ratio of the normal stress to the shear stress of the polymer component of the fluid $Wi = \frac{N_{1}}{\sigma}$.
-For small shear rates, this is approximately equivalent to $Wi \approx \lambda \dot{\gamma} = De$ where $\dot{\gamma}$ is the shear rate and $De$ is the Deborah number.
-
-We present a linear stability analysis of the Kelvin-Helmholtz instability in the purely elastic regime using direct numerical simulation of both the Oldroyd-B and FENE-CR constitutive models for a polymeric fluid.
+We present a linear stability analysis of the Kelvin-Helmholtz instability in the purely elastic regime using direct numerical simulation of both the Oldroyd-B and FENE-CR constituitive models for a polymeric fluid.
 The purely elastic fluid is found to be unstable at sufficiently high numbers of the dimensionless parameter, the Weissenberg number.
-The growth rate of the largest growing eigenmode of the instability is found to increase with increasing Weissenberg number for low Reynold's number.
+The growth rate of the largest growing eigenmode of the instability is found to increase with increasing Weissenberg number for low Weissenberg number.
 This behaviour is consistent across both the Oldroyd-B and FENE-CR models.
 
-The system we use for our analysis uses a hyperbolic tangent shaped laminar profile for the streamwise velocity across a channel, where the instability takes place between $y = \pm \Delta$.
-$y=0$ is the centreline of the channel, so that if $\Delta << 1$ the flow can be said to be a free shear instability.
-This gives a base flow profile,
+The system we use for our analysis uses a $\tanh$ shaped laminar profile for the streamwise velocity across a plane Couette flow channel, where the instability takes place about $y=0$ as seen in (figure \ref{fig:diagram}).
+The equation used was:
+
 \begin{align}
-    U(y) &= \tanh \left( y/\Delta \right) \coth \left( 1/\Delta \right) \nonumber\\
-    V &= 0 \nonumber \\
-    T_{xx}(y) &= 2 Wi \left( \dy{U} \right)^{2} \nonumber \\
-    T_{xy}(y) &= \dy{U} \nonumber \\
-    T_{yy}(y) &= 0 \nonumber 
+    U &= \tanh \left( y/\Delta \right) \coth \left( 1/\Delta \right) \\
+    V &= 0 
     \label{eq:KH_laminar_profile}
@@
 
-We use Gauss-Labatto points in the wall-normal ($y$) direction for the base profile, and decomposed the disturbances to this flow into Fourier modes.
-\begin{equation}
-    g(y) = \sum\limits_{n=-N}^{N} \widetilde{g}(y) e^{ikx + \lambda t}
-\end{equation}
-for all disturbance variables $g = u, v, p, \tau_{i,j}$.
-Where $N$ is the number of Fourier modes, $k$ is the streamwise wavenumber of the disturbance and $\lambda$ is the growth rate of the mode.
-This code uses two domains of pseudo-spectral points to give increased resolution in the centre of the simulation.
-The simulation was also repeated using a code for which the system of points was stretched using:
-\begin{align}
-    z_{u} &= \frac{y_{u}}{1-y_{u}} \\
-    z_{b} &= \frac{y_{b}}{1+y_{b}} \\
-    U     &= \tanh{z/\Delta} 
-    \label{eq:KH_inf_profile}
-\end{align}
-This system ought to be completely insensitive to the boundary conditions on the flow and so also behave as a free shear instability.
-
-The dimensionless quantities used throughout are non-dimensionalised relative to the instability size, $\Delta$, rather than the total simulation size.
-The obvious reason for this is that $\Delta$ is the length scale for the free shear instability.
-
-In order to simulate this flow, we used an Oldroyd-B fluid with very low Reynolds number $\Rey < 0.01$ and a small ratio between the solvent and total viscosities $\beta = \frac{\mu_{s}}{\mu_{s}+\mu_{p}}$.
-This approximates a purely elastic fluid, where the polymer contribution to the dynamics is higher than the solvent contribution.
-The Oldroyd-B Navier stokes and constitutive equations are then:
-\begin{align}
-    Re \left[ \dt{\mathbf{v}} + \mathbf{v} \cdot \nabla  \mathbf{v} \right] &= - \nabla p + \beta \nabla^{2} \mathbf{v} + \frac{1-\beta}{Wi} \nabla \cdot \mathbf{\tau} \\
-    \dot{\tau}/Wi + \overset{\nabla}\tau &= \left(\nabla \mathbf{v}\right)^{T} + \nabla{\mathbf{v}}
-\end{align}
-With $Wi$ denoting the Weissenberg number and $\tau$ the stress in the polymeric fluid.
-The FENE-CR viscoelastic fluid has the advantage of being similarly easy to simulate, but also including a finite extensibility for the polymers.
-This leads to a stress which depends on a conformation tensor ($\mathbf{C}$) for the polymer dumbbells via a non-linear spring force:
-
-\begin{equation}
-    \mathbf{\tau} = \frac{1-\frac{3}{L^{2}}}{1 + \frac{L^{2}}{tr(\mathbf{C^{2}})}}
-\end {equation}
-
 \begin{figure}
     \centering
-    \includegraphics[width=0.3\textwidth]{KH_diagram}
+    \includegraphics[width=0.6\textwidth]{KH_diagram}
     \caption{diagram of the system}
@@
 
-At low Reynolds number, low $\beta$ and sufficiently large Weissenberg number we observe an instability across a range of streamwise disturbance wavenumbers.
-This leads us to suppose that this instability might be a plausible reason for the instability in viscoelastic plane Couette flow, similar to that observed by Waleffe.
+For low Reynold's number and high Weissenberg number we see an instability grow from around $k_x \sim 0.1$ and move to lower $k_x$ as the Weissenberg number increases.
+The height of the instability also increases with increasing Weissenberg number.
 
-The instability remains unchanged under variation of $\Delta$ at low $\Delta$, proving that it is a free shear instability.
-Although the instability appears to require some inertia in the fluid, it is still present for  $\Rey = 0.01$  - far lower than the usual threshold of $\Rey = 1000$ for a Newtonian Kelvin-Helmholtz instability.
-
-We see an instability grow from around $k_x \sim 0.1$ and move to lower $k_x$ as the Weissenberg number increases. The height of the instability also increases with increasing Weissenberg number.
+At this point we are unsure as to why the instability is being supressed at high Weissenberg number.
 
 \begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{inf_purely_elastic}
-	\caption{}
-	\label{fig:inf_low_Re}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.48\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{inf_dispersions_low_Re}
-	\caption{}
-	\label{fig:dispersions_low_Re}
-    \end{subfigure}
-    \caption{a) Free shear version of the instability.
-Plot of the maximum growth rate against Wiessenberg number at $\Rey = 0.01$.
-b) Dispersion relations at various Weissenberg numbers to accompany the trend in figure a).}
+    \includegraphics[width=\textwidth]{KH_low_Wi_vary_Re}
+    \caption{The change in the height of the dispersion relation as the Reynolds number is reduced at $\Wi=5$.
+At low $\Rey$ the instability is clearly still present for large polymer concentrations, consistent with purely elastic turbulence.
+}
+    \label{fig:KH_reduce_Re}
 \end{figure}
-
-The dispersion relation saturates at $Wi \sim 50$ and remains approximately constant with increasing Weissenberg number.
-The dispersion relation for the instability remains broad in $k$ until $Wi \sim 100$ where a new eigenvector becomes dominant.
-At this point the old peak decreases in size and the new, much narrower, peak stays the same height.
-It is unclear what this means for the instability at this point.
-
 \begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{inf_vary_Re}
-	\caption{}
-	\label{fig:inf_low_Re}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.48\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{inf_dispersions_low_Wi}
-	\caption{}
-	\label{fig:dispersions_low_Wi}
-    \end{subfigure}
-    \caption{a) Free shear version of the instability.
-Plot of the maximum growth rate against Reynold's number with $\Wi=50$.
-b) Dispersion relations at various Reynold's numbers to accompany the trend in figure a).}
+    \includegraphics[width=\textwidth]{KH_low_Re_vary_Wi}
+    \caption{The change in the height of the dispersion relation as $\Wi$ is increased at $\Rey = 0$. This instability must be entirely elastic in nature. }
+    \label{fig:KH_purely_elastic}
 \end{figure}
-
-\subsection{ Shear instability with walls}
-
-If we examine the eigenvectors of the instability, we see that there are very large polymer stresses in the $\pm \Delta$ region.
-This corresponds to the large shear rate brought about as the two flows pass each other.
-Examining the flow field, we see that there are large vortices arranged with opposite rotational directions above and below the shear region which extend almost to the walls.
-
 \begin{figure}
-    \begin{subfigure}[b]{\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{psi_low_delta}
-    \caption{}
-    \label{fig:psi_low_delta}
-    \end{subfigure}
-    \vspace{1 mm}
-    \begin{subfigure}[b]{\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{txx_low_delta}
-    \caption{}
-    \label{fig:stress_low_delta}
-    \end{subfigure}
-    \caption{a) Streamfunction of the largest eigenfunction of the instability when $\Rey = 0.1$ and $\Wi =100$. b) xx stress for the same instability.}
-\end{figure}
-
-Dependence of the instability on the channel walls persists at very small $\Delta$.
-We believe that this is due to the inertial effects at low Reynold's number being so weak.
-This means it is very easy to move the fluid even in at a low shear rate, far from the centre of the channel.
-I think that the shear rate in the wall normal direction is only less than that in the streamwise direction close to the walls at low Re.
-The inertial effects must reduce the velocity of the fluid far from the walls so that it can feel the effect of the streamwise component of the velocity gradient.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{KH_vary_delta}
-    \caption{Dispersion relations for various values of $\Delta$ at $\Rey = 0.1$, $\Wi = 100$.
-The sensitivity to the walls seems only to increase the strength of the instability.
-Even when the system is insensitive to the walls, at $\Delta= 0.0125$, there is still an instability present.}
-    \label{fig:walls_dependence}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{psi_high_delta}
-    \caption{Streamfunction of the eigenfunction of the instability at $\Delta = 0.1$. The magnitude is scaled by the xx stress in the centre of the channel.}
-    \label{fig:psi_high_delta}
-\end{figure}
-
-All of this goes to say why it is difficult to see the instability at $\Rey = 0$.
-As the Reynold's number is reduced the walls become more important to the instability.
-In order to remove the dependence on the walls and recover a free shear instability it is necessary to move them further away.
-This problem gets worse at lower $\Rey$.
-By introducing just a very small contribution from inertia, we can remove the dependence on the walls.
-This is why all of our results are taken for $\Rey \leq 0.1$ on the length scale of the instability.
-
-The reason we have have the simulation with the walls at all is because of the implications for the plane Couette problem.
-The Kelvin-Helmholtz instability in the Newtonian problem takes place on a length scale of about 10\% of the width of the channel, or $\Delta = 0.1$ (a guess).
-The viscoelastic Kelvin-Helmholtz instability is sensitive to the walls at this $\Delta$ and a $\Rey \lesssim 1$ (see figure \ref{fig:vary_Re_delta_conv}).
-This means that on the scale of the channel, $\Rey \gtrsim 10$ for the walls not to affect the instability.
-So, the important results for the purely elastic instability from the point of view of the plane Couette problem are probably those for which the walls are relevant.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\textwidth]{vary_Re_delta_conv}
-    \caption{The blue line is the data from the stretched code and the green line is the $\Delta = 0.1$ data.
-By $\Rey = 1$ it is clear that the Reynold's number is sufficient such that the walled system behaves as though it were insensitive to the walls.}
-    \label{fig:vary_Re_delta_conv}
-\end{figure}
-
-At $\Delta = 0.1$ we see the same instability as that seen in the completely free case.
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-	\centering
-    \includegraphics[width=\textwidth]{KH_purely_elastic}
-    \caption{}
-    \label{fig:KH_purely_elastic}
-\end{subfigure}
-~
-\begin{subfigure}[b]{0.48\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{KH_low_Wi_vary_Re}
-    \caption{}
-    \label{fig:KH_reduce_Re}
-\end{subfigure}
-
-\begin{subfigure}[b]{0.48\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{KH_low_Re_vary_Wi}
-    \caption{ }
-    \label{fig:KH_purely_elastic}
-\end{subfigure}
-~
-\begin{subfigure}[b]{0.48\textwidth}
-    \centering
     \includegraphics[width=\textwidth]{KH_onset_beta_Wi}
-    \caption{}
+    \caption{The value of the Weissenberg number at which the velocity profile becomes unstable against $\beta$. The onset of the purely elastic instability moves to higher $Wi$ as $\beta$ increases.}
     \label{fig:KH_elastic_onset}
-\end{subfigure}
-\caption{a) The change in the height of the dispersion relation as $\Wi$ is increased at $\Rey = 0$.
-This instability must be entirely elastic in nature.
-b) The change in the height of the dispersion relation as the Reynolds number is reduced at $\Wi=5$.
-At low $\Rey$ the instability is clearly still present for large polymer concentrations, consistent with purely elastic turbulence.
-c) The change in the height of the dispersion relation as $\Wi$ is increased at $\Rey = 0$.
-This instability must be entirely elastic in nature.
-d) The value of the Weissenberg number at which the velocity profile becomes unstable against $\beta$.
-The onset of the purely elastic instability moves to higher $Wi$ as $\beta$ increases.}
 \end{figure}
@@
 \subsection{Consistency of results with the FENE model}
-
-The finite extensibility version of the model gives good agreement with the Oldroyd-B version.
-Shorter lengths bring about a larger instability but do not delay it to higher Weissenberg number.
-Otherwise similar dispersion relations are observed with a similar dependence on the distance to the walls.
-
 \begin{figure}
-    \centering
-    \includegraphics[width=0.7\textwidth]{FENE_low_Re_vary_Wi}
+    \includegraphics[width=\textwidth]{FENE_low_Re_vary_Wi}
     \caption{Results are consistent with figure \ref{fig:KH_purely_elastic}}
@@
 \begin{figure}
-    \centering
-    \includegraphics[width=0.7\textwidth]{high_Re_vary_delta}
+    \includegraphics[width=\textwidth]{high_Re_vary_delta}
     \caption{When results are rescaled for the various delta, The instability is found to be insensitive to the width of the instability relative to the wall.
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{KH_high_Re_vary_Wi}
+    \includegraphics[width=\textwidth]{KH_high_Re_vary_Wi}
     \caption{The height of the dispersion relation is reduced for the Kelvin-Helmholtz instability as the Weissenberg number is increased.
@@
 
-In conclusion, we can say that there is a Kelvin-Helmholtz like instability for purely elastic shear flows.
-The unstable region is much larger than that seen in Newtonian fluids relative to the region of shear.
-The wavenumber of the instability is much smaller in the viscoelastic case ($k<0.06$), suggesting a larger minimal flow unit is required in viscoelastic fluids.
-This instability is enhanced by introducing a finite extensibility to the polymers.
-The instability has grown to its maximum by the time it reaches an effective Weissenberg number $ Wi \sim 50$ after which it is saturated.
-The instability is also strongly dependent on the walls at low effective Reynold's number.
+What a great and useful thing to have found out. think of all the marvelous implications.
 

### 2013-10-22 paper/story/story.tex
adding initial version of paper

--- 2013-10-22 paper/paper.tex
@@
-%	paper.tex	Toby Searle
-%	Last modified: Tue 22 Oct 13:14:21 2013
-%	using jfm template
+%
+%   The Story of a Kelvin-Helmholtz like viscoelastic instability
+%   Last modified: Mon 21 Oct 11:00:34 2013
 
-\NeedsTeXFormat{LaTeX2e}
-
-\documentclass{jfm}
-
-\usepackage{graphicx}
-\usepackage{natbib}
-%%%%%%%%%%%Added to template:
-\usepackage{caption,subcaption, mathtools} % add my own packages
-\graphicspath{ {./images/} }
-\newcommand\Wi{\mbox{\textit{Wi}}}
+%   PREAMBLE:
+\documentclass{article}
+\usepackage{amsmath, amssymb}
+%   MY MATH MACROS 
 \newcommand{\dt}[1]{\frac{d #1}{d t}} %time deriv
 \newcommand{\dy}[1]{\frac{\partial #1}{\partial y}}
-%%%%%%%%%%%%%%%
 
-% See if the author has AMS Euler fonts installed: If they have, attempt
-% to use the 'upmath' package to provide upright math.
-\ifCUPmtlplainloaded \else
-  \checkfont{eurm10}
-  \iffontfound
-    \IfFileExists{upmath.sty}
-      {\typeout{^^JFound AMS Euler Roman fonts on the system,
-                   using the 'upmath' package.^^J}%
-       \usepackage{upmath}}
-      {\typeout{^^JFound AMS Euler Roman fonts on the system, but you
-                   dont seem to have the}%
-       \typeout{'upmath' package installed. JFM.cls can take advantage
-                 of these fonts,^^Jif you use 'upmath' package.^^J}%
-       \providecommand\upi{\pi}%
-      }
-  \else
-    \providecommand\upi{\pi}%
-  \fi
-\fi
-
-% See if the author has AMS symbol fonts installed: If they have, attempt
-% to use the 'amssymb' package to provide the AMS symbol characters.
-
-\ifCUPmtlplainloaded \else
-  \checkfont{msam10}
-  \iffontfound
-    \IfFileExists{amssymb.sty}
-      {\typeout{^^JFound AMS Symbol fonts on the system, using the
-                'amssymb' package.^^J}%
-       \usepackage{amssymb}%
-       \let\le=\leqslant  \let\leq=\leqslant
-       \let\ge=\geqslant  \let\geq=\geqslant
-      }{}
-  \fi
-\fi
-
-% See if the author has the AMS 'amsbsy' package installed: If they have,
-% use it to provide better bold math support (with \boldsymbol).
-
-\ifCUPmtlplainloaded \else
-  \IfFileExists{amsbsy.sty}
-    {\typeout{^^JFound the 'amsbsy' package on the system, using it.^^J}%
-     \usepackage{amsbsy}}
-    {\providecommand\boldsymbol[1]{\mbox{\boldmath $##1$}}}
-\fi
-
-%%% Example macros (some are not used in this sample file) %%%
-
-% For units of measure
-\newcommand\dynpercm{\nobreak\mbox{$\;$dyn\,cm$^{-1}$}}
-\newcommand\cmpermin{\nobreak\mbox{$\;$cm\,min$^{-1}$}}
-
-% Various bold symbols
-\providecommand\bnabla{\boldsymbol{\nabla}}
-\providecommand\bcdot{\boldsymbol{\cdot}}
-\newcommand\biS{\boldsymbol{S}}
-\newcommand\etb{\boldsymbol{\eta}}
-
-% For multiletter symbols
-\newcommand\Real{\mbox{Re}} % cf plain TeX's \Re and Reynolds number
-\newcommand\Imag{\mbox{Im}} % cf plain TeX's \Im
-\newcommand\Rey{\mbox{\textit{Re}}}  % Reynolds number
-\newcommand\Pran{\mbox{\textit{Pr}}} % Prandtl number, cf TeX's \Pr product
-\newcommand\Pen{\mbox{\textit{Pe}}}  % Peclet number
-\newcommand\Ai{\mbox{Ai}}            % Airy function
-\newcommand\Bi{\mbox{Bi}}            % Airy function
-
-% For sans serif characters:
-% The following macros are setup in JFM.cls for sans-serif fonts in text
-% and math.  If you use these macros in your article, the required fonts
-% will be substitued when you article is typeset by the typesetter.
-%
-% \textsfi, \mathsfi   : sans-serif slanted
-% \textsfb, \mathsfb   : sans-serif bold
-% \textsfbi, \mathsfbi : sans-serif bold slanted (doesnt exist in CM fonts)
-%
-% For san-serif roman use \textsf and \mathsf as normal.
-%
-\newcommand\ssC{\mathsf{C}}    % for sans serif C
-\newcommand\sfsP{\mathsfi{P}}  % for sans serif sloping P
-\newcommand\slsQ{\mathsfbi{Q}} % for sans serif bold-sloping Q
-
-% Hat position
-\newcommand\hatp{\skew3\hat{p}}      % p with hat
-\newcommand\hatR{\skew3\hat{R}}      % R with hat
-\newcommand\hatRR{\skew3\hat{\hatR}} % R with 2 hats
-\newcommand\doubletildesigma{\skew2\tilde{\skew2\tilde{\Sigma}}}
-%       italic Sigma with double tilde
-
-% array strut to make delimiters come out right size both ends
-\newsavebox{\astrutbox}
-\sbox{\astrutbox}{\rule[-5pt]{0pt}{20pt}}
-\newcommand{\astrut}{\usebox{\astrutbox}}
-
-\newcommand\GaPQ{\ensuremath{G_a(P,Q)}}
-\newcommand\GsPQ{\ensuremath{G_s(P,Q)}}
-\newcommand\p{\ensuremath{\partial}}
-\newcommand\tti{\ensuremath{\rightarrow\infty}}
-\newcommand\kgd{\ensuremath{k\gamma d}}
-\newcommand\shalf{\ensuremath{{\scriptstyle\frac{1}{2}}}}
-\newcommand\sh{\ensuremath{^{\shalf}}}
-\newcommand\smh{\ensuremath{^{-\shalf}}}
-\newcommand\squart{\ensuremath{{\textstyle\frac{1}{4}}}}
-\newcommand\thalf{\ensuremath{{\textstyle\frac{1}{2}}}}
-\newcommand\Gat{\ensuremath{\widetilde{G_a}}}
-\newcommand\ttz{\ensuremath{\rightarrow 0}}
-\newcommand\ndq{\ensuremath{\frac{\mbox{$\partial$}}{\mbox{$\partial$} n_q}}}
-\newcommand\sumjm{\ensuremath{\sum_{j=1}^{M}}}
-\newcommand\pvi{\ensuremath{\int_0^{\infty}%
-  \mskip \ifCUPmtlplainloaded -30mu\else -33mu\fi -\quad}}
-
-\newcommand\etal{\mbox{\textit{et al.}}}
-\newcommand\etc{etc.\ }
-\newcommand\eg{e.g.\ }
-
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-
-\title[Viscoelastic Kelvin-Helmholtz instabilty]{Viscoelastic Kelvin-Helmholtz instability}
-
-\author[T. W. Searle and A. N. Morozov]%
-{T. W. Searle$^1$ and A. N. Morozov$^1$%
-  \thanks{Email address for correspondence: jfm@damtp.cam.ac.uk},\ns
-}
-
-% NOTE: A full address must be provided: department, university/institution, town/city, zipcode/postcode, country.
-\affiliation{$^1$SUPA, School of Physics and Astronomy, University of Edinburgh, Mayfield Road,
-Edinburgh, EH9 3JZ, UK\\[\affilskip]
-}
-
-\pubyear{2013}
-\volume{650}
-\pagerange{119--126}
-% Do not enter received and revised dates. These will be entered by the editorial office.
-\date{?; revised ?; accepted ?. - To be entered by editorial office}
-%\setcounter{page}{1}
 \begin{document}
+\title{Viscoelastic Kelvin-Helmholtz instability}
 
 \maketitle
-
-\begin{abstract}
-  Abstract goes here. Abstract goes here. Viscoelastic Kelvin-Helmholtz instability. 
-\end{abstract}
-
-\begin{keywords}
-Authors should not enter keywords on the manuscript, as these must be chosen by the author during the online submission process and will then be added during the typesetting process (see http://journals.cambridge.org/data/\linebreak[3]relatedlink/jfm-\linebreak[3]keywords.pdf for the full list)
-\end{keywords}
-
-\section{Introduction}
 
@@
 
-In order to simulate this flow, we used an Oldroyd-B fluid with very low Reynolds number $\Rey < 0.01$ and a small ratio between the solvent and total viscosities $\beta = \frac{\mu_{s}}{\mu_{s}+\mu_{p}}$.
+In order to simulate this flow, we used an Oldroyd-B fluid with very low Reynolds number $Re < 0.01$ and a small ratio between the solvent and total viscosities $\beta = \frac{\mu_{s}}{\mu_{s}+\mu_{p}}$.
 This approximates a purely elastic fluid, where the polymer contribution to the dynamics is higher than the solvent contribution.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.3\textwidth]{KH_diagram}
-    \caption{diagram of the system}
-    \label{fig:diagram}
-\end{figure}
+\section{Drag reduction}
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{KH_dispersion}
-    \caption{Example of dispersion relation for Weissenberg numbers 200, 100 and $10^{-5}$, with $\beta = 0.1$ and $\Rey = 10000$. Polymer elasticity reduces the height of the instability.}
-    \label{fig:KH_growth_rate}
-\end{figure}
+We see a reduction in the height of the instability with increasing Weissenberg number at high Reynolds number and high $\beta$.
+This is consistent with the addition of a small amount of polymeric fluid reducing the instability of a Newtonian Kelvin-Helmholtz flow.
+Presumably, this would bring about drag reduction on the walls and delay the onset of the turbulence to larger Reynold's number.
+This is further confirming evidence for the model when the Reynold's number is high.
 
-We performed a Chebyshev decomposition of the flow in the wall-normal ($y$) direction for the base profile, and decomposed the disturbances to this flow in both Chebyshev and Fourier modes.
-
-\begin{equation}
-    g(y) = \sum\limits_{m=1}^{m=M} \widetilde{g}_{m} T_{m}(y) e^{ikx + \lambda t}
-\end{equation}
-
-for all disturbance variables $g = u, v, p, \tau_{i,j}$.
-Where $M$ is the number of Chebyshev modes, $T_{m}$ is the mth Chebyshev polynomial of the 1st kind, $k$ is the streamwise wavenumber of the disturbance and $\lambda$ is the growth rate of the mode.
-
-\section{A purely elastic instability}
+\section{The Purely Elastic Instability}
 
@@
 The instability remains unchanged under variation of $\Delta$ at low $\Delta$, proving that it is a free shear instability.
-Although the instability appears to require some inertia in the fluid, it is still present for  $\Rey = 0.01$  - far lower than the usual threshold of $\Rey = 1000$ for a Newtonian Kelvin-Helmholtz instability.
+Although the instability appears to require some inertia in the fluid, it is still present for  $Re = 0.01$  - far lower than the usual threshold of $Re = 1000$ for a Newtonian Kelvin-Helmholtz instability.
 
-We see an instability grow from around $k_x \sim 0.1$ and move to lower $k_x$ as the Weissenberg number increases. The height of the instability also increases with increasing Weissenberg number.
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{inf_purely_elastic}
-	\caption{}
-	\label{fig:inf_low_Re}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.48\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{inf_dispersions_low_Re}
-	\caption{}
-	\label{fig:dispersions_low_Re}
-    \end{subfigure}
-    \caption{a) Free shear version of the instability.
-Plot of the maximum growth rate against Wiessenberg number at $\Rey = 0.01$.
-b) Dispersion relations at various Weissenberg numbers to accompany the trend in figure a).}
-\end{figure}
+We found that the instability sets in at approximately $Wi = 15$ for $\beta = 0.1$, and that this onset Weissenberg number stays the same up to about $\beta = 0.6$ after which it quickly rises.
+This suggests that there is a concentration of polymers required in the fluid in order to enable the viscoelastic version of the instability.
 
@@
 
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{inf_vary_Re}
-	\caption{}
-	\label{fig:inf_low_Re}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.48\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{inf_dispersions_low_Wi}
-	\caption{}
-	\label{fig:dispersions_low_Wi}
-    \end{subfigure}
-    \caption{a) Free shear version of the instability.
-Plot of the maximum growth rate against Reynold's number with $\Wi=50$.
-b) Dispersion relations at various Reynold's numbers to accompany the trend in figure a).}
-\end{figure}
-
-\subsection{ Shear instability with walls}
-
 If we examine the eigenvectors of the instability, we see that there are very large polymer stresses in the $\pm \Delta$ region.
 This corresponds to the large shear rate brought about as the two flows pass each other.
-Examining the flow field, we see that there are large vortices arranged with opposite rotational directions above and below the shear region which extend almost to the walls.
+Examining the flow field, we see that there are large vortices arranged with opposite rotational directions above and below the shear region.
 
-\begin{figure}
-    \begin{subfigure}[b]{\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{psi_low_delta}
-    \caption{}
-    \label{fig:psi_low_delta}
-    \end{subfigure}
-    \vspace{1 mm}
-    \begin{subfigure}[b]{\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{txx_low_delta}
-    \caption{}
-    \label{fig:stress_low_delta}
-    \end{subfigure}
-    \caption{a) Streamfunction of the largest eigenfunction of the instability when $\Rey = 0.1$ and $\Wi =100$. b) xx stress for the same instability.}
-\end{figure}
+\section{Varying the distance of the channel walls}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{KH_vary_delta}
-    \caption{Dispersion relations for various values of $\Delta$ at $\Rey = 0.1$, $\Wi = 100$.
-The sensitivity to the walls seems only to increase the strength of the instability.
-Even when the system is insensitive to the walls, at $\Delta= 0.0125$, there is still an instability present.}
-    \label{fig:walls_dependence}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{psi_high_delta}
-    \caption{Streamfunction of the eigenfunction of the instability at $\Delta = 0.1$. The magnitude is scaled by the xx stress in the centre of the channel.}
-    \label{fig:psi_high_delta}
-\end{figure}
-
-All of this goes to say why it is difficult to see the instability at $\Rey = 0$.
+All of this goes to say why it is difficult to see the instability at $Re = 0$.
 As the Reynold's number is reduced the walls become more important to the instability.
 In order to remove the dependence on the walls and recover a free shear instability it is necessary to move them further away.
-This problem gets worse at lower $\Rey$.
+This problem gets worse at lower $Re$.
 By introducing just a very small contribution from inertia, we can remove the dependence on the walls.
-This is why all of our results are taken for $\Rey \leq 0.1$ on the length scale of the instability.
+This is why all of our results are taken for $\Re \leq 0.1$ on the length scale of the instability.
 
 The reason we have have the simulation with the walls at all is because of the implications for the plane Couette problem.
-The Kelvin-Helmholtz instability in the Newtonian problem takes place on a length scale of about 10\% of the width of the channel, or $\Delta = 0.1$ (a guess).
-The viscoelastic Kelvin-Helmholtz instability is sensitive to the walls at this $\Delta$ and a $\Rey \lesssim 1$ (see figure \ref{fig:vary_Re_delta_conv}).
-This means that on the scale of the channel, $\Rey \gtrsim 10$ for the walls not to affect the instability.
+The Kelvin-Helmholtz instability in the Newtonian problem takes place on a length scale of about 10\% of the width of the channel, or $\Delta = 0.1$.
+The viscoelastic Kelvin-Helmholtz instability is sensitive to the walls at this $\Delta$ and a $Re \lesssim 10$.
+This means that on the scale of the channel $Re \gtrsim 100$ for the walls not to affect the instability.
 So, the important results for the purely elastic instability from the point of view of the plane Couette problem are probably those for which the walls are relevant.
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\textwidth]{vary_Re_delta_conv}
-    \caption{The blue line is the data from the stretched code and the green line is the $\Delta = 0.1$ data.
-By $\Rey = 1$ it is clear that the Reynold's number is sufficient such that the walled system behaves as though it were insensitive to the walls.}
-    \label{fig:vary_Re_delta_conv}
-\end{figure}
-
-At $\Delta = 0.1$ we see the same instability as that seen in the completely free case.
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-	\centering
-    \includegraphics[width=\textwidth]{KH_purely_elastic}
-    \caption{}
-    \label{fig:KH_purely_elastic}
-\end{subfigure}
-~
-\begin{subfigure}[b]{0.48\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{KH_low_Wi_vary_Re}
-    \caption{}
-    \label{fig:KH_reduce_Re}
-\end{subfigure}
-
-\begin{subfigure}[b]{0.48\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{KH_low_Re_vary_Wi}
-    \caption{ }
-    \label{fig:KH_purely_elastic}
-\end{subfigure}
-~
-\begin{subfigure}[b]{0.48\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{KH_onset_beta_Wi}
-    \caption{}
-    \label{fig:KH_elastic_onset}
-\end{subfigure}
-\caption{a) The change in the height of the dispersion relation as $\Wi$ is increased at $\Rey = 0$.
-This instability must be entirely elastic in nature.
-b) The change in the height of the dispersion relation as the Reynolds number is reduced at $\Wi=5$.
-At low $\Rey$ the instability is clearly still present for large polymer concentrations, consistent with purely elastic turbulence.
-c) The change in the height of the dispersion relation as $\Wi$ is increased at $\Rey = 0$.
-This instability must be entirely elastic in nature.
-d) The value of the Weissenberg number at which the velocity profile becomes unstable against $\beta$.
-The onset of the purely elastic instability moves to higher $Wi$ as $\beta$ increases.}
-\end{figure}
-
-\section{Confirming the model}
-
-\subsection{Consistency of results with the FENE model}
+\section{Consistency with the FENE-CR model}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\textwidth]{FENE_low_Re_vary_Wi}
-    \caption{Results are consistent with figure \ref{fig:KH_purely_elastic}}
-    \label{fig:FENE_low_Re}
-\end{figure}
-
-\subsection{Varying width of the instability}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\textwidth]{high_Re_vary_delta}
-    \caption{When results are rescaled for the various delta, The instability is found to be insensitive to the width of the instability relative to the wall.
-At delta = 0.1, $\Rey = 10000$, $\Wi = 0.001$.
-300 Gauss-Labatto points were used for each calculation.}
-    \label{fig:delta_dispersion}
-\end{figure}
-
-\subsection{Drag reduction}
-
-We see drag reduction using the Oldroyd-B model. It is not clear whether or not the maximum drag reduction asymptote is present.
-
-\begin{figure}
-%    \showthe\columnwidth %use this to determine size of figures.
-    \centering
-    \includegraphics[width=0.7\textwidth]{KH_high_Re_vary_Wi}
-    \caption{The height of the dispersion relation is reduced for the Kelvin-Helmholtz instability as the Weissenberg number is increased.
-The grey dashed line is the height of the dispersion relation for the Newtonian fluid.
-The decrease in $\lambda_{r}$ corresponds to increased stability of the base flow and so confirms the presence of drag reduction in this system.}
-    \label{fig:KH_drag_reduction}
-\end{figure}
-
-\section{Conclusions}
+\section{Conclusion}
 
@@
 
-\bibliographystyle{jfm}
-% Note the spaces between the initials
-
-%\bibliography{jfm-instructions}
-
 \end{document}

### 2013-10-29 paper/paper.tex
last commit of paper before giving it to Alexander to write.

@@
 %	paper.tex	Toby Searle
-%	Last modified: Tue 22 Oct 13:14:21 2013
+%	Last modified: Tue 29 Oct 10:24:24 2013
 %	using jfm template
@@
 Presumably, this will also be a Kelvin-Helmholtz instability as the streaks shear with the rest of the fluid.
+The Kelvin-Helmholtz instability is also often integral to the transition to turbulence in Newtonian fluids.
+It is hoped that by finding a purely elastic version of this instability, we might be able to probe one of the important mechanisms for the transition to purely elastic turbulence.
 To explore this mechanism in the purely elastic regime we have constructed a simple model system of a shearing viscoelastic fluid.
 
-The Kelvin-Helmholtz instability is fundamental to Newtonian fluids, and is often integral to the transition to turbulence in these fluids.
-It is hoped that by finding a purely elastic version of this instability, we might be able to probe one of the important mechanisms for the transition to purely elastic turbulence.
-
 The key dimensionless number for turbulence without inertia in Viscoelastic flows is the Weissenberg number, which is the ratio of the normal stress to the shear stress of the polymer component of the fluid $Wi = \frac{N_{1}}{\sigma}$.
-For small shear rates, this is approximately equivalent to $Wi \approx \lambda \dot{\gamma} = De$ where $\dot{\gamma}$ is the shear rate and $De$ is the Deborah number.
+For small shear rates, this is approximately equivalent to $De$, the Deborah number, so that $Wi \approx De = \lambda \dot{\gamma}$ where $\dot{\gamma}$ is the shear rate.
 
@@
 
+$U$ and $V$ are the base streamwise (x) and wall normal (y) velocities respectively.
+$T$ is the base stress tensor.
 We use Gauss-Labatto points in the wall-normal ($y$) direction for the base profile, and decomposed the disturbances to this flow into Fourier modes.
@@
 \end{align}
-With $Wi$ denoting the Weissenberg number and $\tau$ the stress in the polymeric fluid.
+With $\mathbf{v}$ as the total (base flow and disturbance) velocity and $\tau$ as the total stress in the polymeric fluid.
 The FENE-CR viscoelastic fluid has the advantage of being similarly easy to simulate, but also including a finite extensibility for the polymers.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{KH_dispersion}
-    \caption{Example of dispersion relation for Weissenberg numbers 200, 100 and $10^{-5}$, with $\beta = 0.1$ and $\Rey = 10000$. Polymer elasticity reduces the height of the instability.}
-    \label{fig:KH_growth_rate}
-\end{figure}
-
-We performed a Chebyshev decomposition of the flow in the wall-normal ($y$) direction for the base profile, and decomposed the disturbances to this flow in both Chebyshev and Fourier modes.
-
-\begin{equation}
-    g(y) = \sum\limits_{m=1}^{m=M} \widetilde{g}_{m} T_{m}(y) e^{ikx + \lambda t}
-\end{equation}
-
-for all disturbance variables $g = u, v, p, \tau_{i,j}$.
-Where $M$ is the number of Chebyshev modes, $T_{m}$ is the mth Chebyshev polynomial of the 1st kind, $k$ is the streamwise wavenumber of the disturbance and $\lambda$ is the growth rate of the mode.
+Again, we used Gauss-Labatto points in the wall normal direction and Fourier modes in the streamwise direction.
 
@@
 At low Reynolds number, low $\beta$ and sufficiently large Weissenberg number we observe an instability across a range of streamwise disturbance wavenumbers.
-This leads us to suppose that this instability might be a plausible reason for the instability in viscoelastic plane Couette flow, similar to that observed by Waleffe.
+This leads us to suppose that this instability might be a plausible cause for a self-sustaining process in viscoelastic plane Couette flow, similar to that observed by Waleffe.
 
 The instability remains unchanged under variation of $\Delta$ at low $\Delta$, proving that it is a free shear instability.
-Although the instability appears to require some inertia in the fluid, it is still present for  $\Rey = 0.01$  - far lower than the usual threshold of $\Rey = 1000$ for a Newtonian Kelvin-Helmholtz instability.
+Although the instability appears to require some inertia in the fluid, it is still present for  $\Rey = 0.01$, far lower than the usual threshold of $\Rey = 1000$ for a Newtonian Kelvin-Helmholtz instability.
 
-We see an instability grow from around $k_x \sim 0.1$ and move to lower $k_x$ as the Weissenberg number increases. The height of the instability also increases with increasing Weissenberg number.
+We see an instability grow from around $k \sim 0.06$ and move to lower $k$ as the Weissenberg number increases (figure \ref{fig:dispersions_low_Re}).
+The height of the instability also increases with increasing Weissenberg number (figure \ref{fig:inf_low_Re}).
 
@@
 The dispersion relation for the instability remains broad in $k$ until $Wi \sim 100$ where a new eigenvector becomes dominant.
-At this point the old peak decreases in size and the new, much narrower, peak stays the same height.
-It is unclear what this means for the instability at this point.
 
@@
 	\caption{}
-	\label{fig:inf_low_Re}
+	\label{fig:inf_vary_Re}
     \end{subfigure}
@@
 \end{figure}
+
+As the Reynold's number is reduced, new eigenvalues become dominant.
+Although the dominant eigenvalue changes the flow is still unstable, even down to $\Rey = 0.01$ (see figures \ref{fig:inf_vary_Re} and \ref{fig:dispersions_low_Wi}).
 
@@
     \end{subfigure}
-    \caption{a) Streamfunction of the largest eigenfunction of the instability when $\Rey = 0.1$ and $\Wi =100$. b) xx stress for the same instability.}
+    \caption{a) Streamfunction of the largest eigenfunction of the instability when $\Rey = 0.1$, $\Wi =100$, $\Delta = 0.005$.
+Red is positive (streamlines of the flow point clockwise around the contours), Blue is negative (streamlines of the flow point anticlockwise around the contours) b) xx stress for the same instability.}
 \end{figure}
@@
 We believe that this is due to the inertial effects at low Reynold's number being so weak.
-This means it is very easy to move the fluid even in at a low shear rate, far from the centre of the channel.
-I think that the shear rate in the wall normal direction is only less than that in the streamwise direction close to the walls at low Re.
+This means it is very easy to move the fluid even in at the shear rate present far from the centre of the channel.
+I think the instability generated by the elasticity of the fluid needs the walls to dampen it for some reason.
+The fluid moves more as one block because it has high a viscosity.
+This one block is easier to get going because of the low inertia it is also easy to stop.
+It then needs something solid to kill the fluid motion, this is either a very large body of stationary fluid or a wall.
 The inertial effects must reduce the velocity of the fluid far from the walls so that it can feel the effect of the streamwise component of the velocity gradient.
@@
     \includegraphics[width=\textwidth]{psi_high_delta}
-    \caption{Streamfunction of the eigenfunction of the instability at $\Delta = 0.1$. The magnitude is scaled by the xx stress in the centre of the channel.}
+    \caption{Streamfunction of the eigenfunction of the instability at $\Delta = 0.1$, $\Wi = 100$, $\Rey=0.1$. The magnitude is scaled by the xx stress in the centre of the channel.}
     \label{fig:psi_high_delta}
@@
 
-All of this goes to say why it is difficult to see the instability at $\Rey = 0$.
+It is difficult to see the instability at $\Rey = 0$.
 As the Reynold's number is reduced the walls become more important to the instability.
@@
     \centering
-    \includegraphics[width=\textwidth]{KH_low_Re_vary_Wi}
-    \caption{ }
-    \label{fig:KH_purely_elastic}
-\end{subfigure}
-~
-\begin{subfigure}[b]{0.48\textwidth}
-    \centering
     \includegraphics[width=\textwidth]{KH_onset_beta_Wi}
@@
 \end{subfigure}
-\caption{a) The change in the height of the dispersion relation as $\Wi$ is increased at $\Rey = 0$.
+\caption{a) The change in the height of the dispersion relation as $\Wi$ is increased at $\Rey = 0$ with $\Delta = 0.1$.
 This instability must be entirely elastic in nature.
 b) The change in the height of the dispersion relation as the Reynolds number is reduced at $\Wi=5$.
-At low $\Rey$ the instability is clearly still present for large polymer concentrations, consistent with purely elastic turbulence.
-c) The change in the height of the dispersion relation as $\Wi$ is increased at $\Rey = 0$.
-This instability must be entirely elastic in nature.
-d) The value of the Weissenberg number at which the velocity profile becomes unstable against $\beta$.
+At low $\Rey$ the instability is clearly still present for large polymer concentrations, consistent with purely elastic turbulence with $\Delta = 0.1$.
+c) The value of the Weissenberg number at which the velocity profile becomes unstable against $\beta$ at $\Delta = 0.1$.
 The onset of the purely elastic instability moves to higher $Wi$ as $\beta$ increases.}
@@
 Shorter lengths bring about a larger instability but do not delay it to higher Weissenberg number.
-Otherwise similar dispersion relations are observed with a similar dependence on the distance to the walls.
+Otherwise similar dispersion relations are observed with a similar dependence on the distance to the walls (figure \ref{fig:FENE_low_Re}).
 
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{FENE_low_Re_vary_Wi}
-    \caption{Results are consistent with figure \ref{fig:KH_purely_elastic}}
+    \includegraphics[width=0.7\textwidth]{FENE_purely_elastic}
+    \caption{The FENE-CR model fluid at $\Rey = 0$  when $\Delta = 0.1$. Results are consistent with figure \ref{fig:KH_purely_elastic}.}
     \label{fig:FENE_low_Re}
@@
     \includegraphics[width=0.7\textwidth]{high_Re_vary_delta}
-    \caption{When results are rescaled for the various delta, The instability is found to be insensitive to the width of the instability relative to the wall.
-At delta = 0.1, $\Rey = 10000$, $\Wi = 0.001$.
-300 Gauss-Labatto points were used for each calculation.}
+    \caption{ Dispersion relations for various values of $\Delta$ and $\Rey = 1000$, $\Wi = 0.01$.
+When results are rescaled for delta, The instability is found to be insensitive to the width of the instability relative to the wall at this combination of Reynold's number and Wiessenberg number.}
     \label{fig:delta_dispersion}
@@
 
-We see drag reduction using the Oldroyd-B model. It is not clear whether or not the maximum drag reduction asymptote is present.
+We see drag reduction using the Oldroyd-B model. It is not clear whether or not the maximum drag reduction asymptote is present (figure \ref{fig:KH_drag_reduction}).
 
@@
     \includegraphics[width=0.7\textwidth]{KH_high_Re_vary_Wi}
-    \caption{The height of the dispersion relation is reduced for the Kelvin-Helmholtz instability as the Weissenberg number is increased.
+    \caption{Peak growth rate against Wiessenberg number at $\Rey = 1000$, $\Delta = 0.1$ The height of the dispersion relation is reduced for the Kelvin-Helmholtz instability as the Weissenberg number is increased.
 The grey dashed line is the height of the dispersion relation for the Newtonian fluid.
@@
 \end{figure}
+
+\section{Outline of the mechanism}
 
@@
 
-%\bibliography{jfm-instructions}
+\bibliography{KH_paper}
 

### 2014-02-26 Alex_spectrum.py
From Bott, added all code. should be merged with code on my mac and totally up to date. hopefully.

@@ -1,0 +1,253 @@
+##------------------------------------
+
+from scipy import *
+from scipy.linalg import inv, solve, eig, det
+import pickle
+
+
+##------------------------------------
+
+M = 150
+
+Re = 0
+Wi = 10.82
+bbeta = 0.1
+
+_delta = 0.14
+
+##------------------------------------
+
+II = identity(M,dtype='d')
+
+cbar = ones(M,dtype='d')
+cbar[0] = 2.0
+cbar[M-1] = 2.0
+
+
+ygl = zeros(M,dtype='d')
+for m in range(M):
+    ygl[m] = cos(pi*m/(M-1))
+
+zzz_up = zeros(M,dtype='d')
+for m in range(M):
+    zzz_up[m] = 0.5*(ygl[m]+1.0)
+
+zzz_down = zeros(M,dtype='d')
+for m in range(M):
+    zzz_down[m] = 0.5*(ygl[m]-1.0)
+
+
+D1 = zeros((M,M),dtype='d')
+for l in range(M):
+    for j in range(M):
+        if l != j:
+            D1[l,j] = cbar[l]*((-1)**(l+j))/(cbar[j]*(ygl[l]-ygl[j]))
+
+for j in range(1,M-1):
+    D1[j,j] = -0.5*ygl[j]/(1.0-ygl[j]*ygl[j])
+
+D1[0,0] = (2.0*(M-1)*(M-1)+1.0)/6.0
+D1[M-1,M-1] = -D1[0,0]
+
+D1 = 2*D1
+D2 = dot(D1,D1)
+
+## Laminar profile
+
+U0up = zeros(M,dtype='d')
+for m in range(M):
+    U0up[m] = tanh(zzz_up[m]/_delta)/tanh(1.0/_delta)
+Txyup = dot(D1,U0up)
+Txxup = 2*Wi*Txyup*Txyup
+U0up_p = dot(D1,U0up)
+
+U0down = zeros(M,dtype='d')
+for m in range(M):
[…]

### 2014-02-26 DD_eigenvectors.py

@@ -1,0 +1,281 @@
+##------------------------------------
+
+from scipy import *
+from scipy.linalg import inv, solve, eig, det
+import cPickle as pickle
+import sys
+
+
+##------------------------------------
+
+M = 150
+
+Re = 0.0
+Wi = 10.
+bbeta = 0.1
+
+_delta = 0.1
+alpha = 0.28
+##------------------------------------
+parameter_string =  \
+"""Parameters:       M = {M}
+                     Re = {Re}
+                     Wi = {Wi}
+                     beta = {bbeta}
+                     _delta ={_delta}""".format(M=M,Re=Re,Wi=Wi,bbeta=bbeta,
+                                                _delta=_delta)
+print parameter_string
+
+II = identity(M,dtype='d')
+
+cbar = ones(M,dtype='d')
+cbar[0] = 2.0
+cbar[M-1] = 2.0
+
+
+ygl = zeros(M,dtype='d')
+for m in range(M):
+    ygl[m] = cos(pi*m/(M-1))
+
+zzz_up = zeros(M,dtype='d')
+for m in range(M):
+    zzz_up[m] = 0.5*(ygl[m]+1.0)
+
+zzz_down = zeros(M,dtype='d')
+for m in range(M):
+    zzz_down[m] = 0.5*(ygl[m]-1.0)
+
+
+D1 = zeros((M,M),dtype='d')
+for l in range(M):
+    for j in range(M):
+        if l != j:
+            D1[l,j] = cbar[l]*((-1)**(l+j))/(cbar[j]*(ygl[l]-ygl[j]))
+
+for j in range(1,M-1):
+    D1[j,j] = -0.5*ygl[j]/(1.0-ygl[j]*ygl[j])
+
+D1[0,0] = (2.0*(M-1)*(M-1)+1.0)/6.0
+D1[M-1,M-1] = -D1[0,0]
+
+D1 = 2*D1
+D2 = dot(D1,D1)
+
+## Laminar profile
+
+U0up = zeros(M,dtype='d')
+for m in range(M):
[…]

### 2014-02-26 D_domain.py

@@ -1,0 +1,254 @@
+##------------------------------------
+
+from scipy import *
+from scipy.linalg import inv, solve, eig, det
+import pickle
+
+
+##------------------------------------
+
+M = 100
+
+Re = 10000
+Wi = 0.01
+bbeta = 0.1
+
+_delta = 0.1
+
+##------------------------------------
+
+II = identity(M,dtype='d')
+
+cbar = ones(M,dtype='d')
+cbar[0] = 2.0
+cbar[M-1] = 2.0
+
+
+ygl = zeros(M,dtype='d')
+for m in range(M):
+    ygl[m] = cos(pi*m/(M-1))
+
+zzz_up = zeros(M,dtype='d')
+for m in range(M):
+    zzz_up[m] = 0.5*(ygl[m]+1.0)
+
+zzz_down = zeros(M,dtype='d')
+for m in range(M):
+    zzz_down[m] = 0.5*(ygl[m]-1.0)
+
+
+D1 = zeros((M,M),dtype='d')
+for l in range(M):
+    for j in range(M):
+        if l != j:
+            D1[l,j] = cbar[l]*((-1)**(l+j))/(cbar[j]*(ygl[l]-ygl[j]))
+
+for j in range(1,M-1):
+    D1[j,j] = -0.5*ygl[j]/(1.0-ygl[j]*ygl[j])
+
+D1[0,0] = (2.0*(M-1)*(M-1)+1.0)/6.0
+D1[M-1,M-1] = -D1[0,0]
+
+D1 = 2*D1
+D2 = dot(D1,D1)
+
+## Laminar profile
+
+U0up = zeros(M,dtype='d')
+for m in range(M):
+    U0up[m] = tanh(zzz_up[m]/_delta)/tanh(1.0/_delta)
+Txyup = dot(D1,U0up)
+Txxup = 2*Wi*Txyup*Txyup
+U0up_p = dot(D1,U0up)
+
+U0down = zeros(M,dtype='d')
+for m in range(M):
+    U0down[m] = tanh(zzz_down[m]/_delta)/tanh(1.0/_delta)
+Txydown = dot(D1,U0down)
[…]

### 2014-02-26 S_domain.py

@@ -1,0 +1,236 @@
+#----------------------------------------------------------------------------#
+#   Linear Stability Analysis of velocity profile in 2D 
+#   Last modified: Mon 22 Jul 2013 12:10:19 BST
+#----------------------------------------------------------------------------#
+
+"""Using the fully spectral method, find the stability of a 2D velocity 
+   profile"""
+
+#MODULES
+import sys
+import time
+from scipy import *
+from scipy import linalg
+import cPickle as pickle
+import ConfigParser
+
+#FUNCTIONS
+
+def mkDiffY():
+    """Makes a matrix to differentiate array wrt to y"""
+
+    y = YPOINTS 
+    # The C function:
+    C = ones(M, dtype='d')
+    C[0] = 2.0
+    C[M-1] = 2.0
+
+    # Set up the differentiation matrix
+    Dy = zeros((M, M) , dtype= 'd')
+    Dy[0, 0] = (2.0*(M-1)**2 + 1) / 6.0
+    Dy[M-1, M-1] = -(2.0*(M-1)**2 + 1) /  6.0
+    for n in range(M):
+        for m in range(M):
+            if n != m:
+                Dy[n, m] =  C[n] / C[m]
+                Dy[n, m] = Dy[n, m] * pow(-1, n + m) / (y[n] - y[m]) 		 
+            if n == m and n != 0 and n != (M-1):
+                Dy[n, m] = -y[m] / (2 * (1 - pow(y[m],2)) )
+    return Dy
+
+def mkEqnMat():
+    """make the matrix holding the linear stability equations."""
+    equation_mat = zeros((6*M,6*M), dtype='complex')
+
+    ####################### x direction       ############################
+    #du
+    equation_mat[0:M,0:M] = -Re*1.j*kx*MMU + beta*(-(kx**2)*eye(M,M) + MDYY)
+    #dv
+    equation_mat[0:M,M:2*M] = -Re*MMDYU
+    #dp
+    equation_mat[0:M,2*M:3*M] = -1.j*kx*eye(M,M)
+    #dtxx
+    equation_mat[0:M,3*M:4*M] = (1.-beta)*1.j*kx*eye(M,M)
+    #dtyy
[…]

### 2014-02-26 analysis_code/plot_colour_map.py

@@ -1,0 +1,134 @@
+#
+#   Plot eigenvector
+#
+"""Convert grid of GL points/Fourier points back to real space, then plot in a
+   colour map"""
+
+from matplotlib import pyplot as plt
+import cPickle as pickle
+from scipy import *
+from scipy import interpolate
+# PARAMETERS
+
+M = 150
+
+Re = 0.0
+Wi = 10.
+bbeta = 0.1
+
+_delta = 0.1
+alpha = 0.28
+
+XPOINTS = 100
+
+#FUNCTIONS
+def my_interp(vec):
+
+    f = interpolate.interp1d(y_points[::-1],vec[::-1], bounds_error=False,
+                         kind='linear')
+    return f(y_new)
+
+def fourier_transform(vec):
+    mat = zeros((2*M, XPOINTS), dtype='complex')
+    for m in xrange (2*M):
+        for n in xrange(XPOINTS):
+            mat[m,n] = vec[m] * exp(1.j*alpha*x_points[n])
+
+    del m,n
+    return mat
+
+# MAIN
+
+ygl = zeros(M,dtype='d')
+for m in range(M):
+    ygl[m] = cos(pi*m/(M-1))
+
+zzz_up = zeros(M,dtype='d')
+for m in range(M):
+    zzz_up[m] = 0.5*(ygl[m]+1.0)
+
+zzz_down = zeros(M,dtype='d')
+for m in range(M):
+    zzz_down[m] = 0.5*(ygl[m]-1.0)
+
+y_points = concatenate((zzz_up, zzz_down))
+
+x_points = zeros(XPOINTS,dtype='d') 
+for n in range(XPOINTS):
+    #               2lambda     * fractional position
+    x_points[n] = (2.*pi/alpha) * ((1.*n)/XPOINTS)
+del n
+
+y_new = zeros(2*M)
+for m in range(2*M):
+    y_new[m] = -1 + ((1.*m)/M)
+del m
+
+fileName = \
+'evec-k{k}-b{b}-M{M}-Re{Re}-Wi{Wi}-del{delta}.dat'.format(k=alpha,
+                                                              b=bbeta, M=M,
+                                                              Re=Re,  Wi=Wi,
+                                                              delta=_delta)
+titleString = \
+' for k = {k}, b = {b}, Re = {Re}, Wi = {Wi}, delta = {delt}'.format(k=alpha,
[…]

### 2014-02-26 analysis_code/plot_delta_test.py

@@ -1,0 +1,56 @@
+#------------------------------------------------------------------------------
+#   Make a 2D plot using matplotlib
+#   Last modified: Wed 23 Oct 15:15:13 2013
+#
+#------------------------------------------------------------------------------
+
+from scipy import *
+import matplotlib.pyplot as plt
+from matplotlib import rc
+# This next import is supposed to make sure fonts are good, regardless of os
+from matplotlib.font_manager import fontManager, FontProperties
+
+# MAIN
+
+fig_width_pt = 452.0  # Get this from LaTeX using \showthe\columnwidth
+inches_per_pt = 1.0/72.27                # Convert pt to inch
+golden_ratio = (sqrt(5)+1.0)/2.0         # Aesthetic ratio
+fig_width = fig_width_pt*inches_per_pt   # width in inches
+fig_height = fig_width/golden_ratio      # height in inches
+fig_size =  [fig_width,fig_height]
+
+#Use the Latex distribution for text.
+rc('text', usetex=True)
+#Make sure font is the same as that in the template/style file!
+rc('font', family='serif', size='12')
+rc('figure', figsize=fig_size)
+
+FileList =[ r"../high_R_delta_test/b0.1-M150-Re20000.0-Wi0.0005-del0.05.dat",
+            r"../high_R_delta_test/b0.1-M150-Re10000.0-Wi0.001-del0.1.dat",
+            r"../high_R_delta_test/b0.1-M150-Re5000.0-Wi0.002-del0.2.dat" ]
+
+low = genfromtxt(FileList[0])
+x1,y1 = low[:,0]*0.1, low[:,1]*0.1
+mid = genfromtxt(FileList[1])
+x2,y2 = mid[:,0]*0.1, mid[:,1]*0.1
+high = genfromtxt(FileList[2])
+x3,y3 = high[:,0]*0.1, high[:,1]*0.1
+outFilename = r'high_Re_vary_delta.pdf'
+
+fig = plt.figure()
+
+ax = plt.subplot(111)
+
+ax.plot(x1*0.05,y1*0.05,'-',linewidth=1)
+ax.plot(x2*0.1,y2*0.1,'-',linewidth=1)
+ax.plot(x3*0.2,y3*0.2,'-',linewidth=1)
+
[…]

### 2014-02-26 analysis_code/plot_onset.py

@@ -1,0 +1,41 @@
+#------------------------------------------------------------------------------
+#   Make a 2D plot using matplotlib
+#   Last modified: Wed 23 Oct 15:05:51 2013
+#
+#------------------------------------------------------------------------------
+
+from scipy import *
+import matplotlib.pyplot as plt
+from matplotlib import rc
+
+# MAIN
+fig_width_pt = 452.0  # Get this from LaTeX using \showthe\columnwidth
+inches_per_pt = 1.0/72.27                # Convert pt to inch
+golden_ratio = (sqrt(5)+1.0)/2.0         # Aesthetic ratio
+fig_width = fig_width_pt*inches_per_pt   # width in inches
+fig_height = fig_width/golden_ratio      # height in inches
+fig_size =  [fig_width,fig_height]
+
+
+#Use the Latex distribution for text.
+rc('text', usetex=True)
+#Make sure font is the same as that in the template/style file!
+rc('font', family='serif', size='12')
+rc('figure', figsize=fig_size)
+
+
+lowBeta = genfromtxt('beta_vs_Wi_stability.dat')
+outFilename = 'onset_beta_Wi.pdf'
+
+plt.plot(lowBeta[:,0], lowBeta[:,1]/0.1, 'ro') 
+
+#plt.axis([0, 100, 0, 1])
+
+plt.ylabel(r'$Wi$ at the onset of instability')
+plt.xlabel(r'$\beta$')
+
+fig = plt.gcf()
+
+plt.savefig(outFilename)
+
+plt.show()

### 2014-02-26 analysis_code/plot_stability.py

@@ -1,0 +1,66 @@
+#------------------------------------------------------------------------------
+#   Make a 2D plot using matplotlib
+#   Last modified: Wed 23 Oct 15:13:03 2013
+#
+#------------------------------------------------------------------------------
+
+from scipy import *
+import matplotlib.pyplot as plt
+from matplotlib import rc
+# This next import is supposed to make sure fonts are good, regardless of os
+from matplotlib.font_manager import fontManager, FontProperties
+
+# MAIN
+
+fig_width_pt = 452.0  # Get this from LaTeX using \showthe\columnwidth
+inches_per_pt = 1.0/72.27                # Convert pt to inch
+golden_ratio = (sqrt(5)+1.0)/2.0         # Aesthetic ratio
+fig_width = fig_width_pt*inches_per_pt   # width in inches
+fig_height = fig_width/golden_ratio      # height in inches
+fig_size =  [fig_width,fig_height]
+
+#Use the Latex distribution for text.
+rc('text', usetex=True)
+#Make sure font is the same as that in the template/style file!
+rc('font', family='serif', size='12')
+rc('figure', figsize=fig_size)
+
+lowBeta = genfromtxt('stability-beta0.1-Re10000.0.dat')
+x1,y1 = lowBeta[:,0]/0.1, lowBeta[:,2]*0.1
+midBeta = genfromtxt('stability-beta0.5-Re10000.0.dat')
+x2,y2 = midBeta[:,0]/0.1, midBeta[:,2]*0.1
+highBeta = genfromtxt('stability-beta0.9-Re10000.0.dat')
+x3,y3 = highBeta[:,0]/0.1, highBeta[:,2]*0.1
+outFilename = 'KH_high_Re_vary_Wi.pdf'
+
+fig = plt.figure()
+
+ax = plt.subplot(111)
+
+ax.plot(x1,y1,'-',linewidth=1)
+ax.plot(x2,y2,'-',linewidth=1)
+ax.plot(x3,y3,'-',linewidth=1)
+
+# Insert a horizontal line to mark the solution for the Newtonian instability
+plt.axhline(y=0.1880, ls='--', linewidth=0.6,  color='black')
+
+# Insert point at yaxis intercept
+theIntercept = lowBeta[0,2]*0.1
+ax.plot([0], [theIntercept], 'o', color='red')
+
[…]

### 2014-02-26 analysis_code/plot_stability_Re0.py

@@ -1,0 +1,67 @@
+#------------------------------------------------------------------------------
+#   Make a 2D plot using matplotlib
+#   Last modified: Wed 23 Oct 16:37:20 2013
+#
+#------------------------------------------------------------------------------
+
+from scipy import *
+import matplotlib.pyplot as plt
+from matplotlib import rc
+# This next import is supposed to make sure fonts are good, regardless of os
+from matplotlib.font_manager import fontManager, FontProperties
+
+# MAIN
+
+fig_width_pt = 452.0  # Get this from LaTeX using \showthe\columnwidth
+inches_per_pt = 1.0/72.27                # Convert pt to inch
+golden_ratio = (sqrt(5)+1.0)/2.0         # Aesthetic ratio
+fig_width = fig_width_pt*inches_per_pt   # width in inches
+fig_height = fig_width/golden_ratio      # height in inches
+fig_size =  [fig_width,fig_height]
+
+#Use the Latex distribution for text.
+rc('text', usetex=True)
+#Make sure font is the same as that in the template/style file!
+rc('font', family='serif', size='12')
+rc('figure', figsize=fig_size)
+
+lowBeta = genfromtxt('stability-beta0.1-Re0.dat')
+x1,y1 = lowBeta[:,0]/0.1, lowBeta[:,2]*0.1
+midBeta = genfromtxt('stability-beta0.5-Re0.dat')
+x2,y2 = midBeta[:,0]/0.1, midBeta[:,2]*0.1
+highBeta = genfromtxt('stability-beta0.9-Re0.dat')
+x3,y3 = highBeta[:,0]/0.1, highBeta[:,2]*0.1
+outFilename = 'KH_purely_elastic.pdf'
+
+fig = plt.figure()
+
+ax = plt.subplot(111)
+
+ax.plot(x1,y1,'-',linewidth=1)
+ax.plot(x2,y2,'-',linewidth=1)
+ax.plot(x3,y3,'-',linewidth=1)
+
+# Insert a horizontal line to mark the solution for the Newtonian instability
+plt.axhline(y=0.1880, ls='--', linewidth=0.6,  color='black')
+
+# Insert point at yaxis intercept
+# theIntercept = (lowBeta[0,2])*0.1
+# ax.plot([0], [theIntercept], 'o', color='red')
+
[…]

### 2014-02-26 analysis_code/plot_stability_changeRe.py

@@ -1,0 +1,69 @@
+#------------------------------------------------------------------------------
+#   Make a 2D plot using matplotlib
+#   Last modified: Wed 23 Oct 15:02:08 2013
+#
+#------------------------------------------------------------------------------
+
+from scipy import *
+import matplotlib.pyplot as plt
+from matplotlib import rc
+# This next import is supposed to make sure fonts are good, regardless of os
+from matplotlib.font_manager import fontManager, FontProperties
+
+# MAIN
+
+fig_width_pt = 452.0  # Get this from LaTeX using \showthe\columnwidth
+inches_per_pt = 1.0/72.27                # Convert pt to inch
+golden_ratio = (sqrt(5)+1.0)/2.0         # Aesthetic ratio
+fig_width = fig_width_pt*inches_per_pt   # width in inches
+fig_height = fig_width/golden_ratio      # height in inches
+fig_size =  [fig_width,fig_height]
+
+#Use the Latex distribution for text.
+rc('text', usetex=True)
+#Make sure font is the same as that in the template/style file!
+rc('font', family='serif', size='12')
+rc('figure', figsize=fig_size)
+
+lowBeta = genfromtxt('stability-beta0.1-Wi5.0.dat')
+x1,y1 = lowBeta[:,0]*0.1, lowBeta[:,2]*0.1
+midBeta = genfromtxt('stability-beta0.5-Wi5.0.dat')
+x2,y2 = midBeta[:,0]*0.1, midBeta[:,2]*0.1
+highBeta = genfromtxt('stability-beta0.9-Wi5.0.dat')
+x3,y3 = highBeta[:,0]*0.1, highBeta[:,2]*0.1
+outFilename = 'KH_low_Wi_vary_Re.pdf'
+
+fig = plt.figure()
+
+ax = plt.subplot(111)
+
+ax.plot(x1,y1,'-',linewidth=1)
+ax.plot(x2,y2,'-',linewidth=1)
+ax.plot(x3,y3,'-',linewidth=1)
+
+# Insert a horizontal line to mark the solution for the Newtonian instability
+plt.axhline(y=0.1880, ls='--', linewidth=0.6,  color='black')
+
+# Insert point at yaxis intercept
+theIntercept = lowBeta[0,2]*0.1
+ax.plot([0], [theIntercept], 'o', color='blue')
[…]

### 2014-02-26 analysis_code/stability_curve.py

@@ -1,0 +1,60 @@
+#------------------------------------------------------------------------------
+#   Process data to make a stability curve.
+#   Last modified: Sun 19 May 16:45:45 2013
+#
+#------------------------------------------------------------------------------
+
+from scipy import *
+import glob
+import re
+
+#-----------------------------------------
+
+M = 150
+
+Re = 10000.0
+bbeta = 0.1
+
+_delta = 0.1
+
+#-----------------------------------------
+
+# MAIN
+
+fileList = glob.glob('*.dat')
+
+outstream = open('stability-beta{bbeta}-Re{Re}.dat'.format(bbeta=bbeta, Re=Re),
+               'w')
+
+for filename in fileList:
+    splitString = re.split('-',filename)
+    MString = splitString[0]
+    varString = splitString[1]
+
+    m = re.match('M',MString)
+    if m is  None:
+        continue
+
+    files_M = int(MString[m.end():])
+
+    if files_M is M:
+        print files_M
+        print varString 
+        varMatch = re.match('Wi',varString)
+        if varMatch is None:
+            continue
+        filesVar = float(varString[varMatch.end():-4])
+        print filesVar
+
+        dispersionData = genfromtxt(filename)
+        maxIndex = argmax(dispersionData[:,1])
+
+        outstream.write('{var}, {k}, {eig}\n'.format(
+                        var=filesVar,
+                        k=dispersionData[maxIndex,0],
+                        eig=dispersionData[maxIndex,1]))
+
+outstream.close()
+
+
+

### 2014-02-26 batch_Alex.py

@@ -1,0 +1,264 @@
+##------------------------------------
+
+from scipy import *
+from scipy.linalg import inv, solve, eig, det
+import pickle
+import sys
+
+
+##------------------------------------
+
+M = 200
+
+Re = double(sys.argv[1])
+Wi = double(sys.argv[2])
+bbeta = 0.1
+
+_delta = 0.05
+kxList = r_[0.05:0.7:0.05]
+##------------------------------------
+parameter_string =  \
+"""Parameters:       M = {M}
+                     Re = {Re}
+                     Wi = {Wi}
+                     beta = {bbeta}
+                     _delta ={_delta}""".format(M=M,Re=Re,Wi=Wi,bbeta=bbeta,
+                                                _delta=_delta)
+print parameter_string
+
+II = identity(M,dtype='d')
+
+cbar = ones(M,dtype='d')
+cbar[0] = 2.0
+cbar[M-1] = 2.0
+
+
+ygl = zeros(M,dtype='d')
+for m in range(M):
+    ygl[m] = cos(pi*m/(M-1))
+
+zzz_up = zeros(M,dtype='d')
+for m in range(M):
+    zzz_up[m] = 0.5*(ygl[m]+1.0)
+
+zzz_down = zeros(M,dtype='d')
+for m in range(M):
+    zzz_down[m] = 0.5*(ygl[m]-1.0)
+
+
+D1 = zeros((M,M),dtype='d')
+for l in range(M):
+    for j in range(M):
+        if l != j:
+            D1[l,j] = cbar[l]*((-1)**(l+j))/(cbar[j]*(ygl[l]-ygl[j]))
+
+for j in range(1,M-1):
+    D1[j,j] = -0.5*ygl[j]/(1.0-ygl[j]*ygl[j])
+
+D1[0,0] = (2.0*(M-1)*(M-1)+1.0)/6.0
+D1[M-1,M-1] = -D1[0,0]
+
+D1 = 2*D1
+D2 = dot(D1,D1)
+
+## Laminar profile
+
[…]

### 2014-02-26 infinite_walls.py

@@ -1,0 +1,282 @@
+##------------------------------------
+
+from scipy import *
+from scipy.linalg import inv, solve, eig, det
+import pickle
+
+
+##------------------------------------
+
+M = 150
+
+Re = 0.0
+Wi = 10.0
+bbeta = 0.1
+offset =  1e-6
+
+kxList = r_[0.02:1.0:0.02]
+
+##------------------------------------
+
+II = identity(M,dtype='d')
+
+cbar = ones(M,dtype='d')
+cbar[0] = 2.0
+cbar[M-1] = 2.0
+
+
+ygl = zeros(M,dtype='d')
+for m in range(M):
+    ygl[m] = cos(pi*m/(M-1))
+
+zzz_up = zeros(M,dtype='d')
+for m in range(M):
+    zzz_up[m] = 0.5*(ygl[m]+1.0)
+
+zzz_down = zeros(M,dtype='d')
+for m in range(M):
+    zzz_down[m] = 0.5*(ygl[m]-1.0)
+
+# put functions onto domain with infinite walls
+zzz_up = -(zzz_up) / (zzz_up - 1 - offset) 
+zzz_down = (zzz_down) / (1 + offset + zzz_down)
+
+D1 = zeros((M,M),dtype='d')
+for l in range(M):
+    for j in range(M):
+        if l != j:
+            D1[l,j] = cbar[l]*((-1)**(l+j))/(cbar[j]*(ygl[l]-ygl[j]))
+
+for j in range(1,M-1):
+    D1[j,j] = -0.5*ygl[j]/(1.0-ygl[j]*ygl[j])
+
+D1[0,0] = (2.0*(M-1)*(M-1)+1.0)/6.0
+D1[M-1,M-1] = -D1[0,0]
+
+D1up = 2*dot(diag(1./((zzz_up + 1. + offset)**2)),D1)
+D2up = dot(D1up,D1up)
+
+D1down = 2*dot(diag(1./((zzz_down - 1 - offset)**2)),D1)
+D2down = dot(D1down,D1down)
+
+del D1
+
+
+## Laminar profile
+
+U0up = zeros(M,dtype='d')
+for m in range(M):
[…]

### 2014-05-15 paper/paper.tex
updated paper a bit

@@
 %	paper.tex	Toby Searle
-%	Last modified: Tue 29 Oct 10:24:24 2013
+%	Last modified: Wed 14 May 22:10:55 2014
 %	using jfm template
@@
 \begin{keywords}
-Authors should not enter keywords on the manuscript, as these must be chosen by the author during the online submission process and will then be added during the typesetting process (see http://journals.cambridge.org/data/\linebreak[3]relatedlink/jfm-\linebreak[3]keywords.pdf for the full list)
+Authors should not enter keywords on the manuscript, as these must be chosen by
+the author during the online submission process and will then be added during
+the typesetting process (see
+http://journals.cambridge.org/data/\linebreak[3]relatedlink/jfm-\linebreak[3]keywords.pdf
+for the full list)
 \end{keywords}
@@
 
-Turbulence without inertia in viscoelastic fluids has generated much interest since it was discovered in Taylor-Couette flow by Larson, Shaqfeh and Muller in 1990 \cite{Larson1990}.
-As well as this numerical and experimental study of Taylor-Couette flow, Groisman and Steinberg \cite{Groisman2000} discovered turbulence in viscoelastic fluids between two counter rotating plates.
+Turbulence without inertia in viscoelastic fluids has generated much interest
+since it was discovered in Taylor-Couette flow by Larson, Shaqfeh and Muller in
+1990 \cite{Larson1990}. As well as this numerical and experimental study of
+Taylor-Couette flow, Groisman and Steinberg \cite{Groisman2000} discovered
+turbulence in viscoelastic fluids between two counter rotating plates.
 
-For a long time it was thought that the elasticity of a viscoelastic fluid only served to dampen instability.
-It was observed that the drag in fluid could be reduced by the addition of small amounts of viscoelastic fluid.
-This drag reduction has been much studied over the last 70 years.
-However, the studies above give reason to believe that viscoelastic turbulence is present at very low Reynolds number, where it is driven by the elasticity of the polymeric fluid rather than its inertia.
+It was long thought that the elasticity of a viscoelastic fluid only served to
+dampen instability. This view stems from early results showing that drag ina
+turbulent Newtonian flow can be reduced by the addition of small amounts of
+viscoelastic fluid (\cite{Toms1977}). Although drag reduction has recieved a
+lot of attention in the past the studies above give reason to believe that
+there is a potentially more prevalent and useful phenomenon at work in
+viscoelastic fluids. It seems that viscoelastic turbulence is present at very
+low Reynolds number, where it is driven by the elasticity of the polymeric
+fluid rather than its inertia.
 
-In 1997 Fabian Waleffe identified a Newtonian self sustaining process in plane Couette flow \cite{Waleffe97}.
-Streamwise rolls redistribute the streamwise velocity into a streaky flow.
-This streaky flow is unstable through a Kelvin-Helmholtz instability creating a three dimensional perturbation which in turn re-energises the original streamwise rolls.
-This exact solution to the Navier-Stokes equations is thought to be a component of the transition to turbulence.
-In 1998 Waleffe constructed a bifurcation diagram for this exact solution \cite{Waleffe98} containing what looks like a bifurcation from infinity.
-This is the behaviour expected of the transition to turbulence in Couette flow.
+In 1997 Fabian Waleffe identified a Newtonian self sustaining process in plane
+Couette flow \cite{Waleffe1997}. Streamwise rolls redistribute the streamwise
+velocity into a streaky flow. This streaky flow is unstable through a
+Kelvin-Helmholtz instability leading to a symmetry bifurcation to a three
+dimensional perturbation which in turn re-energises the original streamwise
+rolls. This exact solution to the Navier-Stokes equations is thought to be a
+component of the transition to turbulence. In 1998 Waleffe constructed a
+bifurcation diagram for this exact solution \cite{Waleffe1998} containing what
+looks like a bifurcation from infinity. This is the behaviour expected of the
+transition to turbulence in Couette flow.
 
-Using this work in Newtonian fluid dynamics as a template for the structure of purely elastic turbulence reveals a similar pattern of streaks and, hopefully, a similar self-sustaining process.
-An important step towards explaining this process in purely elastic flows is establishing the mechanism by which the streaks become unstable.
-Presumably, this will also be a Kelvin-Helmholtz instability as the streaks shear with the rest of the fluid.
-The Kelvin-Helmholtz instability is also often integral to the transition to turbulence in Newtonian fluids.
-It is hoped that by finding a purely elastic version of this instability, we might be able to probe one of the important mechanisms for the transition to purely elastic turbulence.
-To explore this mechanism in the purely elastic regime we have constructed a simple model system of a shearing viscoelastic fluid.
+Using this work in Newtonian fluid dynamics as a template for the structure of
+purely elastic turbulence reveals a similar pattern of streaks and, hopefully,
+a similar self-sustaining process \cite{US!}. An important step towards
+explaining this process in purely elastic flows is establishing the mechanism
+by which the streaks become unstable. Presumably, this will also be a
+Kelvin-Helmholtz instability as the streaks shear with the rest of the fluid.
+The Kelvin-Helmholtz instability is also often integral to the transition to
+turbulence in Newtonian fluids. It is hoped that by finding a purely elastic
+version of this instability, we might be able to probe one of the important
+mechanisms for the transition to purely elastic turbulence. To explore this
+mechanism in the purely elastic regime we have constructed a simple model
+system of a shearing viscoelastic fluid.
 
-The key dimensionless number for turbulence without inertia in Viscoelastic flows is the Weissenberg number, which is the ratio of the normal stress to the shear stress of the polymer component of the fluid $Wi = \frac{N_{1}}{\sigma}$.
-For small shear rates, this is approximately equivalent to $De$, the Deborah number, so that $Wi \approx De = \lambda \dot{\gamma}$ where $\dot{\gamma}$ is the shear rate.
+The key dimensionless number for turbulence without inertia in viscoelastic
+flows is the Weissenberg number, which is the ratio of the normal stress to the
+shear stress of the polymer component of the fluid $Wi = \frac{N_{1}}{\sigma}$.
+For small shear rates, this is approximately equivalent to $De$, the Deborah
+number, so that $Wi \approx De = \lambda \dot{\gamma}$ where $\dot{\gamma}$ is
+the shear rate.
 
-We present a linear stability analysis of the Kelvin-Helmholtz instability in the purely elastic regime using direct numerical simulation of both the Oldroyd-B and FENE-CR constitutive models for a polymeric fluid.
-The purely elastic fluid is found to be unstable at sufficiently high numbers of the dimensionless parameter, the Weissenberg number.
-The growth rate of the largest growing eigenmode of the instability is found to increase with increasing Weissenberg number for low Reynold's number.
-This behaviour is consistent across both the Oldroyd-B and FENE-CR models.
+We present a linear stability analysis of the Kelvin-Helmholtz instability in
+the purely elastic regime using direct numerical simulation of both the
+Oldroyd-B and FENE-P constitutive models for a polymeric fluid. The purely
+elastic fluid is found to be unstable at sufficiently high numbers of the
+dimensionless parameter, the Weissenberg number. The growth rate of the largest
+growing eigenmode of the instability is found to increase with increasing
+Weissenberg number for low Reynold's number. This behaviour is consistent
+across both the Oldroyd-B and FENE-P models.
 
-The system we use for our analysis uses a hyperbolic tangent shaped laminar profile for the streamwise velocity across a channel, where the instability takes place between $y = \pm \Delta$.
-$y=0$ is the centreline of the channel, so that if $\Delta << 1$ the flow can be said to be a free shear instability.
+The system we use for our analysis uses a hyperbolic tangent shaped laminar
+profile for the streamwise velocity across a channel, where the instability
+takes place between $y = \pm \Delta$. $y=0$ is the centreline of the channel,
+so that if $\Delta << 1$ the flow can be said to be a free shear instability.
 This gives a base flow profile, 
@@
 
-$U$ and $V$ are the base streamwise (x) and wall normal (y) velocities respectively.
-$T$ is the base stress tensor.
-We use Gauss-Labatto points in the wall-normal ($y$) direction for the base profile, and decomposed the disturbances to this flow into Fourier modes.
+$U$ and $V$ are the base streamwise (x) and wall normal (y) velocities
+respectively. $T$ is the base stress tensor. We use Gauss-Labatto points in the
+wall-normal ($y$) direction for the base profile, and decomposed the
+disturbances to this flow into Fourier modes.  
 \begin{equation}
@@
 \end{equation}
-for all disturbance variables $g = u, v, p, \tau_{i,j}$.
-Where $N$ is the number of Fourier modes, $k$ is the streamwise wavenumber of the disturbance and $\lambda$ is the growth rate of the mode.
-This code uses two domains of pseudo-spectral points to give increased resolution in the centre of the simulation.
-The simulation was also repeated using a code for which the system of points was stretched using:
+for all disturbance variables $g = u, v, p, \tau_{i,j}$. Where $N$ is the
+number of Fourier modes, $k$ is the streamwise wavenumber of the disturbance
+and $\lambda$ is the growth rate of the mode. This code uses two domains of
+pseudo-spectral points to give increased resolution in the centre of the
+simulation. The simulation was also repeated using a code for which the system
+of points was stretched using: 
 \begin{align}
@@
 \end{align}
-This system ought to be completely insensitive to the boundary conditions on the flow and so also behave as a free shear instability.
+This system ought to be completely insensitive to the boundary conditions on
+the flow and so also behave as a free shear instability.
 
-The dimensionless quantities used throughout are non-dimensionalised relative to the instability size, $\Delta$, rather than the total simulation size.
-The obvious reason for this is that $\Delta$ is the length scale for the free shear instability.
+The dimensionless quantities used throughout are non-dimensionalised relative
+to the instability size, $\Delta$, rather than the total simulation size. The
+obvious reason for this is that $\Delta$ is the length scale for the free shear
+instability.
 
-In order to simulate this flow, we used an Oldroyd-B fluid with very low Reynolds number $\Rey < 0.01$ and a small ratio between the solvent and total viscosities $\beta = \frac{\mu_{s}}{\mu_{s}+\mu_{p}}$.
-This approximates a purely elastic fluid, where the polymer contribution to the dynamics is higher than the solvent contribution.
-The Oldroyd-B Navier stokes and constitutive equations are then:
+In order to simulate this flow, we used an Oldroyd-B fluid with very low
+Reynolds number $\Rey < 0.01$ and a small ratio between the solvent and total
+viscosities $\beta = \frac{\mu_{s}}{\mu_{s}+\mu_{p}}$. This approximates a
+purely elastic fluid, where the polymer contribution to the dynamics is higher
+than the solvent contribution. The Oldroyd-B Navier stokes and constitutive
+equations are then: 
 \begin{align}
-    Re \left[ \dt{\mathbf{v}} + \mathbf{v} \cdot \nabla  \mathbf{v} \right] &= - \nabla p + \beta \nabla^{2} \mathbf{v} + \frac{1-\beta}{Wi} \nabla \cdot \mathbf{\tau} \\
-    \dot{\tau}/Wi + \overset{\nabla}\tau &= \left(\nabla \mathbf{v}\right)^{T} + \nabla{\mathbf{v}}
+    Re \left[ \dt{\mathbf{v}} + \mathbf{v} \cdot \nabla  \mathbf{v} \right] &=
+    - \nabla p + \beta \nabla^{2} \mathbf{v} + \frac{1-\beta}{Wi} \nabla \cdot
+    \mathbf{\tau} \\ \dot{\tau}/Wi + \overset{\nabla}\tau &= \left(\nabla
+    \mathbf{v}\right)^{T} + \nabla{\mathbf{v}}
 \end{align}
-With $\mathbf{v}$ as the total (base flow and disturbance) velocity and $\tau$ as the total stress in the polymeric fluid.
-The FENE-CR viscoelastic fluid has the advantage of being similarly easy to simulate, but also including a finite extensibility for the polymers.
-This leads to a stress which depends on a conformation tensor ($\mathbf{C}$) for the polymer dumbbells via a non-linear spring force:
+With $\mathbf{v}$ as the total (base flow and disturbance) velocity and $\tau$
+as the total stress in the polymeric fluid. The FENE-P viscoelastic fluid has
+the advantage of being similarly easy to simulate, but also including a finite
+extensibility for the polymers. This leads to a stress which depends on a
+conformation tensor ($\mathbf{C}$) for the polymer dumbbells via a non-linear
+spring force:
 
@@
 
-Again, we used Gauss-Labatto points in the wall normal direction and Fourier modes in the streamwise direction.
+Again, we used Gauss-Labatto points in the wall normal direction and Fourier
+modes in the streamwise direction.
 
@@
 
-At low Reynolds number, low $\beta$ and sufficiently large Weissenberg number we observe an instability across a range of streamwise disturbance wavenumbers.
-This leads us to suppose that this instability might be a plausible cause for a self-sustaining process in viscoelastic plane Couette flow, similar to that observed by Waleffe.
+At low Reynolds number, low $\beta$ and sufficiently large Weissenberg number
+we observe an instability across a range of streamwise disturbance wavenumbers.
+This leads us to suppose that this instability might be a plausible cause for a
+self-sustaining process in viscoelastic plane Couette flow, similar to that
+observed by Waleffe.
 
-The instability remains unchanged under variation of $\Delta$ at low $\Delta$, proving that it is a free shear instability.
-Although the instability appears to require some inertia in the fluid, it is still present for  $\Rey = 0.01$, far lower than the usual threshold of $\Rey = 1000$ for a Newtonian Kelvin-Helmholtz instability.
+The instability remains unchanged under variation of $\Delta$ at low $\Delta$,
+proving that it is a free shear instability. Although the instability appears
+to require some inertia in the fluid, it is still present for  $\Rey = 0.01$,
+far lower than the usual threshold of $\Rey = 1000$ for a Newtonian
+Kelvin-Helmholtz instability.
 
-We see an instability grow from around $k \sim 0.06$ and move to lower $k$ as the Weissenberg number increases (figure \ref{fig:dispersions_low_Re}).
-The height of the instability also increases with increasing Weissenberg number (figure \ref{fig:inf_low_Re}).
+We see an instability grow from around $k \sim 0.06$ and move to lower $k$ as
+the Weissenberg number increases (figure \ref{fig:dispersions_low_Re}). The
+height of the instability also increases with increasing Weissenberg number
+(figure \ref{fig:inf_low_Re}).
 
@@
     \end{subfigure}
-    \caption{a) Free shear version of the instability.
-Plot of the maximum growth rate against Wiessenberg number at $\Rey = 0.01$.
-b) Dispersion relations at various Weissenberg numbers to accompany the trend in figure a).}
+    \caption{a) Free shear version of the instability. Plot of the maximum
+	     growth rate against Wiessenberg number at $\Rey = 0.01$. b)
+	     Dispersion relations at various Weissenberg numbers to accompany
+	     the trend in figure a).}
 \end{figure}
 
-The dispersion relation saturates at $Wi \sim 50$ and remains approximately constant with increasing Weissenberg number.
-The dispersion relation for the instability remains broad in $k$ until $Wi \sim 100$ where a new eigenvector becomes dominant.
+The dispersion relation saturates at $Wi \sim 50$ and remains approximately
+constant with increasing Weissenberg number. The dispersion relation for the
+instability remains broad in $k$ until $Wi \sim 100$ where a new eigenvector
+becomes dominant.
 
@@
     \end{subfigure}
-    \caption{a) Free shear version of the instability.
-Plot of the maximum growth rate against Reynold's number with $\Wi=50$.
-b) Dispersion relations at various Reynold's numbers to accompany the trend in figure a).}
+    \caption{
+	a) Free shear version of the instability. Plot of the maximum growth
+	rate against Reynold's number with $\Wi=50$. b) Dispersion relations at
+	various Reynold's numbers to accompany the trend in figure a).
+    } 
     \end{figure}
 
-As the Reynold's number is reduced, new eigenvalues become dominant.
-Although the dominant eigenvalue changes the flow is still unstable, even down to $\Rey = 0.01$ (see figures \ref{fig:inf_vary_Re} and \ref{fig:dispersions_low_Wi}).
+As the Reynold's number is reduced, new eigenvalues become dominant. Although
+the dominant eigenvalue changes the flow is still unstable, even down to $\Rey
+= 0.01$ (see figures \ref{fig:inf_vary_Re} and \ref{fig:dispersions_low_Wi}).
 
@@
 
-If we examine the eigenvectors of the instability, we see that there are very large polymer stresses in the $\pm \Delta$ region.
-This corresponds to the large shear rate brought about as the two flows pass each other.
-Examining the flow field, we see that there are large vortices arranged with opposite rotational directions above and below the shear region which extend almost to the walls.
+If we examine the eigenvectors of the instability, we see that there are very
+large polymer stresses in the $\pm \Delta$ region. This corresponds to the
+large shear rate brought about as the two flows pass each other. Examining the
+flow field, we see that there are large vortices arranged with opposite
+rotational directions above and below the shear region which extend almost to
+the walls.
 
@@
     \end{subfigure}
-    \caption{a) Streamfunction of the largest eigenfunction of the instability when $\Rey = 0.1$, $\Wi =100$, $\Delta = 0.005$.
-Red is positive (streamlines of the flow point clockwise around the contours), Blue is negative (streamlines of the flow point anticlockwise around the contours) b) xx stress for the same instability.}
+    \caption{
+	a) Streamfunction of the largest eigenfunction of the instability when
+	$\Rey = 0.1$, $\Wi =100$, $\Delta = 0.005$. Red is positive
+	(streamlines of the flow point clockwise around the contours), Blue is
+	negative (streamlines of the flow point anticlockwise around the
+	contours) b) xx stress for the same instability.
+    }
 \end{figure}
 
-Dependence of the instability on the channel walls persists at very small $\Delta$.
-We believe that this is due to the inertial effects at low Reynold's number being so weak.
-This means it is very easy to move the fluid even in at the shear rate present far from the centre of the channel.
-I think the instability generated by the elasticity of the fluid needs the walls to dampen it for some reason.
-The fluid moves more as one block because it has high a viscosity.
-This one block is easier to get going because of the low inertia it is also easy to stop.
-It then needs something solid to kill the fluid motion, this is either a very large body of stationary fluid or a wall.
-The inertial effects must reduce the velocity of the fluid far from the walls so that it can feel the effect of the streamwise component of the velocity gradient.
+Dependence of the instability on the channel walls persists at very small
+$\Delta$. We believe that this is due to the inertial effects at low Reynold's
+number being so weak. This means it is very easy to move the fluid even in at
+the shear rate present far from the centre of the channel. I think the
+instability generated by the elasticity of the fluid needs the walls to dampen
+it for some reason. The fluid moves more as one block because it has high a
+viscosity. This one block is easier to get going because of the low inertia it
+is also easy to stop. It then needs something solid to kill the fluid motion,
+this is either a very large body of stationary fluid or a wall. The inertial
+effects must reduce the velocity of the fluid far from the walls so that it can
+feel the effect of the streamwise component of the velocity gradient.
 
@@
     \includegraphics[width=\textwidth]{KH_vary_delta}
-    \caption{Dispersion relations for various values of $\Delta$ at $\Rey = 0.1$, $\Wi = 100$.
-The sensitivity to the walls seems only to increase the strength of the instability.
-Even when the system is insensitive to the walls, at $\Delta= 0.0125$, there is still an instability present.}
+    \caption{
+    Dispersion relations for various values of $\Delta$ at $\Rey = 0.1$, $\Wi =
+    100$. The sensitivity to the walls seems only to increase the strength of
+    the instability. Even when the system is insensitive to the walls, at
+    $\Delta= 0.0125$, there is still an instability present.
+    }
     \label{fig:walls_dependence}
@@
     \includegraphics[width=\textwidth]{psi_high_delta}
-    \caption{Streamfunction of the eigenfunction of the instability at $\Delta = 0.1$, $\Wi = 100$, $\Rey=0.1$. The magnitude is scaled by the xx stress in the centre of the channel.}
+    \caption{
+    Streamfunction of the eigenfunction of the instability at $\Delta = 0.1$,
+    $\Wi = 100$, $\Rey=0.1$. The magnitude is scaled by the xx stress in the
+    centre of the channel.
+    }
     \label{fig:psi_high_delta}
@@
 
-It is difficult to see the instability at $\Rey = 0$.
-As the Reynold's number is reduced the walls become more important to the instability.
-In order to remove the dependence on the walls and recover a free shear instability it is necessary to move them further away.
-This problem gets worse at lower $\Rey$.
-By introducing just a very small contribution from inertia, we can remove the dependence on the walls.
-This is why all of our results are taken for $\Rey \leq 0.1$ on the length scale of the instability.
+It is difficult to see the instability at $\Rey = 0$. As the Reynold's number
+is reduced the walls become more important to the instability. In order to
+remove the dependence on the walls and recover a free shear instability it is
+necessary to move them further away. This problem gets worse at lower $\Rey$.
+By introducing just a very small contribution from inertia, we can remove the
+dependence on the walls. This is why all of our results are taken for $\Rey
+\leq 0.1$ on the length scale of the instability.
 
-The reason we have have the simulation with the walls at all is because of the implications for the plane Couette problem.
-The Kelvin-Helmholtz instability in the Newtonian problem takes place on a length scale of about 10\% of the width of the channel, or $\Delta = 0.1$ (a guess).
-The viscoelastic Kelvin-Helmholtz instability is sensitive to the walls at this $\Delta$ and a $\Rey \lesssim 1$ (see figure \ref{fig:vary_Re_delta_conv}).
-This means that on the scale of the channel, $\Rey \gtrsim 10$ for the walls not to affect the instability.
-So, the important results for the purely elastic instability from the point of view of the plane Couette problem are probably those for which the walls are relevant.
+The reason we have have the simulation with the walls at all is because of the
+implications for the plane Couette problem. The Kelvin-Helmholtz instability in
+the Newtonian problem takes place on a length scale of about 10\% of the width
+of the channel, or $\Delta = 0.1$ (a guess). The viscoelastic Kelvin-Helmholtz
+instability is sensitive to the walls at this $\Delta$ and a $\Rey \lesssim 1$
+(see figure \ref{fig:vary_Re_delta_conv}). This means that on the scale of the
+channel, $\Rey \gtrsim 10$ for the walls not to affect the instability. So, the
+important results for the purely elastic instability from the point of view of
+the plane Couette problem are probably those for which the walls are relevant.
 
@@
     \includegraphics[width=0.7\textwidth]{vary_Re_delta_conv}
-    \caption{The blue line is the data from the stretched code and the green line is the $\Delta = 0.1$ data.
-By $\Rey = 1$ it is clear that the Reynold's number is sufficient such that the walled system behaves as though it were insensitive to the walls.}
+    \caption{
+	The blue line is the data from the stretched code and the green line is
+	the $\Delta = 0.1$ data. By $\Rey = 1$ it is clear that the Reynold's
+	number is sufficient such that the walled system behaves as though it
+	were insensitive to the walls.
+    }
     \label{fig:vary_Re_delta_conv}
@@
 
-At $\Delta = 0.1$ we see the same instability as that seen in the completely free case.
+At $\Delta = 0.1$ we see the same instability as that seen in the completely
+free case.
 
@@
 \end{subfigure}
-\caption{a) The change in the height of the dispersion relation as $\Wi$ is increased at $\Rey = 0$ with $\Delta = 0.1$.
-This instability must be entirely elastic in nature.
-b) The change in the height of the dispersion relation as the Reynolds number is reduced at $\Wi=5$.
-At low $\Rey$ the instability is clearly still present for large polymer concentrations, consistent with purely elastic turbulence with $\Delta = 0.1$.
-c) The value of the Weissenberg number at which the velocity profile becomes unstable against $\beta$ at $\Delta = 0.1$.
-The onset of the purely elastic instability moves to higher $Wi$ as $\beta$ increases.}
+\caption{
+a) The change in the height of the dispersion relation as $\Wi$ is increased at
+$\Rey = 0$ with $\Delta = 0.1$. This instability must be entirely elastic in
+nature. b) The change in the height of the dispersion relation as the Reynolds
+number is reduced at $\Wi=5$. At low $\Rey$ the instability is clearly still
+present for large polymer concentrations, consistent with purely elastic
+turbulence with $\Delta = 0.1$.  c) The value of the Weissenberg number at
+which the velocity profile becomes unstable against $\beta$ at $\Delta = 0.1$.
+The onset of the purely elastic instability moves to higher $Wi$ as $\beta$
+increases.
+}
 \end{figure}
@@
 
-The finite extensibility version of the model gives good agreement with the Oldroyd-B version.
-Shorter lengths bring about a larger instability but do not delay it to higher Weissenberg number.
-Otherwise similar dispersion relations are observed with a similar dependence on the distance to the walls (figure \ref{fig:FENE_low_Re}).
+The finite extensibility version of the model gives good agreement with the
+Oldroyd-B version. Shorter lengths bring about a larger instability but do not
+delay it to higher Weissenberg number. Otherwise similar dispersion relations
+are observed with a similar dependence on the distance to the walls (figure
+\ref{fig:FENE_low_Re}).
 
@@
     \includegraphics[width=0.7\textwidth]{FENE_purely_elastic}
-    \caption{The FENE-CR model fluid at $\Rey = 0$  when $\Delta = 0.1$. Results are consistent with figure \ref{fig:KH_purely_elastic}.}
+    \caption{
+    The FENE-P model fluid at $\Rey = 0$  when $\Delta = 0.1$. Results are
+    consistent with figure \ref{fig:KH_purely_elastic}.
+    }
     \label{fig:FENE_low_Re}
@@
     \includegraphics[width=0.7\textwidth]{high_Re_vary_delta}
-    \caption{ Dispersion relations for various values of $\Delta$ and $\Rey = 1000$, $\Wi = 0.01$.
-When results are rescaled for delta, The instability is found to be insensitive to the width of the instability relative to the wall at this combination of Reynold's number and Wiessenberg number.}
+    \caption{ 
+    Dispersion relations for various values of $\Delta$ and $\Rey = 1000$, $\Wi
+    = 0.01$. When results are rescaled for delta, The instability is found to
+    be insensitive to the width of the instability relative to the wall at this
+    combination of Reynold's number and Wiessenberg number.
+    }
     \label{fig:delta_dispersion}
@@
 
-We see drag reduction using the Oldroyd-B model. It is not clear whether or not the maximum drag reduction asymptote is present (figure \ref{fig:KH_drag_reduction}).
+We see drag reduction using the Oldroyd-B model. It is not clear whether or not
+the maximum drag reduction asymptote is present (figure
+\ref{fig:KH_drag_reduction}).
 
@@
     \includegraphics[width=0.7\textwidth]{KH_high_Re_vary_Wi}
-    \caption{Peak growth rate against Wiessenberg number at $\Rey = 1000$, $\Delta = 0.1$ The height of the dispersion relation is reduced for the Kelvin-Helmholtz instability as the Weissenberg number is increased.
-The grey dashed line is the height of the dispersion relation for the Newtonian fluid.
-The decrease in $\lambda_{r}$ corresponds to increased stability of the base flow and so confirms the presence of drag reduction in this system.}
+    \caption{
+	Peak growth rate against Wiessenberg number at $\Rey = 1000$, $\Delta =
+	0.1$ The height of the dispersion relation is reduced for the
+	Kelvin-Helmholtz instability as the Weissenberg number is increased.
+	The grey dashed line is the height of the dispersion relation for the
+	Newtonian fluid. The decrease in $\lambda_{r}$ corresponds to increased
+	stability of the base flow and so confirms the presence of drag
+	reduction in this system.
+    }
     \label{fig:KH_drag_reduction}
@@
 
-In conclusion, we can say that there is a Kelvin-Helmholtz like instability for purely elastic shear flows.
-The unstable region is much larger than that seen in Newtonian fluids relative to the region of shear.
-The wavenumber of the instability is much smaller in the viscoelastic case ($k<0.06$), suggesting a larger minimal flow unit is required in viscoelastic fluids.
-This instability is enhanced by introducing a finite extensibility to the polymers.
-The instability has grown to its maximum by the time it reaches an effective Weissenberg number $ Wi \sim 50$ after which it is saturated.
-The instability is also strongly dependent on the walls at low effective Reynold's number.
+In conclusion, we can say that there is a Kelvin-Helmholtz like instability for
+purely elastic shear flows. The unstable region is much larger than that seen
+in Newtonian fluids relative to the region of shear. The wavenumber of the
+instability is much smaller in the viscoelastic case ($k<0.06$), suggesting a
+larger minimal flow unit is required in viscoelastic fluids. This instability
+is enhanced by introducing a finite extensibility to the polymers. The
+instability has grown to its maximum by the time it reaches an effective
+Weissenberg number $ Wi \sim 50$ after which it is saturated. The instability
+is also strongly dependent on the walls at low effective Reynold's number.
 

### 2015-07-03 paper/paper.tex
D_domain.py : added cline support

@@
 %	paper.tex	Toby Searle
-%	Last modified: Wed 14 May 22:10:55 2014
+%	Last modified: Fri  6 Jun 15:39:17 2014
 %	using jfm template
@@
 It was long thought that the elasticity of a viscoelastic fluid only served to
-dampen instability. This view stems from early results showing that drag ina
+dampen instability. This view stems from early results showing that drag in a
 turbulent Newtonian flow can be reduced by the addition of small amounts of
-viscoelastic fluid (\cite{Toms1977}). Although drag reduction has recieved a
-lot of attention in the past the studies above give reason to believe that
-there is a potentially more prevalent and useful phenomenon at work in
-viscoelastic fluids. It seems that viscoelastic turbulence is present at very
+viscoelastic fluid (\cite{Toms1977}). Although drag reduction has received a
+lot of attention in the past, studies on turbulence without inertia give reason
+to believe that there may be purely elastic instabilities present in elastic
+fluids relevent to industry.  This purely elastic turbulence is present at very
 low Reynolds number, where it is driven by the elasticity of the polymeric
@@
 Kelvin-Helmholtz instability leading to a symmetry bifurcation to a three
-dimensional perturbation which in turn re-energises the original streamwise
-rolls. This exact solution to the Navier-Stokes equations is thought to be a
-component of the transition to turbulence. In 1998 Waleffe constructed a
-bifurcation diagram for this exact solution \cite{Waleffe1998} containing what
-looks like a bifurcation from infinity. This is the behaviour expected of the
-transition to turbulence in Couette flow.
+dimensional flow. Finally, the nonlinear effects due to this instability
+re-energises the original streamwise rolls. This exact solution to the
+Navier-Stokes equations is thought to be a component of the transition to
+turbulence. In 1998 Waleffe constructed a bifurcation diagram for this exact
+solution \cite{Waleffe1998} containing what looks like a bifurcation from
+infinity, just the behaviour expected of the transition to turbulence in plane
+Couette flow.
 
@@
 flows is the Weissenberg number, which is the ratio of the normal stress to the
-shear stress of the polymer component of the fluid $Wi = \frac{N_{1}}{\sigma}$.
-For small shear rates, this is approximately equivalent to $De$, the Deborah
-number, so that $Wi \approx De = \lambda \dot{\gamma}$ where $\dot{\gamma}$ is
-the shear rate.
+shear stress of the polymer component of the fluid $Wi = \frac{N_{1}}{\sigma} =
+\lambda \dot{\gamma}$ where $\dot{\gamma}$ is the shear rate.
 
@@
 number of Fourier modes, $k$ is the streamwise wavenumber of the disturbance
-and $\lambda$ is the growth rate of the mode. This code uses two domains of
+and $\lambda$ is the growth rate of the mode. This program uses two domains of
 pseudo-spectral points to give increased resolution in the centre of the
@@
 $\Delta$. We believe that this is due to the inertial effects at low Reynold's
-number being so weak. This means it is very easy to move the fluid even in at
+number being so weak. This means it is very easy to move the fluid even at
 the shear rate present far from the centre of the channel. I think the
 instability generated by the elasticity of the fluid needs the walls to dampen
-it for some reason. The fluid moves more as one block because it has high a
-viscosity. This one block is easier to get going because of the low inertia it
-is also easy to stop. It then needs something solid to kill the fluid motion,
-this is either a very large body of stationary fluid or a wall. The inertial
-effects must reduce the velocity of the fluid far from the walls so that it can
-feel the effect of the streamwise component of the velocity gradient.
+it for some reason.
 
@@
 \end{subfigure}
+~
+\begin{subfigure}[b]{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{fin_dispersions_Wi50}
+    \caption{}
+    \label{fig:KH_finite_dispersions}
+\end{subfigure}
 \caption{
@@
 The onset of the purely elastic instability moves to higher $Wi$ as $\beta$
-increases.
+increases. d) Dispersion relations at Wi =50 for $\Delta =0.1$.
 }
@@
 larger minimal flow unit is required in viscoelastic fluids. This instability
-is enhanced by introducing a finite extensibility to the polymers. The
-instability has grown to its maximum by the time it reaches an effective
-Weissenberg number $ Wi \sim 50$ after which it is saturated. The instability
-is also strongly dependent on the walls at low effective Reynold's number.
+is enhanced slightly by introducing a finite extensibility to the polymers but
+remains of essentially the same form. The instability has grown to its maximum
+by the time it reaches an effective Weissenberg number $ Wi \sim 50$ after
+which it is saturated. The instability is also strongly dependent on the walls
+at low effective Reynold's number.
 

### 2015-07-03 D_domain.py

@@ -3,17 +3,46 @@
 from scipy import *
 from scipy.linalg import inv, solve, eig, det
 import pickle
-
+import argparse
 
 ##------------------------------------
 
 M = 100
 
-Re = 10000
-Wi = 0.01
-bbeta = 0.1
+Re = float(1000.0)
+Wi = float(1.2)
+bbeta = float(0.1)
+kxLo = 0.1
+kxHi = 10.0
+kxStep = 0.1 
 
 _delta = 0.1
+
+argparser = argparse.ArgumentParser()
+
+argparser.add_argument("-M", type=int, default=M, 
+                help='Override Number of Chebyshev modes in the file')
+argparser.add_argument("-Re", type=float, default=Re, 
+                help="Override Reynold's number in the file") 
+argparser.add_argument("-b", type=float, default=bbeta, 
+                help='Override beta of the file')
+argparser.add_argument("-Wi", type=float, default=Wi, 
+                help='Override Weissenberg number of the file')
+argparser.add_argument("-kxLo", type=float, default=kxLo, 
+                help='Override initial wavenumber of the file')
+argparser.add_argument("-kxHi", type=float, default=kxHi, 
+                help='Override final wavenumber of the file')
+argparser.add_argument("-kxStep", type=float, default=kxStep, 
+                help='Override step wavenumber of the file')
+
+args = argparser.parse_args()
+M = args.M
+Re = args.Re
+Wi = args.Wi
+bbeta = args.b
+kxLo = args.kxLo
+kxHi = args.kxHi
+kxStep = args.kxStep
 
 ##------------------------------------
 
@@ -70,7 +99,7 @@ U0down_p = dot(D1,U0down)
 
 
 f=open('b{bbeta}-M{M}-Re{Re}-Wi{Wi}.dat'.format(bbeta=bbeta, M=M, Re=Re,  Wi=Wi),'w')
-for alpha in r_[0.1:10.0:0.1]:
+for alpha in r_[kxLo:kxHi+kxStep:kxStep]:
 
     print alpha
 

### 2016-01-22 paper/paper.tex
updated the paper with an over the top lit review.

@@
 %	paper.tex	Toby Searle
-%	Last modified: Fri  6 Jun 15:39:17 2014
+%	Last modified: Fri 22 Jan 15:20:25 2016
 %	using jfm template
@@
 \usepackage{caption,subcaption, mathtools} % add my own packages
+\usepackage[section]{placeins}
 \graphicspath{ {./images/} }
@@
 
-Turbulence without inertia in viscoelastic fluids has generated much interest
-since it was discovered in Taylor-Couette flow by Larson, Shaqfeh and Muller in
-1990 \cite{Larson1990}. As well as this numerical and experimental study of
-Taylor-Couette flow, Groisman and Steinberg \cite{Groisman2000} discovered
-turbulence in viscoelastic fluids between two counter rotating plates.
-
 It was long thought that the elasticity of a viscoelastic fluid only served to
@@
 turbulent Newtonian flow can be reduced by the addition of small amounts of
-viscoelastic fluid (\cite{Toms1977}). Although drag reduction has received a
-lot of attention in the past, studies on turbulence without inertia give reason
-to believe that there may be purely elastic instabilities present in elastic
-fluids relevent to industry.  This purely elastic turbulence is present at very
-low Reynolds number, where it is driven by the elasticity of the polymeric
-fluid rather than its inertia.
+viscoelastic fluid \citep{Toms1977}. Although drag reduction has been studied
+for a long time, studies on turbulence without inertia \citep{Larson1990,
+Groisman2000} give reason to believe that there are purely elastic bulk
+instabilities present in elastic fluids relevant to industry.  This purely
+elastic turbulence is present at very low Reynolds number, where it is driven
+by the elasticity of a polymeric flow rather than its inertia.
+
+\subsection{Exact coherent structures and Turbulence}
 
 In 1997 Fabian Waleffe identified a Newtonian self sustaining process in plane
-Couette flow \cite{Waleffe1997}. Streamwise rolls redistribute the streamwise
+Couette flow \citep{Waleffe1997}. Streamwise rolls redistribute the streamwise
 velocity into a streaky flow. This streaky flow is unstable through a
@@
 turbulence. In 1998 Waleffe constructed a bifurcation diagram for this exact
-solution \cite{Waleffe1998} containing what looks like a bifurcation from
+solution \citep{Waleffe1998} containing what looks like a bifurcation from
 infinity, just the behaviour expected of the transition to turbulence in plane
@@
 Using this work in Newtonian fluid dynamics as a template for the structure of
-purely elastic turbulence reveals a similar pattern of streaks and, hopefully,
-a similar self-sustaining process \cite{US!}. An important step towards
+purely elastic turbulence reveals a similar pattern of streaks and, a similar
+self-sustaining process \citep{Searle2016a}. An important step towards
 explaining this process in purely elastic flows is establishing the mechanism
-by which the streaks become unstable. Presumably, this will also be a
-Kelvin-Helmholtz instability as the streaks shear with the rest of the fluid.
-The Kelvin-Helmholtz instability is also often integral to the transition to
-turbulence in Newtonian fluids. It is hoped that by finding a purely elastic
-version of this instability, we might be able to probe one of the important
-mechanisms for the transition to purely elastic turbulence. To explore this
-mechanism in the purely elastic regime we have constructed a simple model
-system of a shearing viscoelastic fluid.
+by which the streaks become unstable. It seems this is also a Kelvin-Helmholtz
+instability as the streaks shear with the rest of the fluid.  The
+Kelvin-Helmholtz instability is integral to the transition to turbulence in
+Newtonian fluids. It is hoped that by finding a purely elastic version of this
+instability, we might be able to probe one of the important mechanisms for the
+transition to purely elastic turbulence, One that is presumably present in
+other contexts, such as the oscillatory channel flow problem of
+\cite{Searle2016b}. To explore this mechanism in the purely elastic regime we
+have constructed a simple model system of a shearing viscoelastic fluid.
 
-The key dimensionless number for turbulence without inertia in viscoelastic
-flows is the Weissenberg number, which is the ratio of the normal stress to the
-shear stress of the polymer component of the fluid $Wi = \frac{N_{1}}{\sigma} =
-\lambda \dot{\gamma}$ where $\dot{\gamma}$ is the shear rate.
+\subsection{Shear flow instabilities of Non-Newtonian fluids}
+
+The shear flow instability we are interested in relates to many other
+instabilities in both Newtonian and Non-Newtonian fluids where the fluid
+inertia is not dominant. These instabilities mostly relate to a flow of two
+fluids with differing properties and an instability at the interface between
+them. I will break them up into 4 classes, Newtonian viscously stratified, shear
+thinning viscously stratified, Shear banded and Elastically stratified
+instabilities.
+
+\subsection{Viscous two layer Newtonian shear flows}
+
+In 1967 Yih \citep{Yih1967} performed a long wavelength analytic stability
+calculation of two Newtonian fluids in two-layer viscously stratified plane
+Couette and plane Poiseuille flows. This instability was shown to be an
+instability of the interface. Many subsequent authors copy Yih's technique and
+notation.
+
+In 1983 the viscous stratification instability was studied in a flow which is a
+close relation to ours. Hooper and Boyd tackle the Newtonian two-layer viscous
+instability \citep{Hooper1983} in a flow of two fluids both in unbounded
+Couette flow with a jump in the shear rate at the interface. They use both
+numerical and shortwave asymptotic techniques to obtain that the shortwave
+instability is always unstable without surface tension. Hinch \citep{Hinch1984}
+explained the mechanism of the Hooper and Boyd viscous stratification of above.
+Says that this instability ought to be unimportant since it will be damped by
+surface tension.
+
+Renardy \citep{Renardy1985} repeats both the Yih and the Hooper Newtonian fluid
+problems but does a full numerical linear stability analysis using a
+Chebyshev-Tau method of Orszag. The problems with and without walls yield
+approximately the same critical Reynold's number. Above this the unstable
+eigenmodes for each problem are approximately the same. They include surface
+tension, density, viscosity, and volume fraction ratio.  \citet{Hooper1985}
+then looked at a thin film on top of another Newtonian fluid via a long
+wavelength linear stability analysis. Suggest a mechanism based on the lag
+between phases of velocity and phase of interface.  \citet{Hooper1985} then
+looked at the nonlinear stability of stratified Couette-Poiseuille flow. They
+performed a weakly nonlinear analysis to transform the problem to a
+Kuramoto-Sivishinsky equation and they don't find any travelling waves. Renardy
+\citep{Renardy1989} also looked at this nonlinear stability problem and found
+small amplitude travelling waves.  \citet{Yiantsios1988} do a numerical linear
+stability of two superposed Newtonian fluids, looking at the short wave
+asymptotics like Hooper and Boyd but include surface tension and gravitational
+effects.
+
+\subsection{Viscous two layer shear thinning Non-Newtonian shear flows}
+
+Waters \citep{Waters1983} does a long wavelength linear stability analysis for
+shear thinning power law fluids in plane Couette flow and claims that shear
+thinning has a large effect. Wong and Jeng \citep{Wong1987} do a long wave
+linear stability analysis for co-extruded pipe flow of Ellis model shear
+thinning non-Newtonian fluids. Find that if inner/outer fluid is more viscous
+shear thinning will stabilize/destabilize the flow.
+
+Weinstein \citep{Weinstein1990} examined the flow of shear thinning fluids down
+and incline. Use the Carreau model and look at multilayered flow using analytic
+asymptotics as well as a finite difference shooting method for the eigenvalues.
+Find that effects of shear-thinning are complicated.
+
+Pinarbasi \citep{Pinarbasi1995} in 1995 looked at two shear thinning models for
+the 2-layer Poiseuille flow, Carreau-Yasuda and the Bingham like model. They
+use a pseudospectral method eigensolver to show that shear thinning
+destabilizes.
+
+\subsection{shear banded Non-Newtonian shear flows}
+
+McLeish \citep{McLeish1987} look at the stability of the interface between two
+phases of linear polymer melts using the Doi-Edwards model. Show that a
+shear-banded state has an unstable interface between the fluids. Claims that
+the normal stress effect determines instability. Renardy \citep{Renardy1995a}
+returned to this problem to examine how a shear banding instability might be
+responsible for spurt in two layer Couette flow.  Used the Johnson-Segalman
+model with a pseudospectral eigenvalue solver.
+
+Mike Graham does a review of the sharkskin instability in \citep{Graham1999}
+which discusses a lot of previous work and which I found interesting as an
+insight into how the wall-slip and shear-banding instability factions think
+about melt fracture.
+
+Fielding \citep{Fielding2005} looks at the linear stability of the shear-banded
+flow problem. Use the Johnson-Segalman model, finds that the shear banded state
+can be linearly unstable. The mechanism is not clear. Then Wilson
+\citep{Wilson2006} has a nice little article discussing how an instability can
+depend or not on changing the constitutive model. Using a small amount of
+diffusion in the diffusive Johnson-Segalman model doesn't effect the
+instability even though the limit of zero diffusion is singular.
+
+Fielding and Wilson \citep{Fielding2010} look at the shear banding interfacial
+instability in plane Poiseuille flow via the diffusive Johnson Segalman model.
+They do both a numerical linear stability and find nonlinear travelling
+waves.
+
+\citet{Nicolas2012} look at the shear banding instability, this
+time in Taylor-Couette flow via the diffusive Johnson-Segalman model. Find a
+previously unnoticed azimuthally wavy bulk instability. I particularly enjoyed
+the comparison with the co-rotating problem where there is no shear band.
+
+\subsection{Elastic multilayer Non-Newtonian shear flows}
+
+The study of an elastically stratified shear flow began in 1969 when Li
+\citep{Li1969} examined two Oldroyd-B fluids with different viscosities and
+elasticities. This was a asymptotic expansion of the linear stability to long
+wave length disturbances along the same lines as \citet{Yih1967}. They found
+that elasticity can both stabilize and destabilise the flow. This study along
+with some subsequent ones \citep{Waters1987, Anturkar1990}, used an incorrect
+boundary condition for the traction at the interface between the fluids. Chen
+\citep{Chen1991b} later corrects this mistake, and subsequent studies including
+all the papers by Renardy contain the correct boundary condition.
+
+\citet{Khan1976} studied an experimental realisation of the plane Poiseuille
+flow of two viscoelastic fluids in a duct. They find that the influence of
+viscosity dominates over that of elasticity stratification in their flow. They
+attempt some analytic and numerical work on the Coleman-Noll second order fluid
+to back up their experiments, but they use the wrong interface traction
+boundary condition and their methods look dodgy. In \citet{Khan1977} the same
+authors publish a flawed theory paper using the same constitutive model.
+
+\citet{Han1985} perform a co-extrusion experiment on a pipe flow of two polymer
+melts. Mainly this is just cross-sections of the extrudate showing that lower
+viscosity component wraps higher viscosity component. They have no
+birefringence data but somehow they do get some normal stress data. They claim
+that the viscous stratification is more important than the elastic for their
+system.
+
+Waters and Keeley \citep{Waters1987} use an Newtonian fluid and power-law shear
+thinning Oldroyd-B fluid in stratified plane Couette flow. They do long wave
+asymptotics. Again, this paper uses the incorrect traction boundary condition
+at the interface.  Renardy \citep{Renardy1988} looked at the stability of the
+interface of two layer Couette flow of UCM fluids via short wave asymptotics
+and a Chebyshev-tau method. They find elastic differences between the layers
+alone can stabilize or destabilize the flow. Claim that elasticity can enhance
+the lubrication effect.
+
+Anturkar \citep{Anturkar1990} do a problem involving multiple viscoelastic
+layers in planar co-extrusion. Do numerical and analytical linear stability
+analysis on the Oldroyd-B + Carreau shear thinning model.  Again they use the
+incorrect traction boundary condition at the interfaces between the fluids.
+
+Chen \citep{Chen1991a} looked at the elastic instability in the co-extrusion of
+UCM fluids in a pipe flow. He performed a long wavelength linear stability
+analysis and found an elastic instability. In \citep{Chen1991b} he then went on
+to look at the Couette flow of viscoelastic fluids and corrects the error in
+previous papers \citep{Li1969, Waters1987, Anturkar1990} for the interface
+traction boundary condition. Previous authors took the boundary condition on
+the unperturbed interface between the fluids, rather than the perturbed one.
+It is demonstrated that you can get a purely elastic linear instability via a
+long wave asymptotic analysis. The linear stability of a two layer film of UCM
+fluids down an inclined plane was examined by a long wave asymptotic analysis
+as well as using a pseudospectral method \citep{Chen1992a}. The result is that
+there is an instability when the more elastic component is next to the wall.
+The shortwave instability of the pipe co-extrusion flow is examined in
+\citep{Chen1992b} using the UCM model. Hypothesis formed about the origin of
+sharkskin being due to differing elastic properties of the fluid close to the
+wall.  Find growth rates are in fact higher for the elastic instabilities than
+the viscous Newtonian ones in some settings. Many of the previous viscoelastic
+references are mentioned in \citep{Larson1992}.
+
+\citet{Su1992a} find a purely elastic interfacial instability in superposed
+Poiseuille flow of Oldroyd-B fluids. This is a Plane Poiseuille flow version of
+\citep{Chen1992a}. Long wave asymptotic and some numerical linear stability
+using a pseudospectral technique. Show that strength of elastic instability is
+comparable to that of the Newtonian viscous one. They have some low $\beta$ low
+$\Rey$ results. In \citet{Su1992b} they look at converging and parallel channel
+co-extrusion of two truncated power law Oldroyd-B fluids.  Find that shear
+thinning has a bigger effect than elasticity.  Many phase diagrams.
+
+Hinch, Harris and Rallison \citep{Hinch1992} provide a general understanding of
+the mechanism behind Chens pipe elastic stratification instability
+\citep{Chen1991a}. They look for an arbitrary constitutive model and include
+the effects of jumps in the first and second normal stress differences in order
+to expose how the traction boundary condition can bring about instability.
+
+Wilson and Khomami \citep{Wilson1992, Wilson1993a, Wilson1993b} performed a
+three part experimental investigation of the interfacial instabilities in
+multilayered flow of viscoelastic liquids. They can generate disturbances of
+particular wavelengths in their setup, to probe the dispersion relation. The
+compare with the Oldroyd-B with power law shear thinning fluid and find
+reasonable agreement. They also examine nonlinear effects \citep{Wilson1993a}
+using the same apparatus and they find that there are shear stress imbalances
+in their flows supporting the proposed instability mechanism, and they show
+that differences in the normal stress difference enough to change the
+dispersion relation, lending support to the presence of an elastic instability.
+Find a supercritical bifurcation and it looks like the interface rolls up in a
+Kelvin-Helmholtz like way. They say they see things similar to predictions made
+in \citet{Renardy1989}. No subcritical bifurcation is observed. Complex 3D
+pattern occurs which made it difficult to look at the purely elastic effects
+divorced from the viscous stratification effects. For compatible polymers
+\citep{Wilson1993b} they observe suppression of the growth rate due to diffusive
+and convective mixing.
+
+Chen \citep{Chen1993} looked at the stability of the interface in the pipe
+co-extrusion experiment via pseudospectral eigenvalue solver using the
+Oldroyd-B model. Discusses two kinds of interfacial instability, capillary
+instability due to surface tension and elastic due to first normal stress
+difference.  Explains again the Hinch mechanism, but perhaps easier to
+understand. The Capillary instability can be stabilised by the elasticity
+stratification. In 1994 \citep{Chen1994} Chen examines the instability of a
+large $\Rey$ flow of a Newtonian fluid over an Oldroyd-B fluid. There is an
+asymptotic expansion for the linear stability in the short wave limit.
+
+\citet{Azaiez1994} do the linear stability of a free shear flow of the
+Oldroyd-B, co-rotational Jefferys and Gisekus fluids. Find suppression of the
+Newtonian Kelvin-Helmholtz instability. They do asymptotic long wave linear
+stability such that the Reynold's number is small but finite and the
+Weissenberg number is large with a constant elasticity. They also do a
+numerical linear stability via an orthogonal shooting algorithm. In the
+appendix of this paper Hinch \citep{Azaiez1994} takes the long wavelength limit
+of their problem in a far more elegant way and exposes a stabilisation
+mechanism based on elastic hoop stresses in the curved streamlines.
+
+Renardy returned to the two-layer flow of the elastically stratified UCM model
+to look at the weakly nonlinear problem \citep{Renardy1995b}. They redid the
+numerical linear stability analysis and then found the bifurcations were
+supercritical. Coward and Renardy \citep{Coward1997} looked at a thin film
+core-annular pipe flow of UCM fluids via a weakly nonlinear analysis.
+
+Wilson and Rallison \citep{Wilson1997} looked at the short wave instability of
+the elastically stratified two layer plane Poiseuille flow of Oldroyd-B liquids.
+This was an asymptotic linear stability analysis for short waves. Possibly this
+is a different mechanism than the Hinch one because it happens for short
+wavelengths.
+
+In 1997, Laure \citep{Laure1997} looked at the linear stability of a multilayer
+plane Poiseuille flow of Oldroyd-B fluids. They did a long wave asymptotic
+analysis in the $\Rey \rightarrow 0, \Wi \neq 0$ limit. They also did some
+numerical calculations. They assume that viscous and elastic effects are
+additive in the dispersion relation. \citet{Ganpule1998} thinks this is wrong.
+In the \citet{Ganpule1998} paper they also look at four models, UCM, multimode
+Gisekus, Gisekus and modified PTT. They repeat the linear stability analysis
+and do a perturbation energy analysis using the UCM model. They also compare
+all their results to experiments in \citep{Khomami1997}. Those experiments are
+performed on the multilayer pressure driven flow of polymeric melts. In
+\citet{Ganpule1999} they published a similar theory paper but on just two
+layers in more detail rather than a multilayered flow. Show how the Oldroyd-B
+is qualitative match to experiments but gets the wrong growth rates. Attribute
+this to shear thinning of the experiment in \citep{Khomami1997}. Again they use
+an energy disturbance analysis to study the mechanism and it seems they agree
+with the Hinch mechanism of \citep{Hinch1992}.  It seems whatever the mechanism
+they settle on in this paper, Miller and Rallison disagree with it in
+\citep{Miller2007a}.
+
+\citet{Scotto1999} looks at the linear stability of a three layer Poiseuille
+flow of Oldroyd-B fluids using a Chebyshev-tau method. I think they do the
+dodgy thing of adding together affects from the viscous and elastic terms in
+the dispersion relation.
+
+Renardy \citep{Renardy1999} looks at the spanwise instability between two
+Gisekus Couette layers with only a second normal stress jump. They use a fully
+spectral Chebyshev-Tau method and find that short waves are always unstable and
+without surface tension whereas long waves depend on the depth ratio.
+
+\citet{Wilson1999a} looked at the instability of channel flows of
+elastic liquids having continuously stratified polymer concentration and $\Wi$.
+They look at the long wavelength limit of the Oldroyd-B model using what I
+think is a similar method to to Hinch in \citet{Azaiez1994}. Then they do
+linear stability using a shooting Newton-Rhaphson method. They compare the
+results of the Oldroyd-B model to a White-Mieztner fluid. Conclude that
+blurring of the interface between elasticities would suppress the instability,
+so it is not likely to be responsible for sharkskin. Their instability looks to
+be the closest to ours as far as I can gather.
+
+\citet{Wilson1999b} concerns the structure of the eigenvalue spectrum
+for the instability of UCM and Oldroyd-B fluids in the two-layer channel flow
+problem. Possibly a useful comparison there for our eigenvalue spectra.
+
+Khomami et al performed linear stability analysis of a two layer Oldroyd-B and
+Newtonian pressure-driven channel flow and compared it to an experiment with an
+elastic Boger fluid and a Newtonian fluid in \citep{Khomami2000a, Khomami2000b}.
+They found that they could fit their experiments with the Oldroyd-B model and
+find that their experiments saturated to 2D structures unlike the 3D structures
+seen in \citep{Khomami1997} and they suggest that it is because this was a
+second normal stress effect a la \citep{Renardy1999} which is not present in the
+current experimental setup. Their second paper, \citep{Khomami2000b} does the
+theoretical weakly nonlinear stability analysis and finds supercritical
+bifurcations as expected.
+
+For some entertainment if you have read this far, \citep{Renardy2000} is a
+review article which I think states that my PhD is pointless, "Much early work
+on stability of shear flows was motivated by the desire to explain melt
+fracture (‘viscoelastic turbulence’) as a result of an instability similar to
+the laminar/turbulent transition in Newtonian flows. This is no longer believed
+to be a realistic proposition."
+
+Brady \citep{Brady2002} claim to have a generic instability that explains
+Renardy's \citep{Renardy1999} second normal stress jump result, look at a
+variety of flows including falling film and Newtonian fluid of non-Newtonian
+flow. They use their own viscous-suspension flow constitutive model and
+examine the effects of a jump in the second normal stress.
+
+Meulenbroek \citep{Meulenbroek2004} show that there is weakly nonlinear
+subcritical instability in Poiseuille flow of Oldroyd-B fluids. But seeing as
+you are an author I expect you know that better than me.
+
+Miller  looks at the interfacial instability between sheared UCM and Oldroyd-B
+liquids in channel flow \citep{Miller2007a} and a pipe flow
+\citep{Miller2007b}. They don't like the distinction between short and long
+wave instabilities. They don't think that surface tension stabilises as claimed
+in \citep{Chen1992b}. Look at a new limit, where $L < k^{-1} < U_{0} \lambda$
+the wavelength is long compared to the channel width but short compared to the
+relaxation length scale. They use a combination of short and long wave
+techniques. They claim that their instability has a different origin to the
+Hinch one I think.
+
+Bonhomme, O, Morozov \citep{Bonhomme2011} find an elastic instability in the
+core annular flow of two different Oldroyd-B fluids and perform short wave
+linear stability asymptotics. Also some experiments, but I imagine you would
+know all about this.
+
+Wongsomnuk, \citep{Wongsomnuk2000} do a little experiment to show the sharkskin
+instability onset. I am sure there is probably a better experiment for this out
+there, but this is just the one that came up.
+
+\citet{Yoo2013} does something that may be related to our instability, but
+it is a long shot. They look at the effect of viscoelasticity on an instability
+at the interface between lamellar phases with different orientations under
+oscillatory shear.  They use a linear constitutive law which I don't recognise.
+
+\citet{Dubief2013} looks at the mechanism of elasto-inertial
+turbulence in \citet{Samanta2013}. Possibly related to our instability,
+but we have talked about this instability before and I don't think Yves has
+convinced you it exists yet?
+
+Mahdaoui \citep{Mahdaoui2013} do a numerical investigation of the co-extrusion
+instability. They use a complicated multiscale simulation technique on the
+Carreau-Yasuda multimode Johnson-Segalman model in 2D along with some possibly
+molecular dynamics techniques in areas which are hard to resolve.
+
+Beaumont \citep{Beaumont2013} do some experiments looking at turbulent flows in
+a Taylor-Couette flow of purely elastic wormlike micelles. Find inhomogeneous
+turbulence and suggest the existence of a bulk instability.
+
+Fardin \citep{Fardin2014} has a review article on the Taylor-Couette flow for
+soft matter. It references you a lot and discusses the possibility of a purely
+elastic KH instability. No doubt you are partially responsible for getting that
+line put in there!
+
+McKinley \citep{McKinley1996} gives us the geometrical $\Wi$ scaling. Zilz 2012
+\citep{Zilz2012} have nice serpentine channel purely elastic flow which
+supports the Pakdel-McKinley condition if we choose to use it.
+
+\section{Problem formulation}
 
@@
 Oldroyd-B and FENE-P constitutive models for a polymeric fluid. The purely
-elastic fluid is found to be unstable at sufficiently high numbers of the
-dimensionless parameter, the Weissenberg number. The growth rate of the largest
-growing eigenmode of the instability is found to increase with increasing
-Weissenberg number for low Reynold's number. This behaviour is consistent
-across both the Oldroyd-B and FENE-P models.
+elastic fluid is found to be unstable at sufficiently high Weissenberg number,
+the key dimensionless number for turbulence without inertia in viscoelastic
+flows. This is the ratio of the normal stress to the shear stress of the
+polymeric component of the fluid $Wi = \frac{N_{1}}{\sigma} = \lambda
+\dot{\gamma}$ where $\dot{\gamma}$ is the shear rate.  The growth rate of the
+largest growing eigenmode of the instability is found to increase with
+increasing Weissenberg number for low Reynold's number. This behaviour is
+consistent across both the Oldroyd-B and FENE-P models.
 
@@
 \begin{align} 
-    U(y) &= \tanh \left( y/\Delta \right) \coth \left( 1/\Delta \right) \nonumber\\
-    V &= 0 \nonumber \\
-    T_{xx}(y) &= 2 Wi \left( \dy{U} \right)^{2} \nonumber \\
-    T_{xy}(y) &= \dy{U} \nonumber \\
-    T_{yy}(y) &= 0 \nonumber 
-    \label{eq:KH_laminar_profile}
+    U(y) &= \tanh \left( y/\Delta
+    \right) \coth \left( 1/\Delta \right) \nonumber\\ V &= 0 \nonumber \\
+    T_{xx}(y) &= 2 Wi \left( \dy{U} \right)^{2} \nonumber \\ T_{xy}(y) &=
+    \dy{U} \nonumber \\ T_{yy}(y) &= 0 \nonumber \label{eq:KH_laminar_profile}
 \end{align}
-
 $U$ and $V$ are the base streamwise (x) and wall normal (y) velocities
@@
     z_{u} &= \frac{y_{u}}{1-y_{u}} \\
-    z_{b} &= \frac{y_{b}}{1+y_{b}} \\
-    U     &= \tanh{z/\Delta} 
+    z_{b} &= \frac{y_{b}}{1+y_{b}} \\ U     &= \tanh{z/\Delta}
     \label{eq:KH_inf_profile} 
 \end{align} 
-This system ought to be completely insensitive to the boundary conditions on
-the flow and so also behave as a free shear instability.
+This system ought to be completely insensitive to the boundary conditions at
+the walls so we refer to it as 'free shear' throughout this manuscript.
 
@@
 In order to simulate this flow, we used an Oldroyd-B fluid with very low
-Reynolds number $\Rey < 0.01$ and a small ratio between the solvent and total
+Reynolds number $\Rey \leq 0.01$ and a small ratio between the solvent and total
 viscosities $\beta = \frac{\mu_{s}}{\mu_{s}+\mu_{p}}$. This approximates a
-purely elastic fluid, where the polymer contribution to the dynamics is higher
-than the solvent contribution. The Oldroyd-B Navier stokes and constitutive
-equations are then: 
+purely elastic fluid, where the polymer contribution to the stress on the fluid
+is much larger  than the solvent contribution. The Oldroyd-B Navier stokes and
+constitutive equations are then: 
 \begin{align} 
-    Re \left[ \dt{\mathbf{v}} + \mathbf{v} \cdot \nabla  \mathbf{v} \right] &=
-    - \nabla p + \beta \nabla^{2} \mathbf{v} + \frac{1-\beta}{Wi} \nabla \cdot
-    \mathbf{\tau} \\ \dot{\tau}/Wi + \overset{\nabla}\tau &= \left(\nabla
-    \mathbf{v}\right)^{T} + \nabla{\mathbf{v}}
+    Re \left[ \dt{\mathbf{v}} +
+    \mathbf{v} \cdot \nabla  \mathbf{v} \right] &= - \nabla p + \beta
+    \nabla^{2} \mathbf{v} + \frac{1-\beta}{Wi} \nabla \cdot \mathbf{\tau} \\
+    \dot{\tau}/Wi + \overset{\nabla}\tau &= \left(\nabla \mathbf{v}\right)^{T}
+    + \nabla{\mathbf{v}} 
 \end{align} 
@@
 
-\begin{equation}
-    \mathbf{\tau} = \frac{1-\frac{3}{L^{2}}}{1 + \frac{L^{2}}{tr(\mathbf{C^{2}})}}
-\end {equation}
+\begin{equation} \mathbf{\tau} = \frac{1-\frac{3}{L^{2}}}{1 +
+	\frac{L^{2}}{tr(\mathbf{C^{2}})}} \end {equation}
 
@@
 	\label{fig:inf_low_Re} 
-    \end{subfigure}
-    ~
+    \end{subfigure} ~
     \begin{subfigure}[b]{0.48\textwidth} 
@@
     \end{subfigure} 
-    \caption{a) Free shear version of the instability. Plot of the maximum
-	     growth rate against Wiessenberg number at $\Rey = 0.01$. b)
-	     Dispersion relations at various Weissenberg numbers to accompany
-	     the trend in figure a).}
+    \caption{
+	a) Free shear version of the instability. Plot of the maximum growth
+	rate against Weissenberg number at $\Rey = 0.01$. b) Dispersion
+	relations at various Weissenberg numbers to accompany the trend in
+	figure a).
+    } 
 \end{figure}
@@
 	\label{fig:inf_vary_Re} 
-    \end{subfigure}
-    ~
+    \end{subfigure} ~
     \begin{subfigure}[b]{0.48\textwidth} 
@@
 
-\begin{figure}
-    \begin{subfigure}[b]{\textwidth}
+\begin{figure} \begin{subfigure}[b]{\textwidth} 
 	\centering
@@
 	\label{fig:psi_low_delta}
-    \end{subfigure}
-    \vspace{1 mm}
+    \end{subfigure} \vspace{1 mm}
     \begin{subfigure}[b]{\textwidth}
@@
 Dependence of the instability on the channel walls persists at very small
-$\Delta$. We believe that this is due to the inertial effects at low Reynold's
-number being so weak. This means it is very easy to move the fluid even at
-the shear rate present far from the centre of the channel. I think the
-instability generated by the elasticity of the fluid needs the walls to dampen
-it for some reason.
+$\Delta$ whilst in the purely elastic region of the flow phase space. We are
+not sure why this is. We might be able to understand this by thinking about shear
+waves in an elastic solid? (was thinking about surface Rayleigh waves)
 
@@
     \caption{
-    Dispersion relations for various values of $\Delta$ at $\Rey = 0.1$, $\Wi =
-    100$. The sensitivity to the walls seems only to increase the strength of
-    the instability. Even when the system is insensitive to the walls, at
-    $\Delta= 0.0125$, there is still an instability present.
+	Dispersion relations for various values of $\Delta$ at $\Rey = 0.1$,
+	$\Wi = 100$. The sensitivity to the walls seems only to increase the
+	strength of the instability. Even when the system is insensitive to the
+	walls, at $\Delta= 0.0125$, there is still an instability present.
     } 
@@
     \caption{ 
-    Streamfunction of the eigenfunction of the instability at $\Delta = 0.1$,
-    $\Wi = 100$, $\Rey=0.1$. The magnitude is scaled by the xx stress in the
-    centre of the channel.
+	Streamfunction of the eigenfunction of the instability at $\Delta =
+	0.1$, $\Wi = 100$, $\Rey=0.1$. The magnitude is scaled by the xx stress
+	in the centre of the channel.  
     } 
@@
 
-It is difficult to see the instability at $\Rey = 0$. As the Reynold's number
-is reduced the walls become more important to the instability. In order to
-remove the dependence on the walls and recover a free shear instability it is
-necessary to move them further away. This problem gets worse at lower $\Rey$.
-By introducing just a very small contribution from inertia, we can remove the
-dependence on the walls. This is why all of our results are taken for $\Rey
-\leq 0.1$ on the length scale of the instability.
+As the Reynold's number is reduced the walls become more important to the
+instability, this makes a true $\Rey = 0$ instability difficult for us to
+observe. In order to remove the dependence on the walls and recover a free
+shear instability it is necessary to move them further away. This problem gets
+worse at lower $\Rey$.  By introducing just a very small contribution from
+inertia, we can remove the dependence on the walls. This is why all of our
+results are taken for $\Rey \lesssim 0.1$ on the length scale of the
+instability.
 
@@
 the Newtonian problem takes place on a length scale of about 10\% of the width
-of the channel, or $\Delta = 0.1$ (a guess). The viscoelastic Kelvin-Helmholtz
+of the channel, or $\Delta = 0.1$. If this length scale is similar in the
+purely elastic case, we can make say that the viscoelastic Kelvin-Helmholtz
 instability is sensitive to the walls at this $\Delta$ and a $\Rey \lesssim 1$
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\textwidth]{vary_Re_delta_conv}
-    \caption{
-	The blue line is the data from the stretched code and the green line is
+\begin{figure} \centering
+    \includegraphics[width=0.7\textwidth]{vary_Re_delta_conv} \caption{ The
+	blue line is the data from the free shear system and the green line is
 	the $\Delta = 0.1$ data. By $\Rey = 1$ it is clear that the Reynold's
 	number is sufficient such that the walled system behaves as though it
-	were insensitive to the walls.
-    }
-    \label{fig:vary_Re_delta_conv}
+    were insensitive to the walls.  } \label{fig:vary_Re_delta_conv}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=\textwidth]{KH_purely_elastic}
+	\includegraphics[width=\textwidth]{KH_low_Re_vary_Wi} 
 	\caption{}
 	\label{fig:KH_purely_elastic} 
-\end{subfigure}
-~
+    \end{subfigure} ~
     \begin{subfigure}[b]{0.48\textwidth} 
@@
 	\label{fig:KH_elastic_onset} 
-\end{subfigure}
-~
+    \end{subfigure} ~
     \begin{subfigure}[b]{0.48\textwidth} 
@@
     \caption{ 
-a) The change in the height of the dispersion relation as $\Wi$ is increased at
-$\Rey = 0$ with $\Delta = 0.1$. This instability must be entirely elastic in
-nature. b) The change in the height of the dispersion relation as the Reynolds
-number is reduced at $\Wi=5$. At low $\Rey$ the instability is clearly still
-present for large polymer concentrations, consistent with purely elastic
-turbulence with $\Delta = 0.1$.  c) The value of the Weissenberg number at
-which the velocity profile becomes unstable against $\beta$ at $\Delta = 0.1$.
-The onset of the purely elastic instability moves to higher $Wi$ as $\beta$
-increases. d) Dispersion relations at Wi =50 for $\Delta =0.1$.
+	a) The change in the height of the dispersion relation as $\Wi$ is
+	increased at $\Rey = 0$ with $\Delta = 0.1$. The green and red lines gives
+	the behaviour at $\beta=0.1$, $\beta=0.5$ respectively. b) The change in
+	the height of the dispersion relation as the Reynolds number is reduced at
+	$\Wi=5.0$. The colours give the values of $\beta$ as above, with blue being
+	the behaviour for $\beta=0.9$. At low $\Rey$ the instability is clearly
+	still present for large polymer concentrations, consistent with purely
+	elastic turbulence with $\Delta = 0.1$.  c) The value of the Weissenberg
+	number at which the velocity profile becomes unstable against $\beta$ at
+	$\Delta = 0.1$.  The onset of the purely elastic instability moves to
+	higher $\Wi$ as $\beta$ increases. d) Dispersion relations at Wi =50 for
+	$\Delta =0.1$.  
     }
+\end{figure}
+
+\begin{figure} 
+    \centering
+    \includegraphics[width=0.7\textwidth]{growth_rate_sldim} 
+    \caption{ 
+	Phase diagram showing the growth rate for various values of the
+	Reynold's and Weissenberg numbers at $\beta=0.1$. Grey lines represent
+	lines of constant elasticity. Black squares are data points for which
+	the flow is linearly stable.  
+    } 
+    \label{fig:vary_Re_delta_conv} 
 \end{figure}
@@
     }
-    \label{fig:FENE_low_Re}
-\end{figure}
+	\label{fig:FENE_low_Re} \end{figure}
 
@@
 
-\begin{figure}
-    \centering
+\begin{figure} \centering
     \includegraphics[width=0.7\textwidth]{high_Re_vary_delta} 
     \caption{
-    Dispersion relations for various values of $\Delta$ and $\Rey = 1000$, $\Wi
-    = 0.01$. When results are rescaled for delta, The instability is found to
-    be insensitive to the width of the instability relative to the wall at this
-    combination of Reynold's number and Wiessenberg number.
+	Dispersion relations for various values of $\Delta$ and $\Rey = 1000$,
+	$\Wi = 0.01$. When results are rescaled for delta, The instability is
+	found to be insensitive to the width of the instability relative to the
+	wall at this combination of Reynold's number and Weissenberg number.  
     }
@@
 %   \showthe\columnwidth %use this to determine size of figures.
-    \centering
-    \includegraphics[width=0.7\textwidth]{KH_high_Re_vary_Wi}
+    \centering \includegraphics[width=0.7\textwidth]{KH_high_Re_vary_Wi}
     \caption{ 
-	Peak growth rate against Wiessenberg number at $\Rey = 1000$, $\Delta =
-	0.1$ The height of the dispersion relation is reduced for the
+	Peak growth rate against Weissenberg number at $\Rey = 1000$,
+	$\Delta = 0.1$ The height of the dispersion relation is reduced for the
 	Kelvin-Helmholtz instability as the Weissenberg number is increased.
@@
 \end{figure}
-
-\section{Outline of the mechanism}
 
@@
 which it is saturated. The instability is also strongly dependent on the walls
-at low effective Reynold's number.
+at low Reynold's number.
 
 \bibliographystyle{jfm}
-% Note the spaces between the initials
+%\bibliographystyle{plain}
 

### 2016-01-22 D_domain.py

@@ -9,12 +9,12 @@ import argparse
 
 M = 100
 
-Re = float(1000.0)
-Wi = float(1.2)
+Re = float(.1)
+Wi = float(6.0)
 bbeta = float(0.1)
-kxLo = 0.1
-kxHi = 10.0
-kxStep = 0.1 
+kxLo = 0.05
+kxHi = 1.2
+kxStep = 0.05 
 
 _delta = 0.1
 
@@ -28,6 +28,8 @@ argparser.add_argument("-b", type=float, default=bbeta,
                 help='Override beta of the file')
 argparser.add_argument("-Wi", type=float, default=Wi, 
                 help='Override Weissenberg number of the file')
+argparser.add_argument("-delta", type=float, default=_delta, 
+                help='Override delta number of the file')
 argparser.add_argument("-kxLo", type=float, default=kxLo, 
                 help='Override initial wavenumber of the file')
 argparser.add_argument("-kxHi", type=float, default=kxHi, 
@@ -43,6 +45,7 @@ bbeta = args.b
 kxLo = args.kxLo
 kxHi = args.kxHi
 kxStep = args.kxStep
+_delta = args.delta
 
 ##------------------------------------
 

### 2016-02-12 paper/paper.tex
updated the paper, improved discussion of the wall dependence.

@@
 %	paper.tex	Toby Searle
-%	Last modified: Fri 22 Jan 15:20:25 2016
+%	Last modified: Fri 12 Feb 11:52:33 2016
 %	using jfm template
@@
 
-\section{Problem formulation}
+\section{Problem formulation}\label{sec:KH_problem_formulation}
 
-We present a linear stability analysis of the Kelvin-Helmholtz instability in
-the purely elastic regime using direct numerical simulation of both the
-Oldroyd-B and FENE-P constitutive models for a polymeric fluid. The purely
-elastic fluid is found to be unstable at sufficiently high Weissenberg number,
-the key dimensionless number for turbulence without inertia in viscoelastic
-flows. This is the ratio of the normal stress to the shear stress of the
-polymeric component of the fluid $Wi = \frac{N_{1}}{\sigma} = \lambda
-\dot{\gamma}$ where $\dot{\gamma}$ is the shear rate.  The growth rate of the
-largest growing eigenmode of the instability is found to increase with
-increasing Weissenberg number for low Reynold's number. This behaviour is
-consistent across both the Oldroyd-B and FENE-P models.
+We propose that in fact, besides the shear banding instability and the
+coextrusion instabilities, there is another mechanism by which a purely elastic
+fluid may become unstable. Using a linear stability analysis we examine a new
+Kelvin-Helmholtz like instability in both Oldroyd-B and FENE fluids. A purely
+elastic fluid is found to be unstable at sufficiently high Weissenberg number.
+The growth rate of the largest growing eigenmode of the instability increases
+with increasing Weissenberg number at low Reynolds numbers and this behaviour
+is consistent across both Oldroyd-B and FENE constituitive models.
 
-The system we use for our analysis uses a hyperbolic tangent shaped laminar
-profile for the streamwise velocity across a channel, where the instability
-takes place between $y = \pm \Delta$. $y=0$ is the centreline of the channel,
-so that if $\Delta << 1$ the flow can be said to be a free shear instability.
-This gives a base flow profile, 
+The flow we consider is a hyperbolic tangent shaped laminar profile for the
+streamwise velocity across a channel, where $y = \pm \Delta$ is the region of
+shear. $y=0$ is the centreline of the channel, so that if $\Delta << 1$ the
+flow can be said to be a free shear instability.  This gives a base flow
+profile, 
 \begin{align} 
@@
     T_{xx}(y) &= 2 Wi \left( \dy{U} \right)^{2} \nonumber \\ T_{xy}(y) &=
-    \dy{U} \nonumber \\ T_{yy}(y) &= 0 \nonumber \label{eq:KH_laminar_profile}
+    \dy{U} \nonumber \\ T_{yy}(y) &= 0 \label{eq:KH_laminar_profile}
 \end{align}
@@
 pseudo-spectral points to give increased resolution in the centre of the
-simulation. The simulation was also repeated using a code for which the system
-of points was stretched using: 
+channel. The analysis was repeated using a code for which the system of points
+was stretched using: 
 \begin{align} 
@@
 The dimensionless quantities used throughout are non-dimensionalised relative
-to the instability size, $\Delta$, rather than the total simulation size. The
-obvious reason for this is that $\Delta$ is the length scale for the free shear
-instability.
+to the instability size, $\Delta$, rather than the half channel width. This is
+because $\Delta$ is the length scale for the free shear instability.
 
-In order to simulate this flow, we used an Oldroyd-B fluid with very low
-Reynolds number $\Rey \leq 0.01$ and a small ratio between the solvent and total
-viscosities $\beta = \frac{\mu_{s}}{\mu_{s}+\mu_{p}}$. This approximates a
-purely elastic fluid, where the polymer contribution to the stress on the fluid
-is much larger  than the solvent contribution. The Oldroyd-B Navier stokes and
-constitutive equations are then: 
+We used an Oldroyd-B fluid with very low Reynolds number $\Rey \leq 1.0$ and a
+small ratio between the solvent and total viscosities $\beta =
+\frac{\mu_{s}}{\mu_{s}+\mu_{p}}$. This approximates a purely elastic fluid,
+where the polymer contribution to the stress on the fluid is much larger  than
+the solvent contribution. The Oldroyd-B Navier stokes and constitutive
+equations are then: 
 \begin{align} 
@@
 as the total stress in the polymeric fluid. The FENE-P viscoelastic fluid has
-the advantage of being similarly easy to simulate, but also including a finite
-extensibility for the polymers. This leads to a stress which depends on a
-conformation tensor ($\mathbf{C}$) for the polymer dumbbells via a non-linear
-spring force:
+the advantage of being similarly easy to analyse using our spectral method, but
+also including a finite extensibility for the polymers. This leads to a stress
+which depends on a conformation tensor ($\mathbf{C}$) for the polymer dumbbells
+via a non-linear spring force:
 
-\begin{equation} \mathbf{\tau} = \frac{1-\frac{3}{L^{2}}}{1 +
-	\frac{L^{2}}{tr(\mathbf{C^{2}})}} \end {equation}
+\begin{equation} 
+    \mathbf{\tau} = \frac{1-\frac{3}{L^{2}}}{1 +
+	\frac{L^{2}}{tr(\mathbf{C^{2}})}} \label{eq:KH_FENE_stress}
+\end {equation}
 
@@
     \centering 
-    \includegraphics[width=0.3\textwidth]{KH_diagram}
+    \includegraphics[width=0.3\textwidth]{{KH_diagram}}
     \caption{diagram of the system} 
-    \label{fig:diagram} 
+    \label{fig:KH_diagram} 
 \end{figure}
@@
 
-\section{A purely elastic instability}
+\FloatBarrier
+
+\section{Purely elastic linear stability analysis}\label{sec:KH_linear_stability_analysis}
 
 At low Reynolds number, low $\beta$ and sufficiently large Weissenberg number
-we observe an instability across a range of streamwise disturbance wavenumbers.
-This leads us to suppose that this instability might be a plausible cause for a
-self-sustaining process in viscoelastic plane Couette flow, similar to that
-observed by Waleffe.
-
-The instability remains unchanged under variation of $\Delta$ at low $\Delta$,
-proving that it is a free shear instability. Although the instability appears
-to require some inertia in the fluid, it is still present for  $\Rey = 0.01$,
-far lower than the usual threshold of $\Rey = 1000$ for a Newtonian
-Kelvin-Helmholtz instability.
+we observe a free shear instability across a range of streamwise disturbance
+wavenumbers. This leads us to suppose that this instability might be a
+plausible cause for a self-sustaining process in viscoelastic plane Couette
+flow, similar to that observed by Waleffe for Newtonian flows.
 
 We see an instability grow from around $k \sim 0.06$ and move to lower $k$ as
-the Weissenberg number increases (figure \ref{fig:dispersions_low_Re}). The
+the Weissenberg number increases (figure \ref{fig:KH_inf_dispersions_vary_Wi}). The
 height of the instability also increases with increasing Weissenberg number
-(figure \ref{fig:inf_low_Re}).
+(figure \ref{fig:KH_inf_disp_height_vary_Wi}).
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{inf_purely_elastic} 
+	\includegraphics[width=\textwidth]{{inf_purely_elastic}}
 	\caption{}
-	\label{fig:inf_low_Re} 
+	\label{fig:KH_inf_disp_height_vary_Wi} 
     \end{subfigure} ~
@@
 	\centering
-	\includegraphics[width=\textwidth]{inf_dispersions_low_Re} 
+	\includegraphics[width=\textwidth]{{inf_dispersions_low_Re}} 
 	\caption{}
-	\label{fig:dispersions_low_Re} 
+	\label{fig:KH_inf_dispersions_vary_Wi} 
     \end{subfigure} 
@@
 	\centering
-	\includegraphics[width=\textwidth]{inf_vary_Re} 
+	\includegraphics[width=\textwidth]{{inf_vary_Re}} 
 	\caption{}
-	\label{fig:inf_vary_Re} 
+	\label{fig:KH_inf_disp_height_vary_Re} 
     \end{subfigure} ~
@@
 	\centering
-	\includegraphics[width=\textwidth]{inf_dispersions_low_Wi} 
+	\includegraphics[width=\textwidth]{{inf_dispersions_low_Wi}}
 	\caption{}
-	\label{fig:dispersions_low_Wi} 
+	\label{fig:KH_dispersions_vary_Re} 
     \end{subfigure} 
@@
 the dominant eigenvalue changes the flow is still unstable, even down to $\Rey
-= 0.01$ (see figures \ref{fig:inf_vary_Re} and \ref{fig:dispersions_low_Wi}).
+= 0.01$ (see figures \ref{fig:KH_inf_disp_height_vary_Re} and \ref{fig:KH_dispersions_vary_Re}).
 
-\subsection{ Shear instability with walls}
+\subsection{Shear instability with walls}
+
+Now we use equations \ref{eq:KH_laminar_profile} and examine the unstretched
+pseudospectral domain.  The instability remains present under variation of
+$\Delta$ at low $\Delta$. At $\Delta =0.1$ the instability is still present for
+$\Rey < 0.01$ far lower than the usual threshold of $\Rey \sim 1000$ for a
+Newtonian Kelvin-Helmholtz instability (figure \ref{fig:KH_walls_vary_Re}).
+
+At high Reynolds number the instability is insensitive to the distance to the
+walls when $\Delta =0.1$ (figure \ref{fig:KH_high_Re_walls_dependence}). At low
+Reynolds number, the width of the channel is more important but the instability
+is still present for very low $\Delta$ (figure
+\ref{fig:KH_low_Re_walls_dependence}).
+
+\begin{figure} 
+    \centering 
+    \includegraphics[width=\textwidth]{{KH_vary_delta}}
+    \caption{
+	Dispersion relations for various values of $\Delta$ at $\Rey = 0.1$,
+	$\Wi = 100$. The sensitivity to the walls seems only to increase the
+	strength of the instability. Even when the system is insensitive to the
+	walls, at $\Delta= 0.0125$, there is still an instability present.
+    } 
+    \label{fig:KH_low_Re_walls_dependence} 
+\end{figure}
+
+\begin{figure} \centering
+    \includegraphics[width=0.7\textwidth]{{high_Re_vary_delta}}
+    \caption{
+	Dispersion relations for various values of $\Delta$ and $\Rey = 1000$,
+	$\Wi = 0.01$. When results are rescaled, the instability is
+	found to be insensitive for $\Delta =0.1$.
+    }
+    \label{fig:KH_high_Re_walls_dependence}
+\end{figure}
 
 If we examine the eigenvectors of the instability, we see that there are very
-large polymer stresses in the $\pm \Delta$ region. This corresponds to the
-large shear rate brought about as the two flows pass each other. Examining the
-flow field, we see that there are large vortices arranged with opposite
-rotational directions above and below the shear region which extend almost to
-the walls.
+large polymer stresses in the $\pm \Delta$ region (figure
+\ref{fig:KH_stress_low_delta}). This corresponds to the large shear rate
+brought about as the two flows pass each other. Examining the flow field, we
+see that there are large vortices arranged with opposite rotational directions
+above and below the shear region which extend almost to the walls. This is a
+very different situation from that observed for the Newtonian Kelvin-Helmholtz
+instability, where there is an exponential decay in the velocity outside the
+region of shear (figure \ref{fig:KH_Visco_Newt_evectors}). The larger
+penetration depth out of the shear layer by the viscoelastic eigenvector is
+likely linked to the stronger dependence on $\Delta$ relative to the Newtonian
+instability.
+
+\begin{figure}[h]
+    \includegraphics[width=\textwidth]{{Visco_Newt_slice}.pdf}
+    \caption{
+	Streamfunction of the Newtonian Kelvin Helmholtz instability at $\Rey =
+	1000$ compared with the purely elastic instability for $\beta = 0.1$,
+	$\Rey = 0.0$, $\Wi = 5.0$, both at $\Delta =0.05$. The Newtonian Kelvin
+	Helmholtz instability exponentially decays towards the channel walls
+	whilst large vortices are present outside the walls in the purely
+	elastic case.
+    }
+    \label{fig:KH_Visco_Newt_evectors}
+\end{figure}
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{psi_low_delta}
+	\includegraphics[width=\textwidth]{{psi_low_delta}}
 	\caption{}
-	\label{fig:psi_low_delta}
+	\label{fig:KH_psi_low_delta}
     \end{subfigure} \vspace{1 mm}
@@
 	\centering
-	\includegraphics[width=\textwidth]{txx_low_delta} 
+	\includegraphics[width=\textwidth]{{txx_low_delta}} 
 	\caption{}
-	\label{fig:stress_low_delta} 
+	\label{fig:KH_stress_low_delta} 
     \end{subfigure} 
@@
 
-Dependence of the instability on the channel walls persists at very small
-$\Delta$ whilst in the purely elastic region of the flow phase space. We are
-not sure why this is. We might be able to understand this by thinking about shear
-waves in an elastic solid? (was thinking about surface Rayleigh waves)
+As $\Delta$ decreases for a particular purely elastic instability, the size of
+the velocities expands slightly but in the limit of very small $\Delta$ the
+eigenvector appears independent of the walls (figures
+\ref{fig:KH_psi_low_delta} and \ref{fig:KH_psi_high_delta}). The large width
+vortices in our purely elastic case, seem to correspond to the larger
+elasticity ($G~\Wi/\Rey$) eigenvectors in \citet{Azaiez1994}. Their $G=5$ case
+would only correspond to $\Wi=0.5$ for $\Re=0.1$ in our purely elastic
+instability, so it is a completely different, inertial instability that they
+observe (\citet{Azaiez1994} figure 8). Nonetheless at least one of their observations does apply. The fact
+that the velocity disturbance is essentially zero in the center of the channel,
+implies that the shear layer will be less likely to roll up. In the Newtonian
+instability, net velocities within the shear layer will distort its shape,
+however the purely elastic instability appears to have less of an effect on the
+shear layer.
 
@@
     \centering 
-    \includegraphics[width=\textwidth]{KH_vary_delta}
-    \caption{
-	Dispersion relations for various values of $\Delta$ at $\Rey = 0.1$,
-	$\Wi = 100$. The sensitivity to the walls seems only to increase the
-	strength of the instability. Even when the system is insensitive to the
-	walls, at $\Delta= 0.0125$, there is still an instability present.
-    } 
-    \label{fig:walls_dependence} 
-\end{figure}
-
-\begin{figure} 
-    \centering 
-    \includegraphics[width=\textwidth]{psi_high_delta}
+    \includegraphics[width=\textwidth]{{psi_high_delta}}
     \caption{ 
@@
     } 
-    \label{fig:psi_high_delta}
+    \label{fig:KH_psi_high_delta}
 \end{figure}
@@
 
-The reason we have have the simulation with the walls at all is because of the
-implications for the plane Couette problem. The Kelvin-Helmholtz instability in
-the Newtonian problem takes place on a length scale of about 10\% of the width
-of the channel, or $\Delta = 0.1$. If this length scale is similar in the
-purely elastic case, we can make say that the viscoelastic Kelvin-Helmholtz
-instability is sensitive to the walls at this $\Delta$ and a $\Rey \lesssim 1$
-(see figure \ref{fig:vary_Re_delta_conv}). This means that on the scale of the
-channel, $\Rey \gtrsim 10$ for the walls not to affect the instability. So, the
-important results for the purely elastic instability from the point of view of
-the plane Couette problem are probably those for which the walls are relevant.
+The analysis for the system in the channel has implications for the plane
+Couette problem. The Kelvin-Helmholtz instability in the Newtonian problem
+takes place on a length scale of about 10\% of the width of the channel, or
+$\Delta = 0.1$. If this length scale is similar in the purely elastic case, we
+can say that the viscoelastic Kelvin-Helmholtz instability is sensitive to the
+walls at this $\Delta$ and a $\Rey \lesssim 1$ (see figure
+\ref{fig:KH_disp_height_vary_Re_delta_conv}). This means that on the scale of
+the channel, $\Rey \gtrsim 10$ for the walls not to affect the instability. So,
+the important results for the purely elastic instability from the point of view
+of the plane Couette problem are probably those for which the walls are
+relevant.
 
 \begin{figure} \centering
-    \includegraphics[width=0.7\textwidth]{vary_Re_delta_conv} \caption{ The
-	blue line is the data from the free shear system and the green line is
+    \includegraphics[width=0.7\textwidth]{{vary_Re_delta_conv}}
+    \caption{ The
+	data in red corresponds to the free shear system and the green gives
 	the $\Delta = 0.1$ data. By $\Rey = 1$ it is clear that the Reynold's
 	number is sufficient such that the walled system behaves as though it
-    were insensitive to the walls.  } \label{fig:vary_Re_delta_conv}
+    were insensitive to the walls.  } \label{fig:KH_disp_height_vary_Re_delta_conv}
 \end{figure}
-
-At $\Delta = 0.1$ we see the same instability as that seen in the completely
-free case.
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{KH_low_Re_vary_Wi} 
+	\includegraphics[width=\textwidth]{{KH_low_Re_vary_Wi}}
 	\caption{}
@@
 	\centering
-	\includegraphics[width=\textwidth]{KH_low_Wi_vary_Re} 
+	\includegraphics[width=\textwidth]{{KH_low_Wi_vary_Re}}
 	\caption{}
-	\label{fig:KH_reduce_Re} 
+	\label{fig:KH_walls_vary_Re} 
     \end{subfigure}
@@
 	\centering
-	\includegraphics[width=\textwidth]{KH_onset_beta_Wi} 
+	\includegraphics[width=\textwidth]{{KH_onset_beta_Wi}}
 	\caption{}
@@
 	\centering
-	\includegraphics[width=\textwidth]{fin_dispersions_Wi50} 
+	\includegraphics[width=\textwidth]{{fin_dispersions_Wi50}}
 	\caption{}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{growth_rate_sldim} 
+    \includegraphics[width=0.7\textwidth]{{growth_rate_sldim}} 
     \caption{ 
@@
     } 
-    \label{fig:vary_Re_delta_conv} 
+    \label{fig:KH_growth_rate_phase_diagram} 
 \end{figure}
 
-\section{Confirming the model}
+\FloatBarrier
 
@@
 The finite extensibility version of the model gives good agreement with the
-Oldroyd-B version. Shorter lengths bring about a larger instability but do not
+Oldroyd-B version. Shorter lengths bring about a stronger instability and do not
 delay it to higher Weissenberg number. Otherwise similar dispersion relations
 are observed with a similar dependence on the distance to the walls (figure
-\ref{fig:FENE_low_Re}).
+\ref{fig:KH_FENE_low_Re}).
 
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{FENE_purely_elastic} 
+    \includegraphics[width=0.7\textwidth]{{FENE_purely_elastic}} 
     \caption{ 
-	The FENE-P model fluid at $\Rey = 0$  when $\Delta = 0.1$. Results are
-	consistent with figure \ref{fig:KH_purely_elastic}.  
+	The FENE-P model fluid at $\Rey = 0$  when $\Delta = 0.1$, ranging from
+	$L=100$ (top curve), $L=500$ and the Oldroyd-B model in the bottom
+	curve. Results are consistent with figure \ref{fig:KH_purely_elastic}.  
     }
-	\label{fig:FENE_low_Re} \end{figure}
+	\label{fig:KH_FENE_low_Re} \end{figure}
 
-\subsection{Varying width of the instability}
-
-\begin{figure} \centering
-    \includegraphics[width=0.7\textwidth]{high_Re_vary_delta} 
-    \caption{
-	Dispersion relations for various values of $\Delta$ and $\Rey = 1000$,
-	$\Wi = 0.01$. When results are rescaled for delta, The instability is
-	found to be insensitive to the width of the instability relative to the
-	wall at this combination of Reynold's number and Weissenberg number.  
-    }
-    \label{fig:delta_dispersion}
-\end{figure}
-
-\subsection{Drag reduction}
-
-We see drag reduction using the Oldroyd-B model. It is not clear whether or not
-the maximum drag reduction asymptote is present (figure
-\ref{fig:KH_drag_reduction}).
+We see the height of the instability decrease with increasing Weissenburg number, and this trend is stronger for smaller $\beta$ (figure \ref{fig:KH_drag_reduction}).
 
@@
 %   \showthe\columnwidth %use this to determine size of figures.
-    \centering \includegraphics[width=0.7\textwidth]{KH_high_Re_vary_Wi}
+    \centering \includegraphics[width=0.7\textwidth]{{KH_high_Re_vary_Wi}}
     \caption{ 
@@
 	Newtonian fluid. The decrease in $\lambda_{r}$ corresponds to increased
-	stability of the base flow and so confirms the presence of drag
-	reduction in this system.  
-    } 
+	stability of the base flow, this matches the observations made in \cite{Azaiez1994}} 
     \label{fig:KH_drag_reduction} 
 \end{figure}
+
+\FloatBarrier
 

### 2016-02-12 paper/paper.tex
updated paper with more new plots, improved ordering of some plots

@@
 %	paper.tex	Toby Searle
-%	Last modified: Fri 12 Feb 11:52:33 2016
+%	Last modified: Fri 12 Feb 17:42:28 2016
 %	using jfm template
@@
 \affiliation{$^1$SUPA, School of Physics and Astronomy, University of Edinburgh, Mayfield Road,
-Edinburgh, EH9 3JZ, UK\\[\affilskip]
+Edinburgh, EH9 3JZ, UK\\
+[\affilskip]
 }
@@
 
-It was long thought that the elasticity of a viscoelastic fluid only served to
-dampen instability. This view stems from early results showing that drag in a
-turbulent Newtonian flow can be reduced by the addition of small amounts of
-viscoelastic fluid \citep{Toms1977}. Although drag reduction has been studied
-for a long time, studies on turbulence without inertia \citep{Larson1990,
-Groisman2000} give reason to believe that there are purely elastic bulk
-instabilities present in elastic fluids relevant to industry.  This purely
-elastic turbulence is present at very low Reynolds number, where it is driven
-by the elasticity of a polymeric flow rather than its inertia.
+The Kelvin-Helmholtz instability is integral to the transition to turbulence in
+Newtonian fluids. By finding a purely elastic version of this instability, we
+seek to probe a generic mechanism for the transition to purely elastic
+turbulence, one that is presumably present in other contexts, such as the
+oscillatory channel flow problem of \cite{Searle2016b}. To explore this
+mechanism in the purely elastic regime we have constructed a simple model
+system of a purely elastic flow which generates large jumps in the first normal
+stress difference and so ought to lead to instability.
+
+This flow has not been considered in the past because it does not occur in many
+of the natural contexts where we see the Newtonian Kelvin-Helmholtz. For
+example, the archetypical Kelvin-Helmholtz instability takes place for flow
+over a backwards facing step. In this geometry, the fluids inertia leads to an
+overshoot with vortex behind the step and a hyperbolic tangent streamwise flow
+velocity. In Purely elastic fluids the flow is Stokesian, and so the fluid
+velocity is much smoother with no overshoot.
+
+The backwards facing step is not the flow we are thinking of when we examine
+this instability, however. We are thinking of flows where elastic effects lead
+to sharp changes in velocity and stress. Such jumps in first normal stress
+difference are thought to lead to an instability see \citet{Morozov2007}, and
+we hope to expose this as a generic mechanism by which a flow might become
+unstable.
 
@@
 \citet{Azaiez1994} do the linear stability of a free shear flow of the
-Oldroyd-B, co-rotational Jefferys and Gisekus fluids. Find suppression of the
-Newtonian Kelvin-Helmholtz instability. They do asymptotic long wave linear
-stability such that the Reynold's number is small but finite and the
-Weissenberg number is large with a constant elasticity. They also do a
-numerical linear stability via an orthogonal shooting algorithm. In the
-appendix of this paper Hinch \citep{Azaiez1994} takes the long wavelength limit
-of their problem in a far more elegant way and exposes a stabilisation
+Oldroyd-B, co-rotational Jefferys and Gisekus fluids. For large elasticity they
+find suppression of the Newtonian Kelvin-Helmholtz instability. They do
+asymptotic long wave linear stability such that the Reynold's number is small
+but finite and the Weissenberg number is large with a constant elasticity. They
+also do a numerical linear stability via an orthogonal shooting algorithm. In
+the appendix of this paper Hinch \citep{Azaiez1994} takes the long wavelength
+limit of their problem in a far more elegant way and exposes a stabilisation
 mechanism based on elastic hoop stresses in the curved streamlines.
@@
 With $\mathbf{v}$ as the total (base flow and disturbance) velocity and $\tau$
-as the total stress in the polymeric fluid. The FENE-P viscoelastic fluid has
+as the total stress in the polymeric fluid. The FENE-CR viscoelastic fluid has
 the advantage of being similarly easy to analyse using our spectral method, but
@@
 
-\begin{figure} 
+\begin{figure}[h]
     \centering 
     \includegraphics[width=0.3\textwidth]{{KH_diagram}}
-    \caption{diagram of the system} 
+    \caption{Diagram of a shear layer} 
     \label{fig:KH_diagram} 
@@
 	\label{fig:KH_inf_disp_height_vary_Wi} 
-    \end{subfigure} ~
+    \end{subfigure} 
+    ~
     \begin{subfigure}[b]{0.48\textwidth} 
 	\centering
-	\includegraphics[width=\textwidth]{{inf_dispersions_low_Re}} 
+	\includegraphics[width=\textwidth]{{inf_dispersions_Re0.01}.pdf} 
 	\caption{}
@@
 	\label{fig:KH_inf_disp_height_vary_Re} 
-    \end{subfigure} ~
+    \end{subfigure} 
+    ~
     \begin{subfigure}[b]{0.48\textwidth} 
@@
 
+\FloatBarrier
+
 \subsection{Shear instability with walls}
@@
 Now we use equations \ref{eq:KH_laminar_profile} and examine the unstretched
-pseudospectral domain.  The instability remains present under variation of
-$\Delta$ at low $\Delta$. At $\Delta =0.1$ the instability is still present for
-$\Rey < 0.01$ far lower than the usual threshold of $\Rey \sim 1000$ for a
-Newtonian Kelvin-Helmholtz instability (figure \ref{fig:KH_walls_vary_Re}).
+pseudospectral domain. To validate the code, we examine the high Reynolds
+number regime. We see the height of the instability decrease with increasing
+Weissenburg number, and this trend is stronger for smaller $\beta$ (figure
+\ref{fig:KH_drag_reduction}). This is the same behaviour reported in
+\cite{Azaiez1994}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{{high_Re_vary_delta}}
+    \caption{
+	Dispersion relations for various values of $\Delta$ and $\Rey = 1000$,
+	$\Wi = 0.01$. When results are rescaled, the instability is
+	found to be insensitive for $\Delta =0.1$.
+    }
+    \label{fig:KH_high_Re_walls_dependence}
+\end{figure}
+
+\begin{figure}[h]
+%   \showthe\columnwidth %use this to determine size of figures.
+    \centering \includegraphics[width=0.7\textwidth]{{KH_high_Re_vary_Wi}}
+    \caption{ 
+	Peak growth rate against Weissenberg number at $\Rey = 1000$,
+	$\Delta = 0.1$ The height of the dispersion relation is reduced for the
+	Kelvin-Helmholtz instability as the Weissenberg number is increased.
+	The grey dashed line is the height of the dispersion relation for the
+	Newtonian fluid. The decrease in $\lambda_{r}$ corresponds to increased
+	stability of the base flow, this matches the observations made in \cite{Azaiez1994}} 
+    \label{fig:KH_drag_reduction} 
+\end{figure}
+
+The instability remains present under variation of $\Delta$ at low $\Delta$. At
+$\Delta =0.1$ the instability is still present for $\Rey < 0.01$ far lower than
+the usual threshold of $\Rey \sim 1000$ for a Newtonian Kelvin-Helmholtz
+instability (figure \ref{fig:KH_walls_vary_Re}).
 
@@
 
-\begin{figure} 
+\begin{figure}[h]
     \centering 
@@
     \label{fig:KH_low_Re_walls_dependence} 
-\end{figure}
-
-\begin{figure} \centering
-    \includegraphics[width=0.7\textwidth]{{high_Re_vary_delta}}
-    \caption{
-	Dispersion relations for various values of $\Delta$ and $\Rey = 1000$,
-	$\Wi = 0.01$. When results are rescaled, the instability is
-	found to be insensitive for $\Delta =0.1$.
-    }
-    \label{fig:KH_high_Re_walls_dependence}
 \end{figure}
@@
 \begin{figure}[h]
-    \includegraphics[width=\textwidth]{{Visco_Newt_slice}.pdf}
+    \includegraphics[width=\textwidth]{{visco_Newt_slice}.pdf}
     \caption{
 	Streamfunction of the Newtonian Kelvin Helmholtz instability at $\Rey =
-	1000$ compared with the purely elastic instability for $\beta = 0.1$,
-	$\Rey = 0.0$, $\Wi = 5.0$, both at $\Delta =0.05$. The Newtonian Kelvin
-	Helmholtz instability exponentially decays towards the channel walls
-	whilst large vortices are present outside the walls in the purely
-	elastic case.
+	100$, $k=0.722$ compared with the purely elastic Oldroyd-B and FENE-CR
+	instability for $\beta = 0.1$, $\Rey = 0.0$, $k=0.02$, $\Wi = 50.0$,
+	both at $\Delta =0.05$. Newtonian eigenvector is in red, with the
+	Oldroyd-B in green and the FENE model in dashed purple at $L=100$. The
+	Newtonian Kelvin Helmholtz instability exponentially decays towards the
+	channel walls whilst large vortices are present outside the shear layer
+	in the purely elastic case.
     }
@@
 
-\begin{figure} \begin{subfigure}[b]{\textwidth} 
+\begin{figure}
+    \begin{subfigure}[b]{\textwidth} 
 	\centering
@@
 instability, so it is a completely different, inertial instability that they
-observe (\citet{Azaiez1994} figure 8). Nonetheless at least one of their observations does apply. The fact
-that the velocity disturbance is essentially zero in the center of the channel,
-implies that the shear layer will be less likely to roll up. In the Newtonian
-instability, net velocities within the shear layer will distort its shape,
-however the purely elastic instability appears to have less of an effect on the
-shear layer.
+observe (\citet{Azaiez1994} figure 8). Nonetheless at least one of their
+observations does apply. The fact that the velocity disturbance is essentially
+zero in the center of the channel, implies that the shear layer will be less
+likely to roll up. In the Newtonian instability, net velocities within the
+shear layer will distort its shape, however the purely elastic instability
+appears to have less of an effect on the shear layer.
 
-\begin{figure} 
+\begin{figure}[h]
     \centering 
@@
 
-\begin{figure} \centering
+\begin{figure}[h] 
+    \centering
     \includegraphics[width=0.7\textwidth]{{vary_Re_delta_conv}}
@@
 
-\begin{figure} 
+\begin{figure}[h] 
     \centering
@@
 The finite extensibility version of the model gives good agreement with the
-Oldroyd-B version. Shorter lengths bring about a stronger instability and do not
-delay it to higher Weissenberg number. Otherwise similar dispersion relations
-are observed with a similar dependence on the distance to the walls (figure
-\ref{fig:KH_FENE_low_Re}).
+Oldroyd-B version. Shorter lengths bring about a stronger instability and do
+not delay it to higher Weissenberg number. Otherwise similar dispersion
+relations are observed with a similar dependence on $\Delta$. (figure
+\ref{fig:KH_FENE_low_Re}). The dependence of the instability on wavenumber is
+not shown, but is exactly the same as that seen for the Oldroyd-B model.
 
-\begin{figure} 
+A shorter length scale for the polymers results in an amplification of the
+instability. This suggests that perhaps the instability mechanism involves the
+shear stress on the polymers.
+
+\begin{figure}[h] 
     \centering
@@
     \caption{ 
-	The FENE-P model fluid at $\Rey = 0$  when $\Delta = 0.1$, ranging from
+	The FENE-CR model fluid at $\Rey = 0$  when $\Delta = 0.1$, ranging from
 	$L=100$ (top curve), $L=500$ and the Oldroyd-B model in the bottom
@@
     }
-	\label{fig:KH_FENE_low_Re} \end{figure}
-
-We see the height of the instability decrease with increasing Weissenburg number, and this trend is stronger for smaller $\beta$ (figure \ref{fig:KH_drag_reduction}).
-
-\begin{figure}
-%   \showthe\columnwidth %use this to determine size of figures.
-    \centering \includegraphics[width=0.7\textwidth]{{KH_high_Re_vary_Wi}}
-    \caption{ 
-	Peak growth rate against Weissenberg number at $\Rey = 1000$,
-	$\Delta = 0.1$ The height of the dispersion relation is reduced for the
-	Kelvin-Helmholtz instability as the Weissenberg number is increased.
-	The grey dashed line is the height of the dispersion relation for the
-	Newtonian fluid. The decrease in $\lambda_{r}$ corresponds to increased
-	stability of the base flow, this matches the observations made in \cite{Azaiez1994}} 
-    \label{fig:KH_drag_reduction} 
+    \label{fig:KH_FENE_low_Re} 
 \end{figure}

### 2016-02-15 paper/paper.tex
improved problem formulation and fleshed out the results section of the paper

@@
 %	paper.tex	Toby Searle
-%	Last modified: Fri 12 Feb 17:42:28 2016
+%	Last modified: Mon 15 Feb 2016 18:18:32 GMT
 %	using jfm template
@@
 
-We propose that in fact, besides the shear banding instability and the
-coextrusion instabilities, there is another mechanism by which a purely elastic
-fluid may become unstable. Using a linear stability analysis we examine a new
+We propose that in fact, besides the shear banding and coextrusion
+instabilities, there is another mechanism by which a purely elastic fluid may
+become unstable. Using a linear stability analysis we examine a new
 Kelvin-Helmholtz like instability in both Oldroyd-B and FENE fluids. A purely
-elastic fluid is found to be unstable at sufficiently high Weissenberg number.
-The growth rate of the largest growing eigenmode of the instability increases
-with increasing Weissenberg number at low Reynolds numbers and this behaviour
-is consistent across both Oldroyd-B and FENE constituitive models.
+elastic fluid is found to be unstable at sufficiently high Weissenberg number
+and this behaviour is consistent across both Oldroyd-B and FENE constituitive
+models.
+
+There are a number of ways we might formulate a shear layer problem. We are
+interested in a generic instability for flows with a sharp change in the
+streamwise velocity, and so large normal stresses in the fluid. Precisely
+because we are searching for a generic mechanism, we will not attempt to
+justify our particular choice of a hyperbolic Cosine shear layer.  As well
+examining the dependence on flow properties ($\beta$, $\Wi$ and $\Rey$) of the
+instability, we are also interested in the influence of boundaries so that we
+might assess the relevence of the instability to common experimental and
+real-life examples of flows of viscoelastic fluids - including both the plane
+Couette and Oscillatory flow problems of \citet{Searle2016b} and
+\citeyear{Searle2016a}. As such we consider a nearly free shear layer (with a
+finite, but large, region of constant velocity between the shear layer and the
+walls) as well as a free shear layer.
+
+\begin{figure}[h]
+    \centering 
+    \includegraphics[width=0.3\textwidth]{{KH_diagram}}
+    \caption{Diagram of a shear layer in a channel.} 
+    \label{fig:KH_diagram} 
+\end{figure}
 
@@
 shear. $y=0$ is the centreline of the channel, so that if $\Delta << 1$ the
-flow can be said to be a free shear instability.  This gives a base flow
-profile, 
+flow tends to a free shear instability. This gives a base flow profile, 
 \begin{align} 
@@
 pseudo-spectral points to give increased resolution in the centre of the
-channel. The analysis was repeated using a code for which the system of points
-was stretched using: 
+channel. The analysis was repeated in the limit of no boundaries on the flow by
+performing a passive transform of the coordinate systems such that, 
 \begin{align} 
-    z_{u} &= \frac{y_{u}}{1-y_{u}} \\
-    z_{b} &= \frac{y_{b}}{1+y_{b}} \\ U     &= \tanh{z/\Delta}
+    z &= \frac{y}{1-y},\hphantom{aaa} z>0 \\
+    z &= \frac{y}{1+y},\hphantom{aaa} z<0 \\ 
+    U &= \tanh{z}
     \label{eq:KH_inf_profile} 
 \end{align} 
-This system ought to be completely insensitive to the boundary conditions at
-the walls so we refer to it as 'free shear' throughout this manuscript.
+This system ought to be completely insensitive to the boundary
+conditions at the walls so we refer to it as `free shear' throughout this
+manuscript.
 
 The dimensionless quantities used throughout are non-dimensionalised relative
-to the instability size, $\Delta$, rather than the half channel width. This is
-because $\Delta$ is the length scale for the free shear instability.
+to the instability size, $\Delta$, rather than the half channel width. This
+allows us to effectively examine the dependence of the instability on $\Delta$
+as we approach the free shear limit of $\Delta = 0$.
 
-We used an Oldroyd-B fluid with very low Reynolds number $\Rey \leq 1.0$ and a
-small ratio between the solvent and total viscosities $\beta =
-\frac{\mu_{s}}{\mu_{s}+\mu_{p}}$. This approximates a purely elastic fluid,
+We used an Oldroyd-B fluid at low Reynolds number (typically $\Rey < 10.0$)
+and a small ratio between the solvent and total viscosities $\beta =
+\frac{\mu_{s}}{\mu_{s}+\mu_{p}}$. This approximates a purely elastic flow,
 where the polymer contribution to the stress on the fluid is much larger  than
@@
 via a non-linear spring force:
-
 \begin{equation} 
     \mathbf{\tau} = \frac{1-\frac{3}{L^{2}}}{1 +
-	\frac{L^{2}}{tr(\mathbf{C^{2}})}} \label{eq:KH_FENE_stress}
+	\frac{L^{2}}{tr(\mathbf{C^{2}})}} \mathbf{C} \label{eq:KH_FENE_stress}
 \end {equation}
-
-\begin{figure}[h]
-    \centering 
-    \includegraphics[width=0.3\textwidth]{{KH_diagram}}
-    \caption{Diagram of a shear layer} 
-    \label{fig:KH_diagram} 
-\end{figure}
-
 Again, we used Gauss-Labatto points in the wall normal direction and Fourier
@@
 At low Reynolds number, low $\beta$ and sufficiently large Weissenberg number
-we observe a free shear instability across a range of streamwise disturbance
-wavenumbers. This leads us to suppose that this instability might be a
-plausible cause for a self-sustaining process in viscoelastic plane Couette
-flow, similar to that observed by Waleffe for Newtonian flows.
+we observe an instability across a range of streamwise disturbance wavenumbers.
+This instability persists for larger $\Delta$, albeit with a fairly complex
+dependence on the boundaries. Before we examine the effect of the walls we will
+consider the instability in the free shear limit.
 
-We see an instability grow from around $k \sim 0.06$ and move to lower $k$ as
-the Weissenberg number increases (figure \ref{fig:KH_inf_dispersions_vary_Wi}). The
-height of the instability also increases with increasing Weissenberg number
-(figure \ref{fig:KH_inf_disp_height_vary_Wi}).
+\subsection{Free shear layer}
+
+For a free shear layer we observe an instability grow from around $k \sim 0.06$
+and move to lower wavenumber as the Weissenberg number increases. The
+dispersion relations shown in figure \ref{fig:KH_inf_dispersions_vary_Wi} show
+this dependence of the unstable eigenvalues on $\Wi$. The dispersion relation
+for the instability remains broad in $k$ until $Wi \sim 100$ where a new
+eigenvector becomes dominant.
 
@@
 
-The dispersion relation saturates at $Wi \sim 50$ and remains approximately
-constant with increasing Weissenberg number. The dispersion relation for the
-instability remains broad in $k$ until $Wi \sim 100$ where a new eigenvector
-becomes dominant.
+The height of the instability also increases with increasing Weissenberg
+number. Extracting the peak growth rate from the dispersion relations at a
+fixed $\Rey$ for various $\Wi$ allows us to show how the instability depends on
+both $\beta$ and $\Wi$ (figure \ref{fig:KH_inf_disp_height_vary_Wi}). The
+maximum growth rate saturates at $Wi \sim 50$ and remains approximately
+constant with increasing Weissenberg number. The slight nonmonotonicity in the
+curve is the result of the switchover in the dominant instability eigenmode.
 
@@
 
-As the Reynold's number is reduced, new eigenvalues become dominant. Although
-the dominant eigenvalue changes the flow is still unstable, even down to $\Rey
-= 0.01$ (see figures \ref{fig:KH_inf_disp_height_vary_Re} and \ref{fig:KH_dispersions_vary_Re}).
+As the Reynold's number is reduced the Newtonian Kelvin-Helmholtz instability
+disappears and an entirely separate, purely elastic instability arises.
+Although the dominant eigenvalue changes often as $\Rey$ decreases,  the flow
+is still unstable even down to $\Rey = 0.01$ (see figures
+\ref{fig:KH_inf_disp_height_vary_Re} and \ref{fig:KH_dispersions_vary_Re}).
+Again, the complicated dependence on $\Rey$ appears to be due to the appearance
+and disappearance of new dominant eigenmodes of the instability.
 
@@
 
-Now we use equations \ref{eq:KH_laminar_profile} and examine the unstretched
-pseudospectral domain. To validate the code, we examine the high Reynolds
-number regime. We see the height of the instability decrease with increasing
+Now we use equations \ref{eq:KH_laminar_profile} for a two dimensional flow
+with boundaries.  To validate our approach, we examine the high Reynolds number
+regime in order to recover a Newtonian Kelvin-Helmholtz instability. At high
+Reynolds number the instability is insensitive to the distance to the walls
+when $\Delta =0.1$ (figure \ref{fig:KH_high_Re_walls_dependence}) and is
+consistent with the Kelvin-Helmholtz instability given in \citet{Criminale2003}.
+
+We see the maximum growth rate of the instability decrease with increasing
 Weissenburg number, and this trend is stronger for smaller $\beta$ (figure
 \ref{fig:KH_drag_reduction}). This is the same behaviour reported in
-\cite{Azaiez1994}.
+\cite{Azaiez1994} for the Kelvin-Helmholtz instability of a polymeric fluid.
 
@@
     \caption{ 
-	Peak growth rate against Weissenberg number at $\Rey = 1000$,
-	$\Delta = 0.1$ The height of the dispersion relation is reduced for the
+	Peak growth rate against Weissenberg number at $\Rey = 1000$, $\Delta =
+	0.1$ The height of the dispersion relation is reduced for the
 	Kelvin-Helmholtz instability as the Weissenberg number is increased.
@@
 	Newtonian fluid. The decrease in $\lambda_{r}$ corresponds to increased
-	stability of the base flow, this matches the observations made in \cite{Azaiez1994}} 
+	stability of the base flow, this matches the observations made in
+	\cite{Azaiez1994}
+    } 
     \label{fig:KH_drag_reduction} 
@@
 
-The instability remains present under variation of $\Delta$ at low $\Delta$. At
-$\Delta =0.1$ the instability is still present for $\Rey < 0.01$ far lower than
-the usual threshold of $\Rey \sim 1000$ for a Newtonian Kelvin-Helmholtz
-instability (figure \ref{fig:KH_walls_vary_Re}).
-
-At high Reynolds number the instability is insensitive to the distance to the
-walls when $\Delta =0.1$ (figure \ref{fig:KH_high_Re_walls_dependence}). At low
-Reynolds number, the width of the channel is more important but the instability
-is still present for very low $\Delta$ (figure
-\ref{fig:KH_low_Re_walls_dependence}).
+At low Reynolds number, we can examine the purely elastic shear layer
+instability of above. In this case find that the width of the channel has a
+greater affect on the instablity of the flow. However, the flow is still
+unstable at very low $\Delta$ (figure \ref{fig:KH_low_Re_walls_dependence}). At
+$\Delta = 0.1$ the flow is unstable for $\Rey < 0.01$ far lower than the usual
+threshold of $\Rey \sim 1000$ for a Newtonian Kelvin-Helmholtz instability
+(figure \ref{fig:KH_walls_vary_Re}).
 
@@
 
-As $\Delta$ decreases for a particular purely elastic instability, the size of
-the velocities expands slightly but in the limit of very small $\Delta$ the
-eigenvector appears independent of the walls (figures
-\ref{fig:KH_psi_low_delta} and \ref{fig:KH_psi_high_delta}). The large width
-vortices in our purely elastic case, seem to correspond to the larger
-elasticity ($G~\Wi/\Rey$) eigenvectors in \citet{Azaiez1994}. Their $G=5$ case
-would only correspond to $\Wi=0.5$ for $\Re=0.1$ in our purely elastic
-instability, so it is a completely different, inertial instability that they
-observe (\citet{Azaiez1994} figure 8). Nonetheless at least one of their
-observations does apply. The fact that the velocity disturbance is essentially
-zero in the center of the channel, implies that the shear layer will be less
-likely to roll up. In the Newtonian instability, net velocities within the
-shear layer will distort its shape, however the purely elastic instability
-appears to have less of an effect on the shear layer.
+As $\Delta$ decreases for a particular purely elastic instability, the width of
+the instability increases slightly, however in the limit of very small $\Delta$
+the eigenvector appears independent of the walls (figures
+\ref{fig:KH_psi_low_delta} and \ref{fig:KH_psi_high_delta}). The extended
+vortices in our purely elastic case seem to correspond to the eigenvectors in
+\citet{Azaiez1994} at larger elasticity ($G \sim \Wi/\Rey$) . Their $G=5$ case would
+correspond to only $\Wi=0.5$ for $\Rey=0.1$ in our units, such that the
+instability they observe is still the inertial instability ( see
+\citet{Azaiez1994} figure 8). Nonetheless at least one of their observations
+does apply. The fact that the velocity disturbance is essentially zero in the
+center of the channel, implies that the shear layer will be less likely to roll
+up. In the Newtonian instability, net velocities within the shear layer will
+distort its shape, however the purely elastic instability appears to have less
+of an effect on the shear layer.
 
@@
 worse at lower $\Rey$.  By introducing just a very small contribution from
-inertia, we can remove the dependence on the walls. This is why all of our
-results are taken for $\Rey \lesssim 0.1$ on the length scale of the
+inertia, we can remove the dependence on the walls. This is partly why all of
+our results are taken for $\Rey \lesssim 0.1$ on the length scale of the
 instability.
